### 2021-07-02 Paper_third_version/Article_UV_Mexico.tex
Add Paper versions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=jacsat,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{chemformula} % Formula subscripts using \ch{}
\usepackage[T1]{fontenc} % Use modern font encodings
\usepackage{lineno}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{multirow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Adriana Ipiña}
\email{ipina@ifir-conicet.gov.ar}
% \affiliation{corresponding author}
\affiliation{Instituto de Física Rosario (CONICET-UNR), Rosario, Argentina}
\alsoaffiliation{Centro de Ciencias de la Atmósfera, Universidad Nacional Autónoma de México, Mexico City, Mexico}

\author{Gamaliel López-Padilla}
\affiliation{Facultad de Ciencias Físico Matemáticas, Universidad Autónoma de Nuevo León, San Nicolás de los Garza, México}

\author{Armando Retama}
% \altaffiliation{A shared footnote}
% \email{i.k.groupleader@unknown.uu}
% \phone{+123 (0)123 4445556}
% \fax{+123 (0)123 4445557}
\affiliation{Independent researcher, Mexico City, Mexico}
% \alsoaffiliation[Second University]
% {Department of Chemistry, Second University, Nearby Town}

\author{Rubén D. Piacentini}
% \email{s.k.laborator@bigpharma.co}
\affiliation{Instituto de Física Rosario (CONICET-UNR), Rosario, Argentina}

\author{Sasha Madronich}
\affiliation{National Center for Atmospheric Research, Boulder, Colorado, USA}
% \alsoaffiliation[Second University]
% {Department of Chemistry, Second University, Nearby Town}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[The UV radiation in Mexico City]
  {The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico
  City 2000-2019}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{IR,NMR,UV}
\keywords{Ultraviolet radiation, UV~Index, Megacities, Air pollution,
Urban photochemistry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}
  %\includegraphics[width=9cm, height=3.5cm]{figures/Graphical_Abstract.png}
  \includegraphics[scale=1]{figures/Graphical_Abstract.png}
  Some journals require a graphical entry for the Table of Contents.
  This should be laid out ``print ready'' so that the sizing of the
  text is correct.

  Inside the \texttt{tocentry} environment, the font used is Helvetica
  8\,pt, as required by \emph{Journal of the American Chemical
    Society}.

  The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
  permitted for  \emph{Journal of the American Chemical Society}
  graphical table of content entries. The box will not resize if the
  content is too big: instead it will overflow the edge of the box.

  This box and the associated title will always be printed on a
  separate page at the end of the document.

\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Tropical regions experience naturally high levels of UV radiation, but
  urban pollution can reduce these levels substantially. We analyzed 20
  years of measurements of the UV Index (UVI) at several ground-level
  locations in the Mexico City Metropolitan Area and compared these data
  with UVI values derived from satellite observations of ozone
  and clouds (but not local pollution). The ground-based measurements were
  systematically lower than the satellite-based estimates, by ca. 40\% in
  2000 and 20\% in 2019. Calculations with a radiative transfer model and
  observed concentrations of air pollutants explained well the difference
  between satellite- and ground-based UVI, and showed specific
  contributions from aerosols in the boundary layer and the free troposphere,
  O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}, in
  decreasing order of importance. Such large changes in UV radiation
  between 2000 and 2019 have important implications ranging from human
  health (skin cancer and cataract induction) to air pollution control
  (photochemical smog formation).
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Ultraviolet (UV) radiation is an important component of the urban
environment, affecting human populations directly through UV exposure of
skin and eyes~\citep{Taylor_1988,Varotsos_1997,Lucas_2019}
and less directly (but with great
impact) by driving the formation of photochemical smog, including
tropospheric ozone and other oxidants, as well as secondary aerosols
containing nitrates, sulfates, and
organics.\citep{LEIGHTON_1961,Seinfeld_1998,Finlayson_Pitts_2000}
These pollutants, along with others of primary origin commonly found in urban
atmospheres (e.g., black carbon, sulfur dioxide), can in turn scatter
and/or absorb UV radiation, alter its vertical distribution, and so
modify the photochemical rate of their own formation. Such feedback
complicates the calculation of both the UV radiation field (including at
the surface), and the evolution of photochemical smog in the urban
boundary layer.

The question of how air pollution alters the urban UV environment
(and~\emph{vice versa}) is not new, but studies have relied mostly on
numerical models \cite{Liu_1991,Sabziparvar_1998,Madronich_2011},
with relatively few available observations (e.g.,
\citet{McKenzie_2008}, \citet{Panicker_2009}, \citet{Palancar_2013},
reviewed by \citet{Bais_2015}). Increases in UV have been estimated as a consequence
of emission reductions over the last decades, e.g. in China,\citep{Hollaway_2019,Li_2018,Wang_2020}
and have led to less-than-expected
reductions in photochemical smog, in part due to stronger UV
photochemistry.\citep{Wang_2019,Gao_2020,Ma_2020}
Emission reductions have also occurred
globally during the 2020 COVID-19 pandemic,\citep{Bauwens_2020,Venter_2020}
but ground-level ozone in some polluted areas has actually
increased,\citep{Shi_2020,Le_2020} due at least in part to the increased UV
radiation. Unfortunately, the observational data base of relevant UV
radiation remains rather sparse to evaluate such model-derived
hypotheses.~~

The environment of Mexico City is of particular interest for several
reasons: (1) Nearly 23 million people inhabit the Mexico City
Metropolitan Area (MCMA), and the UV environment has direct implications
for their health, both in terms of skin/eye UV exposure and~\emph{via}
photochemical smog formation. (2) As a tropical megacity, it is to some
extent representative of the situation of many others, with year-round
intense midday UV irradiance, a shallower atmosphere due to the city's
high elevation of 2240 m above sea level, and a transition toward newer
and cleaner technologies, leading to gradual improvements in air
quality. (3) Air quality within MCMA has undergone extensive scrutiny,
with a well-established monitoring network operating since
1986,\cite{RAMA}
numerous intensive field campaigns to study the
meteorology, emissions, and photochemistry of smog
formation,\citep{Doran_1998,Molina_2007,Molina_2010}
and numerical modeling incorporating the
evolving knowledge.\citep{Jazcilevich_2005,Tie_2007,Zhang_2009,Zavala_2020}
This extensive body of knowledge
provides the foundation for understanding our study.

Here, we analyze two decades of continuous measurements of the UV Index
at multiple locations within the MCMA, collected by the Secretariat of
the Environment (Secretaría del Medio Ambiente,
SEDEMA)\footnote{\url{https://www.sedema.cdmx.gob.mx/}} of the Mexico
City government as part of an intensive monitoring network over the
MCMA. The UV Index is defined as:

\begin{equation}
  \label{eq:UVI}
  UVI=40 \int_{250nm}^{400nm} E\left(\lambda,t\right) \cdot S_{er}(\lambda) d\lambda
\end{equation}

where~\(E(\lambda,t)\)\emph{~} is the solar spectral irradiance in
units of W ·m\textsuperscript{-2} ·nm\textsuperscript{-1}
and~\(S_{er}\left(\lambda\right)\) is the erythemal sensitivity of human
skin.\citep{who2002,Webb_2011}
Multiplication by 40 was chosen historically to
express the UVI in small integer numbers, but is otherwise
scientifically arbitrary.

The UVI is recognized by the World Health and Meteorological
Organizations (WHO and WMO) as a standardized metric of UV
radiation\cite{who2002} for global public information. An advantage
of using the UVI as (one) measure of UV radiation is that it is being
increasingly observed or calculated and disseminated, enabling more
objective comparisons among seasons and locations. The UVI observations
from Mexico City, considered here, are an important element of this
global picture.

While the UVI at the surface cannot be translated directly into
photolysis frequencies for various photo-labile molecules, the spectral
weighting of the UVI (ca. 300-320 nm) is approximately similar to that
for the photolysis of ozone to singlet oxygen atoms. Other UV
wavelengths are of course also important, e.g. for the photolysis of
nitrogen dioxide, and may be affected differently depending on the
pollutant. With these considerations and a few other caveats, UVI trends
examined here can also be used to infer accompanying trends in
photolysis frequencies and influences on photochemical smog formation.

\section{Methods}
\label{sec:methods}

\subsection{Ground-based measurements}

The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
meters above sea level (asl), surrounded by mountain ridges exceeding
5000 m asl, with complex topography and thermal inversions that inhibit
winds and favor intense air pollution.\citep{Whiteman_2000,Fast_2007,Carre_n_Sierra_2015}
Air quality
monitoring and surface meteorological measurements in the MCMA are
conducted continuously by the Automated Atmospheric Monitoring Network
(RAMA, by its Spanish acronym) of the Atmospheric Monitoring System
(SIMAT, by its Spanish acronym) of the Mexico City government. Since the
year 2000, UV radiometers (model 501-A, Solar Light Company Inc.,
Glenside, PA) detecting wavelengths between 280-400 nm have been
measuring erythemally-weighted solar radiation. The calibration of the
UV sensors has been carried out annually by comparing against a
factory-calibrated reference sensor. The output voltages from the
network’s sensors have been compared for at least one week against the UV
readings from the reference sensor to derive a calibration factor. New
calibration factors typically differ from the old ones by 2\% or less.
Reference sensors have been also calibrated by the manufacturer and updated
periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
Long term calibration drift are minimized by these yearly re-calibrations.
Although at the beginning only a few stations were in operation and have
been changing, currently 11 stations are recording erythemal
irradiances, which are then multiplied by 40 (see
Eq.~{\ref{eq:UVI}}) to give UV Indices.
Table~{\ref{table:stations}} describes the location of
the stations where the UV Index has been measured.
Figure~{\ref{fig:map}} shows how the radiometers of the
SIMAT have been distributed over MCMA, prioritizing sites with higher population density.
Near real-time data for each station are
available on the SIMAT official
website~\url{http://www.aire.cdmx.gob.mx/default.php}. Daily maximum
values (\(UVI_{\max}\)) were extracted~in each of the stations
around solar noon from the time interval from 11:00 h-15:00 h CST
(Central Standard Time). This database~with 7305 continuous days of
measurements during the period 2000-2019 was analyzed.

\begin{table}[H]
  \centering
  \begin{tabular}{ccccc}
    \hline
    Station  & Environment     & Lat (ºN) & Lon (ºW) & El (masl) \\ \hline
    CHO      & semi-urban      & 19.27    & 98.89    & 2253      \\
    CUT      & ecological park & 19.72    & 99.20    & 2263      \\
    FAC      & urban           & 19.48    & 99.24    & 2299      \\
    HAN      & urban           & 19.42    & 99.08    & 2235      \\
    LAA      & urban           & 19.48    & 99.15    & 2255      \\
    MER      & downtown        & 19.42    & 99.12    & 2245      \\
    MON      & rural           & 19.46    & 98.90    & 2252      \\
    MPA      & rural           & 19.18    & 98.99    & 2594      \\
    PED      & residential     & 19.33    & 99.20    & 2326      \\
    SAG      & urban           & 19.53    & 99.03    & 2241      \\
    SFE      & residential     & 19.36    & 99.26    & 2599      \\
    TLA      & urban           & 19.53    & 99.20    & 2311      \\
    UNAM$^*$ & University city & 19.33    & 99.18    & 2294      \\\hline
  \end{tabular}
  \caption{{{{SIMAT stations and AERONET site$^*$, environmental descriptors and geographical
                positions. Abbreviations names: Chalco (CHA), Cuautitlán (CUT), FES Acatlán
                (FAC), Hangares (HAN), Laboratorio de Análisis Ambiental (LAA), Merced
                (MER), Montecillo (MON), Milpa Alta (MPA), Pedregal (PED), San Agustín
                (SAG), Santa Fe (SFE), Tlalnepantla (TLA) and National Autonomous University of Mexico (UNAM$^*$)}}}}
  \label{table:stations}
\end{table}

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/map}
    \caption{{Map with the location of the SIMAT continuous monitoring stations over
          MCMA. Sites denoted by the blue solid dots correspond to SIMAT stations
          with UV measurements, while the black dots indicate SIMAT stations
          without UV measurements, the site indicated by an open blue dot represents a
          discontinued site, the red dot shows the location of the
          AERONET site. The location~of Mexico City and the acronyms of the UV and
          AERONET site are shown at the upper and lower frames at the right
          respectively.
            {\label{fig:map}}%
        }}
  \end{center}
\end{figure}

With the aim to explore the relationship between UVI and air pollutants
levels, the hourly averages for ozone (O\textsubscript{3}), carbon
monoxide (CO), nitrogen dioxide (NO\textsubscript{2}), sulfur
dioxide~(SO\textsubscript{2}) and particle matter with diameter
sizes~\(\le\) 10 ~$\mu$m (PM\textsubscript{10}), were downloaded
from the SIMAT.\cite{pollutants_data} For purposes of assessing the
influence on the UV Index at solar noon, only values obtained between
11h and 15h CST were considered for the trends analysis. Pollutant
measurements are conducted by the SIMAT using regulatory-grade
commercial instruments. Measurement principles include ultraviolet
photometry (model 400E, Teledyne-API) for O\textsubscript{3},
chemiluminescence (model 200E, Teledyne-API) for NO\textsubscript{2}, UV
fluorescence (model 100E, Teledyne API) for SO\textsubscript{2}, and
infrared absorption (model 300E, Teledyne-API) for CO. The
PM\textsubscript{10} continuous mass concentration was measured with
Tapered Element Oscillating Microbalance (TEOM 1400AB or TEOM 1405 DF,
Thermo Scientific) monitors. Gaseous pollutant levels are reported in
ppb concentration units for O\textsubscript{3}, SO\textsubscript{2} and
NO\textsubscript{2}, and in ppm for CO. Particulate matter mass
concentration is reported in $\mu$g m\textsuperscript{-3} at local
conditions for temperature and pressure.

Aerosol optical depth at 340 nm was obtained from the Institute of
Geophysics of the National Autonomous University of Mexico (UNAM).
Measurements were conducted with a CIMEL sun photometer model CE-318,
which is an automatic sun-sky-scanning spectral radiometer of
the AErosol RObotic NETwork (AERONET~\citep{Holben_1998}). The data
Product Level 2.0 and 1.5 (only in 2019) were selected, and annual
averages AOD\textsubscript{340} were calculated along the period 2000-2019,
except for the year 2011 due to there were no measurements. A previous study of the AOD
behavior from 2000 to 2014 demonstrated that data gaps did not
significantly change the trends calculated for this.\citep{Carabali_2017}
Only 8\% of the data between the years 2014 and 2019 were missing.
The largest data gap occurred in 2018 when the instrument was returned for calibration.

\subsection{Satellite data}

The UV Index data derived from satellite measurements of reflected radiance
were used for comparison with the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated in cooperation between the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical dimension of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33N, 99.18W) and elevation (2268 masl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
Measurements of the ozone profile and cloud cover are used via a
radiative transfer model to estimate the UVI at the ground.
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 data product, version 1.3 and collection 3.

\subsection{TUV model}

Calculations of the UV Index were also made with the Tropospheric
Ultraviolet Visible (TUV v5.3) model.\citep{Madronich_1987} The
model atmosphere was represented by 80 vertical layers, each 1 km thick,
starting at the 2.24 km asl elevation of MCMA, and for which the first
three km constitute the atmospheric boundary layer
(BL).\citep{Shaw_2007} The ozone profile above the BL is from the US
Standard Atmosphere, but rescaled to a value of 259.6 DU. Totals
including the BL contributions (of 13.7 DU in the year 2000 and 9.8 DU
in 2019, see below) were 273.1 DU in 2000 and 269.2 DU. The
climatological O\textsubscript{3} column for this latitude and season is
about 270 DU (plus or minus ca. 5 DU) so in good agreement with the
values used here.

Pollutants within the BL (including O\textsubscript{3}) are assumed to
be well mixed, in agreement with observations from the MILAGRO field
campaign that showed the disappearance of vertical gradients in the
profiles of gases \citep{Velasco_2008,Greenberg_2009} and aerosols
\citep{Rogers_2009,Lewandowski_2010} by late morning. The UV-absorbing gases
considered here are O\textsubscript{3}, NO\textsubscript{2},
and SO\textsubscript{2}, specified in ppb.

BL aerosols are modeled by prescribing the AOD at 340 nm (from AERONET
observations), scaled to other wavelengths inversely with wavelength
(Angstrom coefficient = 1.0), asymmetry factor of 0.7, and a single
scattering albedo of 0.85 at UV wavelengths, following the
determinations made in Mexico City by \citet{Corr_2009} and
\citet{Palancar_2013}.

Above the atmospheric boundary layer, the model was taken to be free of
aerosols, NO\textsubscript{2}, or SO\textsubscript{2}. In one
sensitivity study, a total AOD of 0.7 was redistributed placing 0.2 in
the free troposphere (decreasing vertically with an exponential scale
height of 4 km, and 0.5 remaining in the BL). The calculated UVI
differed by less than 1\%. Thus, as long as the total AOD is known,
knowledge of the exact vertical aerosol profile is not critical towards
ground-level UVI -- but would obviously affect the vertical structure of
photolysis frequencies.

Radiative transfer calculations were carried out with the
pseudo-spherical 4-stream option, at 1 nm steps between 280 and 400 nm.

\section{Results and Discussion}
\label{results-and-discussion}

Figure~{\ref{628947}} shows the diurnal variation of
the UVI for several specific cloud-free days, for different seasons and
several locations (CHO, MER, MON, PED, SAG, SFE and TLA). UV Index from
TUV model was used as reference of the behavior under clear sky days.
According to the comparison of measurements minute by minute, the dates
with prolonged fluctuations along the day were discarded. However,
during the rainy period (from June to October) at least a brief clouds
presence is common, as shown at CHO station around noon in 13 June
2017. Peak values range from 8 during autumn/winter to above 12
in spring/summer, in correspondence to the respective December and June
solstices. Although the stations are all within a 25 km radius,
substantial differences among them are notable. Survey of the locations
revealed that shadowing from nearby structures is not an issue. The good
agreement in the morning, followed by more divergence in the afternoon,
is consistent with the development of photo-chemical pollution hotspots
during the day. Previous studies (e.g., \citet{Castro_2001} and
\citet{Palancar_2013}) have shown
that surface UV radiation in Mexico City is attenuated significantly by
aerosols. The measurements shown in Fig.~{\ref{628947}}
are consistent with this increasing pollution during the course of the
day, with highest aerosol loading (and highest variability) attained in
the afternoon. Further support for the role of pollution in suppressing
the UVI comes from the observation made at the Santa Fe (SFE) site which
in Fig.~{\ref{628947}} are seen to be systematically
higher, e.g. by over 10\% in autumn afternoons, compared to the other
stations. The SFE station is displaced to the west from the majority of
the other stations, and remains in the outskirts. This site is also
approximately 300 m higher than Mexico City downtown, so that the
cleaner atmosphere results from both vertical and horizontal variations
in pollution levels.\citep{aire_cmdx_2017} It is indeed expected to have
higher values of the UVI, in agreement with the observations.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/season}
    \caption{{UV Index measured over MCMA by SIMAT stations each minute along the day
          under practically cloudless conditions for representative days of the
          year.
            {\label{628947}}%
        }}
  \end{center}
\end{figure}

The daily maximum UV Index of each station is denoted
by~\(UVI_{\max}\), all of them were counted in the period 2000-2019.
As shown in Figure~{\ref{461017}}, these values ranged
from 1 to 16, with a majority (61\%) of the days
experienced~\(UVI_{\max}\) values between 6 and 10, and remarkably
few, less than 1\%, in the higher 13-16 range.~The lowest values are
likely due to winter days with heavy cloud cover and low sun angles, and
UV attenuation by pollutants could also be amplified under such
conditions, due to longer photon path lengths at low sun and within
clouds. The extreme sparsity of high UVI values remains surprising, and
may be an indication of the rarity of extremely unpolluted days within
the city.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.49\columnwidth]{figures/Histogram}
    \caption{{Frequency distribution of daily maximums UV Index values in Mexico City
    during 2000 -2019.
    {\label{461017}}%
    }}
  \end{center}
\end{figure}

Similar patterns are found when considering the monthly average of
the~\(UVI_{\max}\)~values as shown in
Figure~{\ref{310112}}. The long-term averages present a
seasonal variation (as in Fig.~{\ref{628947}}) that
follows approximately the cosine of the noontime solar zenith angle.
Notably, values rarely if ever exceed 12 (as in
Fig.~{\ref{461017}}). The lowest average UVI (near 7)
take place in winter while from March to August the values seem to be
flattened in the range 10-11. The rather low monthly UV Index values,
mainly could be a consequence of the presence of clouds in the rainy
season. However, urban aerosol pollution sources, biomass burning for
agriculture and wood cooking also contribute to poor air quality between
March-May~\citep{Retama_2015}. Using the
maximum~\(UVI_{\max}\) from all of stations every day (one daily
point), the monthly averages (\(\overline{UVI}_m\))
were calculated along the period 2000-2019 (except for June 2003 due to there were no measurements).
Long term trends in~\(\overline{UVI}_m\) are shown
in Figure~{\ref{185758}}. A clear~upward trend is seen,
with a slope for the linear fit of 0.9\%/year or +1.5 UVI units over the
two decades.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/Boxplotcos}
    \caption{{Boxplot of the monthly averages of the maximum UV Index values~(black
          dot) in MCMA for the period 2000-2019: median (central bold line),
          standard deviation (box edges),
          25\textsuperscript{th} and 75\textsuperscript{th} percentiles (the whiskers),
          the minimum and maximum  values (plus sign) and the cosine of the solar zenith angle at solar
          noon (blue curve).
            {\label{310112}}%
        }}
  \end{center}
\end{figure}

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/UV_Moving_Average}
    \caption{{Moving average function (light gray curve) quarterly applied to monthly
          average UV Index, standard deviation of all data within a given month
          (black dots and dash line) and linear fit (red line).
            {\label{185758}}%
        }}
  \end{center}
\end{figure}

The UV Index computed from satellite-based observations
over the period 2005-2019 is mapped in
Figure~{\ref{485116}}. The satellite-derived UVIs vary
from 8 in winter to 16 in summer, both values being substantially higher
than the ground-based observations (ca. 7 for winter and 11 for summer,
see Fig.~{\ref{310112}}). We hypothesize that this
large difference between satellite-based estimation and ground-based
observation of the UV index is due to the intense air pollution of
Mexico City.~A rather similar behavior was detected in Santiago city,
Chile.\citep{Cabrera_2012}

Close inspection of Figure~{\ref{485116}} shows that the maximum values
are reached in June and July of each year.
While the early OMI estimates of the UVI did not account for the boundary layer aerosol absorption,
the current version (1.3) includes the postcorrection by \citet{Arola_2009}
for absorbing aerosols based on global monthly aerosol climatology.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/CSUVindex}
    \caption{{UV Index at solar noon for clear sky recorded by OMI-Aura/NIVR-FMI-NASA,
          from 2005 to 2019.
            {\label{485116}}%
        }}
  \end{center}
\end{figure}

\subsection{Effect of pollutants on UV radiation}

Trends and averages in aerosol optical depth AOD\textsubscript{340} and
criteria pollutants PM\textsubscript{10}, CO, NO\textsubscript{2},
O\textsubscript{3~}and SO\textsubscript{2} observed at the SIMAT
stations over 2000-2019, are shown in
Figure~{\ref{829996}} and summarized in
Table~{\ref{table:uvindex}} together with
the~\(UVI_{\max}\). Similar trends in pollutants have been noted
before\citep{Parrish_2011,aire_cmdx_2017,Molina_2019}
and reflect the long-term success of
emission reduction policies and programs.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.63\columnwidth]{figures/pollutants}
    \caption{{Air quality trends in MCMA for the period 2000-2019~ from annual
    averages obtained between 11h to 15h CST every day: PM\textsubscript{10}
    (brown curve), CO (purple curve), NO\textsubscript{2} (blue curve),
    SO\textsubscript{2}(black curve), O\textsubscript{3} (green curve) and
    AOD\textsubscript{340} (pink curve).
    {\label{829996}}%
    }}
  \end{center}
\end{figure}

\begin{table}[H]
  \centering
  \begin{tabular}{cccc} \hline
    Variable               & $\frac{absolute change}{year}$ & Avg$_{2000-2019}$ & $\Delta(\%/year)$ \\ \hline
    UVI                    & 0.08                           & 9.2               & 0.9               \\
    PM\textsubscript{10}   & -0.10                          & 50.2              & -0.2              \\
    CO                     & -0.08                          & 1.0               & -8.2              \\
    NO\textsubscript{2}    & -0.96                          & 28.6              & -3.4              \\
    O\textsubscript{3}     & -1.05                          & 61.3              & -1.7              \\
    AOD\textsubscript{340} & -0.01                          & 0.6               & -1.6              \\
    SO\textsubscript{2}    & -0.76                          & 8.4               & -9.1              \\
    \hline
  \end{tabular}
  \caption{{{{UV Index and criteria pollutants: the absolute change per year for the period 2000-2019,
                averages in units of $\mu g/m^3$(PM$_{10}$), ppm (CO), ppb
                (SO$_2$, NO$_2$ and O$_3$), dimensionless (UV Index and AOD$_{340}$) and
                annual percentage change (\%/year).}}}}
  \label{table:uvindex}
\end{table}

The observed changes in the concentrations of these air pollutants have
significant implications for surface UV radiation, as can be
demonstrated with the TUV radiative transfer model.
Table~{\ref{table:TUVmodel}} summarizes UVI values for
the June-July time period, estimated by the three methods: OMI
satellite-derived UVI, RAMA ground-based observations, and TUV modeling
using air pollution estimates. Two groups of values can be readily
identified: (1) RAMA daily record values, OMI with or without BL
aerosols, and TUV for very clean conditions, all with UVI values around
15-16; and (2) RAMA average daily maxima and TUV UVI using MCMA
pollutants as input, which are in good agreement for both 2018/19 and
2000/01 but much lower than the first group. Compared to the OMI
estimate that included the climatological aerosol correction (15.3),
observed RAMA values were lower by 35\% in 2000 and by 20\% in 2019.
Similarly, TUV values were 35\% lower in 2000 and 22\% lower in 2019
relative to the TUV values of 15.6 for a pristine atmosphere.

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{Conditions for estimation in June-July}     & \textbf{UV Index} \\ \hline
    RAMA maximum reached in period 2000-2019            & 15.0              \\ \hline
    RAMA average maxima 2018, 2019                      & 12.3              \\ \hline
    RAMA average maxima 2000, 2001                      & 9.9               \\ \hline
    OMI clear, local noon, no corrected for BL aerosols & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                          & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}
      }TUV pristine pollution \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                          & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                          & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                          & 10.2              \\ \hline
  \end{tabular}
  \caption{{UV Index monthly maximum estimates for June-July.}}
  \label{table:TUVmodel}
\end{table}

The agreement between RAMA observations and TUV model estimates is
excellent but also probably a bit fortuitous. Clouds on average reduce
the irradiance impingent on the surface, but scattering from them can
also cause transient enhancements (especially if the direct sunbeam is
not blocked) that could be recorded as daily maxima -- with cancellation
between these cloud effects resulting in improved agreement with the
cloud-free model. We cannot exclude that some of the observed trend in
UVI is due to changes in cloud cover. However, the modeled fractional
UVI reductions due to pollutants, shown in Table
  {\ref{table:TUVmodel}}, are in such good agreement with
the observed UVI reductions, that a compelling case can be made for a
dominant role of air pollutants in the long-term UVI trends.

Table~{\ref{table:year2000-2019}} shows the
contributions to UVI reductions from individual pollutants. Aerosols are
seen to be the major factor in both time periods, followed by
O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}. The
2000-2019 UVI increase is seen to result in comparable proportions from
fewer aerosols, less SO\textsubscript{2}, and the combined reductions in
O\textsubscript{3} and NO\textsubscript{2}.

Comparable UV reductions, of 30-40\% due to aerosols, were reported by
\citet{Panicker_2009} over Pune, India from April 2004 to
March 2005, with sensitivity coefficients (i.e. change in UVI per unit
change in AOD) similar to those found here in Table~\ref{table:TUVmodel}.

Comparisons of OMI with ground-based UV measurements have been reviewed
recently by \citet{Zhang_2019} and \citet{Vitt_2020}.
OMI-derived UV generally overestimates
ground-level measurements by 1-10\% in relatively clean conditions (e.g.
rural U.S), by 10-30\% in Southern Europe and by 40\% or more in
Santiago, Chile\citep{Cabrera_2012} and Thailand\citep{Janjai_2013}. The
overestimations appear related in large part to incomplete accounting of
UV absorption by BL aerosol, although other factors such as the
correction to solar noon may also introduce some
bias.\citep{Zhang_2019} Over Europe, ground-based UVI observations for
several decades are systematically lower than those estimated from
satellites even after consideration of climatological aerosol
distributions, showing the importance of local pollution not resolved
from space.\citep{Vitt_2020} However, difference between
satellite-derived and ground-based UVI was less than 1.0 UVI units in
over 90\% of the cases, in contrast to the difference of 3-5 units found
for Mexico City (Table~{\ref{461017}}).

UV reductions by air pollutants are expected to be most severe near the
surface, while chemical reactions leading to photochemical smog occur
through the vertical extent of the BL.
Figure~{\ref{973680}} shows the vertical profiles of
photolysis coefficients (the reciprocals of photolytic lifetimes) for
two key reactions, the photolysis of O\textsubscript{3} to yield excited
oxygen atoms O(1D), and the photolysis of NO\textsubscript{2}. In the
absence of optically active pollutants, these coefficients would be
nearly independent of altitude in the BL. However, the presence of
pollutants leads to a strong decrease toward the surface, with notably
more severe reductions in 2000 compared to 2019.~While the specific
values shown in the figure are only illustrative for typical conditions,
routine daily air quality modeling should carefully account for the long
term variations in these photolysis coefficients.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/jvals}
    \caption{{Vertical profiles of the photolysis coefficients for the
          reaction~\(O_3 + h\nu \rightarrow O(1D) + O_2\) (top axis, blue)~\(NO_2 + h\nu \rightarrow O+NO \) (bottom
          axis, red) for zero pollution (solid) and Mexico City in the years 2000
          (dashed) and 2019 (dotted)
          {\label{973680}}%
        }}
  \end{center}
\end{figure}

An issue that is beginning to gain relevance in radiative balance models
is the influence of a group of organic compounds capable of strongly
absorbing in the UV region (brown carbon).\citep{Laskin_2015} Some of
these compounds are related with emissions from local and regional
wildfires.\citep{Gadhavi_2010} Mexico City is frequently exposed to
regional fire smoke transport during the dry part of the year (November
to May)\citep{Rios_2019}, that sporadically modify the optical
properties of the aerosols.\citep{Barnard_2008} This could partly explain
the relatively minor reductions in PM\textsubscript{10} (see
Fig.~{\ref{829996}}), compared to the larger reductions
of CO, NO\textsubscript{2}, and O\textsubscript{3} that are more
directly related to urban activities, as well as some of the seasonal
asymmetry seen in Fig. {\ref{461017}}. ~

The UVI is specific to wavelengths mainly in the 300-320 nm range, and
so the question remains whether these results can be applied at longer
UV wavelengths, e.g. those important for NO\textsubscript{2} photolysis
(\textless{}420 nm). Absorption by SO\textsubscript{2} and
O\textsubscript{3} vanishes, while absorption by NO\textsubscript{2}
increases and typical aerosols optical depth decrease. These changes can
easily be modeled, but unfortunately far fewer measurements of these
longer wavelengths are available in Mexico City or elsewhere.

Two decades of observations in Mexico City demonstrate unequivocally
that air pollution reduces UV radiation at the ground. The ground-based
observations are well below data derived from satellite-based
observations. Although ideally both data sets should match,
the satellite has a limitation to seeing boundary layer absorbers.
When typical values of the pollutants (aerosols,
tropospheric ozone, and to a lesser extent NO\textsubscript{2}
and SO\textsubscript{2}), are included in a model (e.g. TUV), the
differences between satellite-derived and ground-based measured values
are explained and can be attributed quantitatively to individual
observed pollutants. Long term improvements in air quality, over two
decades, are accompanied by statistically significant increases in the
observed UVI, again in good agreement with the model-predicted changes.

\begin{table}[H]
  \centering
  \begin{tabular}{lccccc}
    \hline
    \multicolumn{1}{c}{\multirow{2}{*}{Pollutant}} & \multicolumn{2}{c}{Year 2000} & \multicolumn{2}{c}{Year 2019} & 2019-2000                 \\ \cline{2-6}
    \multicolumn{1}{c}{}                           & poll. level (a)               & UVI (b)                       & poll. level & UVI   & (c) \\ \hline
    AOD                                            & 0.7                           & -3.7                          & 0.5         & -2.7  & 1.0 \\
    O\textsubscript{3} ppb (DU)                    & 70 (14)                       & -1.4                          & 50 (10)     & -1.0  & 0.4 \\
    NO\textsubscript{2} ppb                        & 40                            & -0.9                          & 20          & -0.5  & 0.4 \\
    SO\textsubscript{2} ppb                        & 30                            & -0.8                          & 1           & -0.04 & 0.8 \\ \hline
  \end{tabular}
  \caption{Contributions of individual pollutants to UV Index changes. (a) Values used one at the time, with the others held at zero. (b) UVI deviation from the zero-pollution value of 16.1 (from Table \ref{table:TUVmodel}). (c) 2019-2000 UVI change due to changes in each pollutant.}
  \label{table:year2000-2019}
\end{table}

The reductions in surface UV radiation with respect to an ideally clear
atmosphere -- by nearly 40\% in 2000 and still 20\% in 2020 -- are
large, both within the context of human UV exposure and air quality
mitigation. In urban areas where ozone production scales proportionally
with UV levels and with volatile organic compound~(VOC) emissions (the
VOC-limited regime), a 10\% increase in BL average photolysis rates
means that VOC emissions will need to be reduced by 10\% to meet the
same goals, or else successful reductions in aerosols would lead to
unwanted UV-driven increases in O\textsubscript{3}.~Such UV changes must
be considered carefully in air quality mitigation strategies. For human
exposure, a 20\% increase in UV irradiances over two decades should be
seen as a non-negligible public health issue requiring some reassessment
of preventive behaviors to minimize the risk of skin cancer, cataract,
and other UV-related health effects. The efforts that Mexico City has
made to improve air quality have achieved positive results in the levels
of most air pollutants. Nevertheless, they caused an increase in UV
radiation that reaches the surface.

A limitation of the present work is our focus on daily maximum values,
which largely exclude cloud cover. Absorption within clouds can be
enhanced by the long path lengths of multiply scattered photons, so that accurate quantification of UV
effects of clouds in polluted environments remains a significant
challenge and interesting opportunity for future work.

Finally, based on our results, the solar radiation monitoring network could be
improved by adding observation sites within or close to the basin, with minor
influences of the urban plume (e. g., Amecameca; latitude: 19.13ºN, longitude: 99.76ºW, elevation: 2420 m asl),
and the complementing of sensors in existing monitoring sites that are at elevations above the urban boundary
layer like Ajusco (AJU, elevation: 2953 m asl) or Instituto de Investigaciones Nucleares (INN, elevation: 3082 m asl).
These sites would provide valuable observations to assess quantitatively the effects of urban pollution on solar radiation levels.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "Acknowledgement" section can be given in all manuscript
%% classes.  This should be given within the "acknowledgement"
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgement}
  We wish to acknowledge the staff of SIMAT, from the Secretariat of
  Environment, for the data and the continuous assistance during the
  realization of this project. Adriana Ipiña would like to extend her
  thanks to Dirección General de Personal Académico, Universidad
  Nacional Autónoma de México (DGAPA-UNAM) for the postdoctoral fellowship
  at Centro de Ciencias de la Atmósfera of the UNAM. Rubén D Piacentini
  wishes to thank CONICET and National University of Rosario, Argentina,
  for their partial support to the present work. The National Center for
  Atmospheric Research is sponsored by the National Science Foundation.
\end{acknowledgement}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %% The same is true for Supporting Information, which should use the
% %% suppinfo environment.
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{suppinfo}

% A listing of the contents of each file supplied as Supporting Information
% should be included. For instructions on what should be included in the
% Supporting Information as well as how to prepare this material for
% publications, refer to the journal's Instructions for Authors.

% The following files are available free of charge.
% \begin{itemize}
%   \item Filename: brief description
%   \item Filename: brief description
% \end{itemize}

% \end{suppinfo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{bibliography/bibliodoi}

\end{document}

### 2021-07-02 Paper_third_version/figures/resize_graphical_abstract.py

@@ -1,0 +1,4 @@
+from PIL import Image
+image = Image.open('Graphical_Abstract.tif')
+image_resize=image.resize((255,100))
+image_resize.save("Graphical_Abstract.png")

### 2021-07-02 Scripts/Calculate_daily_mean_per_hour.py
Reorder prints

@@ -45,16 +45,18 @@ inputs = {
     "Hour final": 15,
     "Month initial": 6,
     "Month final": 7,
-    "Year initial": 2000,
-    "Year final": 2001,
+    "Year initial": 2018,
+    "Year final": 2019,
 }
 files = sorted(os.listdir(inputs["path data"]))
 for wavelength in inputs["wavelength"]:
+    print("Analizando {} en el periodo {}-{}".format(wavelength,
+                                                     inputs["Year initial"],
+                                                     inputs["Year final"]))
     resize = inputs["wavelength"][wavelength]
     files_type = select_files(files,
                               wavelength)
     for i, file in enumerate(files_type):
-        print("Analizando archivo {}".format(file))
         if i == 0:
             data_all = read_data(inputs["path data"],
                                  file)
@@ -69,4 +71,8 @@ for wavelength in inputs["wavelength"]:
     data_all = data_all[data_all.index.month >= inputs["Month initial"]]
     data_all = data_all[data_all.index.month <= inputs["Month final"]]
     data_all = data_all.resample("D").max()
-    print(data_all.max()*resize)
+    mean = data_all.mean()["value"]*resize
+    std = data_all.std()["value"]*resize
+    print("Mean\tStd")
+    print("{:.1f}\t{:.4f}".format(mean,
+                                  std))

### 2021-07-02 Scripts/Calculate_monthly_mean.py
Initialize documentation

@@ -2,7 +2,7 @@ import pandas as pd
 import os
 
 
-def select_files(files, type_name):
+def select_files(files=[], type_name=""):
     files_type = []
     for file in files:
         if type_name in file:
@@ -10,7 +10,7 @@ def select_files(files, type_name):
     return files_type
 
 
-def read_data(path, name):
+def read_data(path="", name=""):
     data = pd.read_csv("{}{}".format(path,
                                      name),
                        index_col=0)
@@ -18,7 +18,7 @@ def read_data(path, name):
     return data
 
 
-def format_date_data(data):
+def format_date_data(data=pd.DataFrame()):
     data.index = pd.to_datetime(data.index)
     data = data.drop(["parameter",
                       "unit",

### 2021-07-02 Scripts/Calculate_RD_between_OMI_and_measurements.py
Add Calculate RD between OMI and measurements

@@ -1,0 +1,189 @@
+import matplotlib.pyplot as plt
+import pandas as pd
+import os
+
+
+def read_OMI_data(path="", name=""):
+    """
+    Lectura de los datos de OMI
+    #### inputs
+    path -> direccion donde se encuentran los datos
+
+    name -> nombre del archivo
+    """
+    # Lectura cruda de los datos
+    data = pd.read_csv("{}UVI_{}.csv".format(path,
+                                             name),
+                       index_col=0)
+    # Formato de fecha a los datos
+    data = format_data(data)
+    return data
+
+
+def format_data(data=pd.DataFrame()):
+    """
+    Formato de fecha en el indice del dataframe
+    """
+    data.index = pd.to_datetime(data.index)
+    return data
+
+
+def obtain_monthly_mean(data=pd.DataFrame()):
+    """
+    Calculo del promedio mensual a partir de un dataframe
+    """
+    return data.resample("MS").mean()
+
+
+def read_SEDEMA_data(path="", resize=1):
+    """
+    Lectura de los datos de la SEDEMA
+    #### inputs
+    path -> direccion donde se encuentran los datos
+
+    resize -> valor para convertir los datos a UVI
+    """
+    # Listado de los archivos de la SEDEMA
+    files = sorted(os.listdir(path))
+    # Seleccionar unicamente los de UVB
+    files = select_SEDEMA_files(files=files,
+                                type_name="UVB")
+    # Ciclo para reunir todos los archivos en un solo dataframe
+    for i, file in enumerate(files):
+        if i == 0:
+            # Lectura de los datos de la SEDEMA
+            data = read_SEDEMA_data_each_file(path,
+                                              file)
+        else:
+            # Lectura de los datos de la SEDEMA
+            data_year = read_SEDEMA_data_each_file(path,
+                                                   file)
+            # Union de todos los dataframe en uno solo
+            data = data.append(data_year)
+    # Obtener el máximo diario de todas las estaciones
+    data = obtain_daily_maximum(data)
+    # Redimensionar los datos UVI
+    data["value"] = data["value"]*resize
+    return data
+
+
+def select_SEDEMA_files(files=[], type_name=""):
+    """
+    Descarta los archivos dependiendo si contienen un nombre en especifico
+    #### inputs
+    files -> listado de los archivos sin filtrar
+
[…]

### 2021-07-02 Scripts/Graphics_uvi_omi.py

@@ -33,7 +33,8 @@ UV_values = np.arange(inputs["UV minium"],
                       inputs["UV maximum"])
 UVI_map = np.zeros((inputs["year final"]-inputs["year initial"]+1,
                     365))
-data = pd.read_csv(inputs["path data"]+"UVI_"+inputs["column"]+".csv",
+data = pd.read_csv("{}UVI_{}.csv".format(inputs["path data"],
+                                         inputs["column"]),
                    index_col=0)
 print(inputs["column"], data.max())
 data.index = pd.to_datetime(data.index)

### 2021-07-02 Scripts/Calculate_RD_between_OMI_and_measurements.py
Add to csv on the monthly mean results

@@ -156,6 +156,8 @@ OMI_monthly_mean = obtain_monthly_mean(OMI_data)
 OMI_monthly_mean = select_data(data=OMI_monthly_mean,
                                date_initial=parameters["Year initial"],
                                date_final=parameters["Year final"])
+monthly_mean = pd.DataFrame(index=OMI_monthly_mean.index)
+monthly_mean["OMI"] = OMI_monthly_mean["CSUVindex"]
 # Lectura de los datoa de SEDEMA
 SEDEMA_data = read_SEDEMA_data(path=parameters["path SEDEMA data"],
                                resize=parameters["wavelength"]["UVB"])
@@ -165,10 +167,14 @@ SEDEMA_monthly_mean = obtain_monthly_mean(SEDEMA_data)
 SEDEMA_monthly_mean = select_data(data=SEDEMA_monthly_mean,
                                   date_initial=parameters["Year initial"],
                                   date_final=parameters["Year final"])
+monthly_mean["SEDEMA"] = SEDEMA_monthly_mean["value"]
 # Calculo de la RD
-RD = (OMI_monthly_mean["CSUVindex"] -
-      SEDEMA_monthly_mean["value"])/SEDEMA_monthly_mean["value"]*100
-print("La diferencial relativa promedio es {:.2f}".format(RD.mean()))
+monthly_mean["RD"] = (monthly_mean["OMI"] -
+                      monthly_mean["SEDEMA"])/monthly_mean["SEDEMA"]*100
+monthly_mean.to_csv("{}Monthly_mean_RD.csv".format(parameters["path data"]),
+                    float_format="%.2f")
+print("La diferencial relativa promedio es {:.2f}".format(
+    monthly_mean["RD"].mean()))
 # Inicio del ploteo de los datos
 dates, years = obtain_xticks(parameters["Year initial"],
                              parameters["Year final"])
@@ -182,7 +188,7 @@ plt.xlim(pd.to_datetime(parameters["Year initial"]),
 plt.xticks(dates, years)
 plt.ylim(0, 120)
 plt.yticks([tick for tick in range(0, 120, 10)])
-plt.scatter(RD.index, RD)
+plt.scatter(monthly_mean.index, monthly_mean["RD"])
 plt.grid(ls="--",
          color="#000000",
          alpha=0.5)

### 2021-07-02 Paper_third_version/Article_UV_Mexico.tex
Add changes from reviewer 3

@@
 The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
-meters above sea level (asl), surrounded by mountain ridges exceeding
+meters above sea level (m asl), surrounded by mountain ridges exceeding
 5000 m asl, with complex topography and thermal inversions that inhibit
@@
     \hline
-    Station  & Environment     & Lat (ºN) & Lon (ºW) & El (masl) \\ \hline
+    Station  & Environment     & Lat (°N) & Lon (°W) & El (m asl) \\ \hline
     CHO      & semi-urban      & 19.27    & 98.89    & 2253       \\
@@
 sizes~\(\le\) 10 ~$\mu$m (PM\textsubscript{10}), were downloaded
-from the SIMAT.\cite{pollutants_data} For purposes of assessing the
+from the SIMAT.\cite{atmosfrico} For purposes of assessing the
 influence on the UV Index at solar noon, only values obtained between
@@
 Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
-OMI performs observations over a geographical dimension of 13$\times$24km\textsuperscript{2} at nadir. For
-the coordinates (19.33N, 99.18W) and elevation (2268 masl) of Mexico City,
+OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
+the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
 the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
-Measurements of the ozone profile and cloud cover are used via a
-radiative transfer model to estimate the UVI at the ground.
+Measurements of the ozone profile and the attenuation by clouds are used via a
+radiative transfer model to estimate the UVI at the ground.\cite{Tanskanen_2006}
 The UV Index used for Mexico City corresponds to values at local noon time and clear sky
-from OMUVB Level 2 data product, version 1.3 and collection 3.
+from OMUVB Level 2 OVP data product, version 1.3 and collection 3.
 
@@
 Ultraviolet Visible (TUV v5.3) model.\citep{Madronich_1987} The
-model atmosphere was represented by 80 vertical layers, each 1 km thick,
+model atmosphere is represented by 80 vertical layers, each 1 km thick,
 starting at the 2.24 km asl elevation of MCMA, and for which the first
@@
 (BL).\citep{Shaw_2007} The ozone profile above the BL is from the US
-Standard Atmosphere, but rescaled to a value of 259.6 DU. Totals
+Standard Atmosphere, but rescaled to a value of 259.6 DU. Total ozone columns
 including the BL contributions (of 13.7 DU in the year 2000 and 9.8 DU
-in 2019, see below) were 273.1 DU in 2000 and 269.2 DU. The
+in 2019, see below) were 273.1 DU in 2000 and 269.2 DU in 2019, respectively. The
 climatological O\textsubscript{3} column for this latitude and season is
@@
 
-Above the atmospheric boundary layer, the model was taken to be free of
-aerosols, NO\textsubscript{2}, or SO\textsubscript{2}. In one
+Above the atmospheric boundary layer, the model atmosphere was specified to be,
+NO\textsubscript{2}, or SO\textsubscript{2}. In one
 sensitivity study, a total AOD of 0.7 was redistributed placing 0.2 in
@@
 differed by less than 1\%. Thus, as long as the total AOD is known,
-knowledge of the exact vertical aerosol profile is not critical towards
-ground-level UVI -- but would obviously affect the vertical structure of
+knowledge of the exact vertical aerosol profile is not critical for
+ground-level UVI but would obviously affect the vertical structure of
 photolysis frequencies.
@@
 the UVI for several specific cloud-free days, for different seasons and
-several locations (CHO, MER, MON, PED, SAG, SFE and TLA). UV Index from
-TUV model was used as reference of the behavior under clear sky days.
+several locations (CHO, MER, MON, PED, SAG, SFE and TLA). UV Index calculated with
+the TUV model was used as reference of the behavior during clear sky days.
 According to the comparison of measurements minute by minute, the dates
 with prolonged fluctuations along the day were discarded. However,
-during the rainy period (from June to October) at least a brief clouds
-presence is common, as shown at CHO station around noon in 13 June
+during the rainy period (from June to October) at least a brief episode of clouds,
+as shown at CHO station around noon in 13 June
 2017. Peak values range from 8 during autumn/winter to above 12
@@
 the other stations, and remains in the outskirts. This site is also
-approximately 300 m higher than Mexico City downtown, so that the
-cleaner atmosphere results from both vertical and horizontal variations
-in pollution levels.\citep{aire_cmdx_2017} It is indeed expected to have
+approximately 300 m higher than Mexico City downtown, so that the cleaner atmosphere at SFE
+is a result of the station’s location farther away from pollution sources,
+both horizontally and vertically.\citep{SEDEMA2018a} It is indeed expected to have
 higher values of the UVI, in agreement with the observations.
@@
     \includegraphics[width=0.70\columnwidth]{figures/season}
-    \caption{{UV Index measured over MCMA by SIMAT stations each minute along the day
-          under practically cloudless conditions for representative days of the
-          year.
+    \caption{{UV Index measurements at 1-minute resolution from several SIMAT stations within the MCMA
+          under mostly cloudless conditions for representative days of the year.
             {\label{628947}}%
@@
 The daily maximum UV Index of each station is denoted
-by~\(UVI_{\max}\), all of them were counted in the period 2000-2019.
+by~\(UVI_{\max}\), these values were counted in the period 2000-2019.
 As shown in Figure~{\ref{461017}}, these values ranged
@@
 experienced~\(UVI_{\max}\) values between 6 and 10, and remarkably
-few, less than 1\%, in the higher 13-16 range.~The lowest values are
+few, less than 1\%, in the 13-16 range.~The lowest values are
 likely due to winter days with heavy cloud cover and low sun angles, and
@@
 Fig.~{\ref{461017}}). The lowest average UVI (near 7)
-take place in winter while from March to August the values seem to be
-flattened in the range 10-11. The rather low monthly UV Index values,
-mainly could be a consequence of the presence of clouds in the rainy
+occurs in winter while from March to August the values seem to be
+flattened in the range 10-11. The rather low monthly UV Index values
+could be a consequence of the presence of clouds in the rainy
 season. However, urban aerosol pollution sources, biomass burning for
@@
           dot) in MCMA for the period 2000-2019: median (central bold line),
-          standard deviation (box edges),
-          25\textsuperscript{th} and 75\textsuperscript{th} percentiles (the whiskers),
-          the minimum and maximum  values (plus sign) and the cosine of the solar zenith angle at solar
+          interquartile range (box edges), 10\% and 90\% percentiles (the whiskers),
+          the minimum and maximum values (asterisk) and the cosine of the solar zenith angle at solar
           noon (blue curve).
@@
     \includegraphics[width=0.70\columnwidth]{figures/UV_Moving_Average}
-    \caption{{Moving average function (light gray curve) quarterly applied to monthly
-          average UV Index, standard deviation of all data within a given month
-          (black dots and dash line) and linear fit (red line).
+    \caption{{3-month running average (violet segments curve) applied to monthly
+          average UV Index (black line), the standard deviation (blue fill area) and linear fit (red line).
             {\label{185758}}%
@@
 The UV Index computed from satellite-based observations
-over the period 2005-2019 is mapped in
+over the period 2005-2019 is shown in
 Figure~{\ref{485116}}. The satellite-derived UVIs vary
@@
 are reached in June and July of each year.
-While the early OMI estimates of the UVI did not account for the boundary layer aerosol absorption,
+While early OMI estimates of the UVI did not account for the boundary layer aerosol absorption,
 the current version (1.3) includes the postcorrection by \citet{Arola_2009}
@@
 the June-July time period, estimated by the three methods: OMI
-satellite-derived UVI, RAMA ground-based observations, and TUV modeling
+satellite-derived UVI, SIMAT ground-based observations, and TUV modeling
 using air pollution estimates. Two groups of values can be readily
-identified: (1) RAMA daily record values, OMI with or without BL
+identified: (1) SIMAT daily record values, OMI with or without BL
 aerosols, and TUV for very clean conditions, all with UVI values around
-15-16; and (2) RAMA average daily maxima and TUV UVI using MCMA
-pollutants as input, which are in good agreement for both 2018/19 and
-2000/01 but much lower than the first group. Compared to the OMI
+15-16; and (2) the average of daily maxima of SIMAT observations and TUV UVI results using
+MCMA pollutants as input. Note that SIMAT and TUV values are in good agreement
+for both 2018-2019 and 2000-2001 and are considerably lower than for case (1). Compared to the OMI
 estimate that included the climatological aerosol correction (15.3),
-observed RAMA values were lower by 35\% in 2000 and by 20\% in 2019.
+observed SIMAT values were lower by 35\% in 2000 and by 20\% in 2019.
 Similarly, TUV values were 35\% lower in 2000 and 22\% lower in 2019
@@
     \textbf{Conditions for estimation in June-July} & \textbf{UV Index} \\ \hline
-    RAMA maximum reached in period 2000-2019            & 15.0              \\ \hline
-    RAMA average maxima 2018, 2019                      & 12.3              \\ \hline
-    RAMA average maxima 2000, 2001                      & 9.9               \\ \hline
-    OMI clear, local noon, no corrected for BL aerosols & 16.6              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                          & 16.1              \\ \hline
-    \begin{tabular}[c]{@{}l@{}
-      }TUV pristine pollution \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                          & 15.6              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                          & 12.1              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                          & 10.2              \\ \hline
+    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
+    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
+    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}OMI maximum value reached in period 2005-2019,\\ not corrected for BL aerosols\end{tabular}                      & 16.6              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O3 0 ppb, NO2 0 ppb, SO2 0 ppb\end{tabular}                      & 16.1              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV pristine pollution\\ AOD 0.05, O3 10 ppb, NO2 0 ppb, SO2 0 ppb\end{tabular}                      & 15.6              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O3 50 ppb, NO2 20 ppb, SO2 1 ppb\end{tabular}                      & 12.1              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O3 70 ppb, NO2 40 ppb, SO2 20 ppb\end{tabular}                      & 10.2              \\ \hline
   \end{tabular}
-  \caption{{UV Index monthly maximum estimates for June-July.}}
+  \caption{{UVI maxima for June-July: averages and standard deviation from ground-based data
+        for the years 2018-2019 and 2000-2001. UVI maximum value reached in the period 2000-2019 for
+        UVI ground-based and the same for satellite in the period 2005-2019. TUV calculations for different conditions.
+      }}
   \label{table:TUVmodel}
@@
 
-The agreement between RAMA observations and TUV model estimates is
+The agreement between SIMAT observations and TUV model estimates is
 excellent but also probably a bit fortuitous. Clouds on average reduce
 the irradiance impingent on the surface, but scattering from them can
-also cause transient enhancements (especially if the direct sunbeam is
-not blocked) that could be recorded as daily maxima -- with cancellation
+also cause transient enhancements (these are only possible if the disk of the Sun is visible)
+that could be recorded as daily maxima -- with cancellation
 between these cloud effects resulting in improved agreement with the
@@
 O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}. The
-2000-2019 UVI increase is seen to result in comparable proportions from
-fewer aerosols, less SO\textsubscript{2}, and the combined reductions in
+2000-2019 UVI increase results in comparable proportions from
+less aerosols, less SO\textsubscript{2}, and the combined reductions in
 O\textsubscript{3} and NO\textsubscript{2}.
@@
 surface, while chemical reactions leading to photochemical smog occur
-through the vertical extent of the BL.
+throughout the vertical extent of the BL.
 Figure~{\ref{973680}} shows the vertical profiles of
@@
 An issue that is beginning to gain relevance in radiative balance models
-is the influence of a group of organic compounds capable of strongly
-absorbing in the UV region (brown carbon).\citep{Laskin_2015} Some of
-these compounds are related with emissions from local and regional
+is the influence of a group of organic compounds known as “brown carbon” that are
+capable of strongly absorbing in the UV region.\citep{Laskin_2015} Some of
+these compounds are related to emissions from local and regional
 wildfires.\citep{Gadhavi_2010} Mexico City is frequently exposed to
 regional fire smoke transport during the dry part of the year (November
-to May)\citep{Rios_2019}, that sporadically modify the optical
+to May)\citep{Rios_2019}, which sporadically modify the optical
 properties of the aerosols.\citep{Barnard_2008} This could partly explain
@@
 (\textless{}420 nm). Absorption by SO\textsubscript{2} and
-O\textsubscript{3} vanishes, while absorption by NO\textsubscript{2}
-increases and typical aerosols optical depth decrease. These changes can
+O\textsubscript{3} vanishes for wavelengths larger than about 330 nm,
+while NO\textsubscript{2} photolysis is mostly driven by UV-A radiation
+and typical aerosols optical depth decrease with wavelength. These changes can
 easily be modeled, but unfortunately far fewer measurements of these
@@
 the satellite has a limitation to seeing boundary layer absorbers.
-When typical values of the pollutants (aerosols,
+When typical values of the pollutants: aerosols,
 tropospheric ozone, and to a lesser extent NO\textsubscript{2}
-and SO\textsubscript{2}), are included in a model (e.g. TUV), the
+and SO\textsubscript{2}, are included in a model (e.g. TUV), the
 differences between satellite-derived and ground-based measured values
 are explained and can be attributed quantitatively to individual
-observed pollutants. Long term improvements in air quality, over two
-decades, are accompanied by statistically significant increases in the
+observed pollutants. Long term improvements in air quality over the last two decades,
+are accompanied by statistically significant increases in the
 observed UVI, again in good agreement with the model-predicted changes.
@@
     \hline
-    \multicolumn{1}{c}{\multirow{2}{*}{Pollutant}} & \multicolumn{2}{c}{Year 2000} & \multicolumn{2}{c}{Year 2019} & 2019-2000                 \\ \cline{2-6}
+    \multicolumn{1}{c}{\multirow{2}{*}{Pollutant}} & \multicolumn{2}{c}{Year 2000} & \multicolumn{2}{c}{Year 2019} & 2000-2019                 \\ \cline{2-6}
     \multicolumn{1}{c}{}                           & poll. level (a)               & UVI (b)                       & poll. level & UVI   & (c) \\ \hline
@@
 and other UV-related health effects. The efforts that Mexico City has
-made to improve air quality have achieved positive results in the levels
+made to improve air quality have reduced levels
 of most air pollutants. Nevertheless, they caused an increase in UV
@@
 Finally, based on our results, the solar radiation monitoring network could be
-improved by adding observation sites within or close to the basin, with minor
-influences of the urban plume (e. g., Amecameca; latitude: 19.13ºN, longitude: 99.76ºW, elevation: 2420 m asl),
+improved by adding observation sites within or close to the Valley of Mexico, with minor
+influences of the urban plume (e. g., Amecameca; latitude: 19.13°N, longitude: 99.76°W, elevation: 2420 m asl),
 and the complementing of sensors in existing monitoring sites that are at elevations above the urban boundary

### 2021-07-02 Scripts/Calculate_RD_between_OMI_and_measurements.py
Add labels and Monthly mean RD graphics

@@ -146,6 +146,7 @@ parameters = {
                    "UVB": 0.0583*40, },
     "Year initial": "2005-01-01",
     "Year final": "2019-12-31",
+    "fontsize": 14,
 }
 # Lectura de los datos de OMI
 OMI_data = read_OMI_data(parameters["path data"],
@@ -179,17 +180,25 @@ print("La diferencial relativa promedio es {:.2f}".format(
 dates, years = obtain_xticks(parameters["Year initial"],
                              parameters["Year final"])
 plt.figure(figsize=(10, 4))
-plt.subplots_adjust(left=0.055,
-                    bottom=0.09,
+plt.subplots_adjust(left=0.085,
+                    bottom=0.13,
                     right=0.971,
                     top=0.926)
+plt.xlabel("Years",
+           fontsize=parameters["fontsize"])
 plt.xlim(pd.to_datetime(parameters["Year initial"]),
          pd.to_datetime(parameters["Year final"]))
-plt.xticks(dates, years)
+plt.xticks(dates, years,
+           fontsize=parameters["fontsize"])
+plt.ylabel("Percentage difference",
+           fontsize=parameters["fontsize"])
 plt.ylim(0, 120)
-plt.yticks([tick for tick in range(0, 120, 10)])
-plt.scatter(monthly_mean.index, monthly_mean["RD"])
+plt.yticks([tick for tick in range(0, 120, 10)],
+           fontsize=parameters["fontsize"])
+plt.scatter(monthly_mean.index, monthly_mean["RD"],
+            c="#9D2449")
 plt.grid(ls="--",
          color="#000000",
          alpha=0.5)
-plt.show()
+plt.savefig("{}Monthly_mean_RD.png".format(parameters["path graphics"]),
+            dpi=400)

### 2021-07-02 Scripts/Calculate_RD_between_OMI_and_measurements.py
Refractor - Change functions to use class on SEDEMA and OMI

@@ -1,129 +1,7 @@
 import matplotlib.pyplot as plt
+from Class_list import *
 import pandas as pd
 import os
-
-
-def read_OMI_data(path="", name=""):
-    """
-    Lectura de los datos de OMI
-    #### inputs
-    path -> direccion donde se encuentran los datos
-
-    name -> nombre del archivo
-    """
-    # Lectura cruda de los datos
-    data = pd.read_csv("{}UVI_{}.csv".format(path,
-                                             name),
-                       index_col=0)
-    # Formato de fecha a los datos
-    data = format_data(data)
-    return data
-
-
-def format_data(data=pd.DataFrame()):
-    """
-    Formato de fecha en el indice del dataframe
-    """
-    data.index = pd.to_datetime(data.index)
-    return data
-
-
-def obtain_monthly_mean(data=pd.DataFrame()):
-    """
-    Calculo del promedio mensual a partir de un dataframe
-    """
-    return data.resample("MS").mean()
-
-
-def read_SEDEMA_data(path="", resize=1):
-    """
-    Lectura de los datos de la SEDEMA
-    #### inputs
-    path -> direccion donde se encuentran los datos
-
-    resize -> valor para convertir los datos a UVI
-    """
-    # Listado de los archivos de la SEDEMA
-    files = sorted(os.listdir(path))
-    # Seleccionar unicamente los de UVB
-    files = select_SEDEMA_files(files=files,
-                                type_name="UVB")
-    # Ciclo para reunir todos los archivos en un solo dataframe
-    for i, file in enumerate(files):
-        if i == 0:
-            # Lectura de los datos de la SEDEMA
-            data = read_SEDEMA_data_each_file(path,
-                                              file)
-        else:
-            # Lectura de los datos de la SEDEMA
-            data_year = read_SEDEMA_data_each_file(path,
-                                                   file)
-            # Union de todos los dataframe en uno solo
-            data = data.append(data_year)
-    # Obtener el máximo diario de todas las estaciones
-    data = obtain_daily_maximum(data)
-    # Redimensionar los datos UVI
-    data["value"] = data["value"]*resize
-    return data
-
-
-def select_SEDEMA_files(files=[], type_name=""):
-    """
-    Descarta los archivos dependiendo si contienen un nombre en especifico
-    #### inputs
[…]

### 2021-07-02 Scripts/Class_list.py

@@ -1,0 +1,110 @@
+from Functions import *
+import pandas as pd
+import os
+
+
+class OMI_data_set:
+    def __init__(self, path="", name=""):
+        self.path = path
+        self.name = name
+        self.read_data()
+
+    def read_data(self):
+        """
+        Lectura de los datos de OMI
+        #### inputs
+        path -> direccion donde se encuentran los datos
+
+        name -> nombre del archivo
+        """
+        # Lectura cruda de los datos
+        data = pd.read_csv("{}UVI_{}.csv".format(self.path,
+                                                 self.name),
+                           index_col=0)
+        # Formato de fecha a los datos
+        self.data = self.format_data(data)
+
+    def format_data(self, data=pd.DataFrame()):
+        """
+        Formato de fecha en el indice del dataframe
+        """
+        data.index = pd.to_datetime(data.index)
+        return data
+
+
+class SEDEMA_data_set:
+    def __init__(self, path="", type_name="UVB"):
+        self.path = path
+        self.type = type_name
+        self.resize = {"UVA": 10,
+                       "UVB": 0.0583*40, }
+        self.resize = self.resize[type_name]
+        self.read_data()
+
+    def read_data(self):
+        """
+        Lectura de los datos de la SEDEMA
+        #### inputs
+        path -> direccion donde se encuentran los datos
+
+        resize -> valor para convertir los datos a UVI
+        """
+        # Listado de los archivos de la SEDEMA
+        files = sorted(os.listdir(self.path))
+        # Seleccionar unicamente los de UVB
+        files = self.select_files(files=files)
+        # Ciclo para reunir todos los archivos en un solo dataframe
+        for i, file in enumerate(files):
+            if i == 0:
+                # Lectura de los datos de la SEDEMA
+                data = self.read_data_each_file(self.path,
+                                                file)
+            else:
+                # Lectura de los datos de la SEDEMA
+                data_year = self.read_data_each_file(self.path,
+                                                     file)
+                # Union de todos los dataframe en uno solo
+                data = data.append(data_year)
+        # Obtener el máximo diario de todas las estaciones
+        self.data = obtain_daily_maximum(data)
+        # Redimensionar los datos UVI
+        self.data["value"] = self.data["value"]*self.resize
+        return data
+
+    def select_files(self, files=[]):
+        """
+        Descarta los archivos dependiendo si contienen un nombre en especifico
+        #### inputs
+        files -> listado de los archivos sin filtrar
+        """
+        files_type = []
[…]

### 2021-07-02 Scripts/Functions.py

@@ -1,5 +1,6 @@
 from matplotlib.colors import LinearSegmentedColormap
 import matplotlib.pyplot as plt
+import pandas as pd
 import datetime
 import locale
 import os
@@ -96,3 +97,26 @@ def colormap_UVI():
                                            colors,
                                            N=n_bin)
     return cm
+
+
+def obtain_monthly_mean(data=pd.DataFrame()):
+    """
+    Calculo del promedio mensual a partir de un dataframe
+    """
+    return data.resample("MS").mean()
+
+
+def obtain_daily_maximum(data=pd.DataFrame()):
+    """
+    Calculo del promedio maximo diario
+    """
+    return data.resample("D").max()
+
+
+def select_data(data=pd.DataFrame(), date_initial="2005-01-01", date_final="2019-12-31"):
+    """
+    Selecciona los datos que se encuentran dentro de un periodo
+    """
+    data = data[data.index >= date_initial]
+    data = data[data.index <= date_final]
+    return data

### 2021-07-02 Scripts/Calculate_RD_between_OMI_and_measurements.py
Refractor - Change functions to use class on SEDEMA and OMI

@@ -39,6 +39,7 @@ monthly_mean["OMI"] = OMI_monthly_mean["CSUVindex"]
 # Lectura de los datoa de SEDEMA
 SEDEMA_data = SEDEMA_data_set(path=parameters["path SEDEMA data"],
                               type_name=parameters["wavelength"])
+SEDEMA_data.data = obtain_daily_maximum(SEDEMA_data.data)
 # Calculo del promedio mensual
 SEDEMA_monthly_mean = obtain_monthly_mean(SEDEMA_data.data)
 # Seleccionar datos que estan dentro del periodo

### 2021-07-02 Scripts/Calculate_daily_mean_per_hour.py

@@ -1,78 +1,34 @@
-import pandas as pd
-import os
+from Class_list import *
 
 
-def select_files(files, type_name):
-    files_type = []
-    for file in files:
-        if type_name in file:
-            files_type.append(file)
-    return files_type
-
-
-def read_data(path, name):
-    data = pd.read_csv("{}{}".format(path,
-                                     name),
-                       index_col=0)
-    data = format_date_data(data)
+def select_data(data=pd.DataFrame(), parameters={}):
+    data = data[data.index.hour >= parameters["Hour initial"]]
+    data = data[data.index.hour <= parameters["Hour final"]]
+    data = data[data.index.year >= parameters["Year initial"]]
+    data = data[data.index.year <= parameters["Year final"]]
+    data = data[data.index.month >= parameters["Month initial"]]
+    data = data[data.index.month <= parameters["Month final"]]
+    data = obtain_daily_maximum(data)
     return data
 
 
-def format_date_data(data):
-    data.index = pd.to_datetime(data.index)
-    data = data.drop(["parameter",
-                      "unit",
-                      "cve_station"],
-                     1)
-    return data
-
-
-def format_results(data, resize):
-    data = data*resize
-    data = data.round({
-        "value": 2,
-        "std": 4,
-    })
-    return data
-
-
-inputs = {
+parameters = {
     "path data": "../Data/SEDEMA_Data/Radiation/",
     "path results": "../Data/",
-    "wavelength": {"UVA": 10,
-                   "UVB": 0.0583*40, },
+    "wavelength": "UVB",
     "Hour initial": 11,
     "Hour final": 15,
     "Month initial": 6,
     "Month final": 7,
-    "Year initial": 2018,
-    "Year final": 2019,
+    "Year initial": 2000,
+    "Year final": 2001,
 }
-files = sorted(os.listdir(inputs["path data"]))
-for wavelength in inputs["wavelength"]:
-    print("Analizando {} en el periodo {}-{}".format(wavelength,
-                                                     inputs["Year initial"],
-                                                     inputs["Year final"]))
-    resize = inputs["wavelength"][wavelength]
-    files_type = select_files(files,
-                              wavelength)
-    for i, file in enumerate(files_type):
-        if i == 0:
-            data_all = read_data(inputs["path data"],
-                                 file)
-        else:
-            data = read_data(inputs["path data"],
-                             file)
[…]

### 2021-07-02 Scripts/Class_list.py

@@ -57,19 +57,16 @@ class SEDEMA_data_set:
         for i, file in enumerate(files):
             if i == 0:
                 # Lectura de los datos de la SEDEMA
-                data = self.read_data_each_file(self.path,
-                                                file)
+                self.data = self.read_data_each_file(self.path,
+                                                     file)
             else:
                 # Lectura de los datos de la SEDEMA
                 data_year = self.read_data_each_file(self.path,
                                                      file)
                 # Union de todos los dataframe en uno solo
-                data = data.append(data_year)
-        # Obtener el máximo diario de todas las estaciones
-        self.data = obtain_daily_maximum(data)
+                self.data = self.data.append(data_year)
         # Redimensionar los datos UVI
         self.data["value"] = self.data["value"]*self.resize
-        return data
 
     def select_files(self, files=[]):
         """

### 2021-07-04 Scripts/Calculate_RD_between_OMI_and_measurements.py
Delete useless imports

@@ -1,7 +1,5 @@
 import matplotlib.pyplot as plt
 from Class_list import *
-import pandas as pd
-import os
 
 
 def obtain_xticks(date_initial="2005-01-01", date_final="2019-12-31"):

### 2021-07-06 Paper_third_version/Article_UV_Mexico.tex
Add Madronich references

@@
 \usepackage{lineno}
+\usepackage{achemso}
+\setkeys{acs}{maxauthors=20}
+\setkeys{acs}{etalmode=truncate}
 \usepackage[colorlinks = true,
@@
 reductions in photochemical smog, in part due to stronger UV
-photochemistry.\citep{Wang_2019,Gao_2020,Ma_2020}
+photochemistry.\citep{Wang_2019,Gao_2020,Ma_2021}
 Emission reductions have also occurred
@@
 Organizations (WHO and WMO) as a standardized metric of UV
-radiation\cite{who2002} for global public information. An advantage
+radiation\citep{who2002} for global public information. An advantage
 of using the UVI as (one) measure of UV radiation is that it is being
@@
 sizes~\(\le\) 10 ~$\mu$m (PM\textsubscript{10}), were downloaded
-from the SIMAT.\cite{atmosfrico} For purposes of assessing the
+from the SIMAT.\cite{pollutants_data} For purposes of assessing the
 influence on the UV Index at solar noon, only values obtained between
@@
 Product Level 2.0 and 1.5 (only in 2019) were selected, and annual
-averages AOD\textsubscript{340} were calculated along the period 2000-2019,
-except for the year 2011 due to there were no measurements. A previous study of the AOD
-behavior from 2000 to 2014 demonstrated that data gaps did not
+averages AOD\textsubscript{340} were calculated for the period 2000-2019,
+except for the year 2011 which contained large data gaps and was therefore not used.
+A previous study of the AOD behavior from 2000 to 2014 demonstrated that data gaps did not
 significantly change the trends calculated for this.\citep{Carabali_2017}
@@
 
-The UV Index data derived from satellite measurements of reflected radiance
-were used for comparison with the ground-based measurements.
+The UV Index data derived from satellite-based measurements
+were used for comparing to the ground-based measurements.
 These data were provided by the Ozone Monitoring
@@
 the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
-Measurements of the ozone profile and the attenuation by clouds are used via a
-radiative transfer model to estimate the UVI at the ground.\cite{Tanskanen_2006}
+The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths.
+The ozone column is estimated by differential absorption of several adjacent wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006} while clouds are estimated from the reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm, \citet{Tanskanen_2007}).
+A correction for absorbing aerosols is made using a global aerosol climatology\citep{Arola_2009}.
 The UV Index used for Mexico City corresponds to values at local noon time and clear sky
@@
 Figure~{\ref{485116}}. The satellite-derived UVIs vary
-from 8 in winter to 16 in summer, both values being substantially higher
+from 8 in winter to 16 in summer, these values being substantially higher
 than the ground-based observations (ca. 7 for winter and 11 for summer,
-see Fig.~{\ref{310112}}). We hypothesize that this
+see Fig.~{\ref{310112}}). For both datasets the maximum values
+are reached in June and July of each year. We hypothesize that this
 large difference between satellite-based estimation and ground-based
@@
 Mexico City.~A rather similar behavior was detected in Santiago city,
-Chile.\citep{Cabrera_2012}
-
-Close inspection of Figure~{\ref{485116}} shows that the maximum values
-are reached in June and July of each year.
-While early OMI estimates of the UVI did not account for the boundary layer aerosol absorption,
-the current version (1.3) includes the postcorrection by \citet{Arola_2009}
-for absorbing aerosols based on global monthly aerosol climatology.
+Chile.\citep{Cabrera_2012} Although the OMI data are corrected for climatological aerosol absorption\citep{Arola_2009}, this correction likely underestimates the absorption within the polluted Mexico City BL.
 
@@
     \begin{tabular}[c]{@{}l@{}}OMI maximum value reached in period 2005-2019,\\ not corrected for BL aerosols\end{tabular}                      & 16.6              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O3 0 ppb, NO2 0 ppb, SO2 0 ppb\end{tabular}                      & 16.1              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV pristine pollution\\ AOD 0.05, O3 10 ppb, NO2 0 ppb, SO2 0 ppb\end{tabular}                      & 15.6              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O3 50 ppb, NO2 20 ppb, SO2 1 ppb\end{tabular}                      & 12.1              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O3 70 ppb, NO2 40 ppb, SO2 20 ppb\end{tabular}                      & 10.2              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV pristine pollution\\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
   \end{tabular}
@@
 Figure~{\ref{973680}} shows the vertical profiles of
-photolysis coefficients (the reciprocals of photolytic lifetimes) for
+photolysis coefficients (the reciprocals of photolytic lifetimes) computed with the TUV model, for
 two key reactions, the photolysis of O\textsubscript{3} to yield excited
@@
 that air pollution reduces UV radiation at the ground. The ground-based
-observations are well below data derived from satellite-based
+observations are well below values derived from satellite-based
 observations. Although ideally both data sets should match,
@@
 (b) UVI deviation from the zero-pollution value of 16.1 (from Table \ref{table:TUVmodel}).
-(c) 2019-2000 UVI change due to changes in each pollutant.}
+(c) 2000-2019 UVI change due to changes in each pollutant.}
   \label{table:year2000-2019}
@@
 radiation that reaches the surface.
-
-A limitation of the present work is our focus on daily maximum values,
-which largely exclude cloud cover. Absorption within clouds can be
-enhanced by the long path lengths of multiply scattered photons, so that accurate quantification of UV
-effects of clouds in polluted environments remains a significant
-challenge and interesting opportunity for future work.
 

### 2021-07-07 Paper_third_version/Article_UV_Mexico.tex
Change table  4 and add figure 8

@@
 \usepackage{lineno}
-\usepackage{achemso}
-\setkeys{acs}{maxauthors=20}
-\setkeys{acs}{etalmode=truncate}
 \usepackage[colorlinks = true,
@@
 radiation. Unfortunately, the observational data base of relevant UV
-radiation remains rather sparse to evaluate such model-derived
-hypotheses.~~
+radiation remains rather sparse to evaluate such model-predicted feedbacks between chemistry and radiation.~~
 
@@
 The UVI is recognized by the World Health and Meteorological
-Organizations (WHO and WMO) as a standardized metric of UV
-radiation\citep{who2002} for global public information. An advantage
+Organizations (WHO and WMO) as a standardized measure of UV
+radiation\cite{who2002} for global public information. An advantage
 of using the UVI as (one) measure of UV radiation is that it is being
@@
 The UV Index data derived from satellite-based measurements
-were used for comparing to the ground-based measurements.
+were used for comparison with the ground-based measurements.
 These data were provided by the Ozone Monitoring
@@
 The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths.
-The ozone column is estimated by differential absorption of several adjacent wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006} while clouds are estimated from the reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm, \citet{Tanskanen_2007}).
-A correction for absorbing aerosols is made using a global aerosol climatology\citep{Arola_2009}.
+The ozone column is estimated by differential absorption of several adjacent
+wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, while clouds are estimated from the reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm, \citet{Tanskanen_2007}).
+A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
 The UV Index used for Mexico City corresponds to values at local noon time and clear sky
@@
 knowledge of the exact vertical aerosol profile is not critical for
-ground-level UVI but would obviously affect the vertical structure of
+ground-level UVI, but would obviously affect the vertical structure of
 photolysis frequencies.
@@
 than the ground-based observations (ca. 7 for winter and 11 for summer,
-see Fig.~{\ref{310112}}). For both datasets the maximum values
-are reached in June and July of each year. We hypothesize that this
-large difference between satellite-based estimation and ground-based
+see Fig.~{\ref{310112}}). The maximum values are reached in June and July of each year for both data sets.
+We hypothesize that this large difference between satellite-based estimation and ground-based
 observation of the UV index is due to the intense air pollution of
@@
     SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}OMI maximum value reached in period 2005-2019,\\ not corrected for BL aerosols\end{tabular}                      & 16.6              \\ \hline
+    OMI maximum value reached in period 2005-2019   & 16.6              \\ \hline
     \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV pristine pollution\\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
+    \begin{tabular}[c]{@{}l@{}
+      }TUV pristine pollution \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
     \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
@@
         for the years 2018-2019 and 2000-2001. UVI maximum value reached in the period 2000-2019 for
-        UVI ground-based and the same for satellite in the period 2005-2019. TUV calculations for different conditions.
+        UVI ground-based and the same for satellite in the period 2005-2019. TUV calculations for specified conditions.
       }}
@@
 
-Table~{\ref{table:year2000-2019}} shows the
-contributions to UVI reductions from individual pollutants. Aerosols are
-seen to be the major factor in both time periods, followed by
-O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}. The
-2000-2019 UVI increase results in comparable proportions from
-less aerosols, less SO\textsubscript{2}, and the combined reductions in
-O\textsubscript{3} and NO\textsubscript{2}.
+Table~{\ref{table:year2000-2019}} shows the contribution of different pollutants
+to the UVI increase between 2000 and 2019, computed with the TUV model.
+The year 2000 was taken as the base case, and each pollutant was decreased
+to its 2019 value individually while the others were maintained at their 2000 value.
+Decreasing aerosol AOD has been the largest driver of the UVI changes,
+but the absorption by gaseous pollutants has also decreased significantly.
+Additional future reductions in AOD, NO\textsubscript{2}, and O\textsubscript{3} could increase the
+UVI further, while the low SO\textsubscript{2} levels reached by 2019 are expected
+to have negligible effects in the UVI.
 
-Comparable UV reductions, of 30-40\% due to aerosols, were reported by
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
+  \caption{The percentage relative difference (\% RD) of the satellite and ground-based monthly means UVI for the period 2005-2019.}
+  \label{fig:percentage_relative_difference}
+\end{figure}
+
+Figure \ref{fig:percentage_relative_difference} shows the percentage relative difference between monthly means
+satellite-based and ground-based data with respect to the last one. The mean percentage relative difference
+was 35\% in the period 2005-2019. Comparable UV reductions, of 30-40\% due to aerosols, were reported by
 \citet{Panicker_2009} over Pune, India from April 2004 to
@@
   \centering
-  \begin{tabular}{lccccc}
+  \begin{tabular}{cc}
     \hline
-    \multicolumn{1}{c}{\multirow{2}{*}{Pollutant}} & \multicolumn{2}{c}{Year 2000} & \multicolumn{2}{c}{Year 2019} & 2000-2019                 \\ \cline{2-6}
-    \multicolumn{1}{c}{}                           & poll. level (a)               & UVI (b)                       & poll. level & UVI   & (c) \\ \hline
-    AOD                                            & 0.7                           & -3.7                          & 0.5         & -2.7  & 1.0 \\
-    O\textsubscript{3} ppb (DU)                    & 70 (14)                       & -1.4                          & 50 (10)     & -1.0  & 0.4 \\
-    NO\textsubscript{2} ppb                        & 40                            & -0.9                          & 20          & -0.5  & 0.4 \\
-    SO\textsubscript{2} ppb                        & 30                            & -0.8                          & 1           & -0.04 & 0.8 \\ \hline
+    Pollutant & UVI Change\\ \hline
+    AOD & 0.8\\
+    O\textsubscript{3} & 0.4\\
+    NO\textsubscript{2} & 0.4\\ 
+    SO\textsubscript{2} & 0.5 \\ \hline
   \end{tabular}
-  \caption{Contributions of individual pollutants to UV Index changes.
-(a) Values used one at the time, with the others held at zero.
-(b) UVI deviation from the zero-pollution value of 16.1 (from Table \ref{table:TUVmodel}).
-(c) 2000-2019 UVI change due to changes in each pollutant.}
+  \caption{Contributions of individual pollutants to the 2000-2019 UV Index changes.
+Baseline calculation for 2000 conditions (AOD = 0.7, O\textsubscript{3} = 70 ppb, NO\textsubscript{2} = 40 ppb, SO\textsubscript{2} = 20 ppb).
+Individual pollutant contributions are estimated by adjusting each pollutant, one at the time, to its 2019 value (AOD = 0.5, O\textsubscript{3} = 50 ppb, NO\textsubscript{2} = 20 ppb, SO\textsubscript{2} = 1 ppb), while maintaining the others at their 2000 value.}
   \label{table:year2000-2019}

### 2021-07-07 Scripts/Calculate_RD_between_OMI_and_measurements.py
Add references limit and change ylabel of RD OMI vs measurements

@@ -66,7 +66,7 @@ plt.xlim(pd.to_datetime(parameters["Year initial"]),
          pd.to_datetime(parameters["Year final"]))
 plt.xticks(dates, years,
            fontsize=parameters["fontsize"])
-plt.ylabel("Percentage difference",
+plt.ylabel("Percentage relative difference (%)",
            fontsize=parameters["fontsize"])
 plt.ylim(0, 120)
 plt.yticks([tick for tick in range(0, 120, 10)],

### 2021-07-12 Scripts/Calculate_RD_between_OMI_and_measurements.py
Change on ylabel

@@ -66,7 +66,7 @@ plt.xlim(pd.to_datetime(parameters["Year initial"]),
          pd.to_datetime(parameters["Year final"]))
 plt.xticks(dates, years,
            fontsize=parameters["fontsize"])
-plt.ylabel("Percentage relative difference (%)",
+plt.ylabel("Deviation (%)",
            fontsize=parameters["fontsize"])
 plt.ylim(0, 120)
 plt.yticks([tick for tick in range(0, 120, 10)],

### 2021-07-12 Scripts/Graphics_daily_maximum_per_month.py
Change name and add path graphics to the format

@@ -1,0 +1,90 @@
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+import datetime
+import os
+
+
+def format_data(data, resize):
+    data.index = pd.to_datetime(data["Dates"])
+    data = data.drop(["Dates", "parameter", "unit"], 1)
+    data["value"] = data["value"]*resize*40
+    return data
+
+
+colors = {
+    "CHO": "Blue",
+    "CUA": "#03071e",
+    "CUT": "#83c5be",
+    "FAC":  "#d00000",
+    "HAN": "#b07d62",
+    "LAA": "#f72585",
+    "MER": "black",
+    "MON": "Purple",
+    "MPA": "#0096c7",
+    "PED": "#f89edf",
+    "SAG": "orange",
+    "SFE": "Green",
+    "TLA": "cyan",
+}
+for month in range(1, 13):
+    inputs = {
+        "path data": "../Data/SEDEMA_Data/Radiation/",
+        "path stations": "../Stations/",
+        "path graphics": "../Graphics/Daily_maximum/",
+        "radiation": "UVB",
+        "size": 0.0583,
+        "year": "2019",
+        "day initial": "2019-"+str(month).zfill(2)+"-01",
+        "day final": "2019-"+str(month+1).zfill(2)+"-01",
+
+    }
+    if month == 12:
+        inputs["day final"] = "2019-12-31"
+    file = inputs["radiation"]+"_"+inputs["year"]+".csv"
+    stations = sorted(os.listdir(inputs["path stations"]))
+    data = pd.read_csv(inputs["path data"]+file)
+    data = format_data(data,
+                       inputs["size"])
+    index = data.resample("D").max()
+    daily_max = pd.DataFrame(columns=stations,
+                             index=index.index)
+    for station in stations:
+        data_max = data[data["cve_station"] == station]
+        data_max = data_max[data_max.index.hour >= 11]
+        data_max = data_max[data_max.index.hour <= 15]
+        data_max = data_max.resample("D").max()
+        daily_max[station] = data_max["value"]
+    data_max = daily_max[daily_max.index <= inputs["day final"]]
+    data_max = data_max[data_max.index >= inputs["day initial"]]
+    for station in stations:
+        data = data_max[station]
+        if data.count() != 0:
+            plt.plot(data,
+                     label=station,
+                     ls="--",
+                     marker="o",
+                     color=colors[station])
+    plt.legend(ncol=5,
+               frameon=False,
[…]

### 2021-07-12 Scripts/Graphics_cloud.py
Delete useless files

@@ -1,79 +1,0 @@
-import matplotlib.pyplot as plt
-from functions import *
-import pandas as pd
-import numpy as np
-import datetime
-inputs = {
-    "path data": "../Data/",
-    "file data": "Cloud_factor.csv",
-    "year initial": 2005,
-    "year final": 2019,
-    "column": "Cld. F.",
-}
-print("Leyendo datos de Cloud Factor")
-cloud_map = np.zeros([inputs["year final"]-inputs["year initial"]+1,
-                      365])
-data = pd.read_csv(inputs["path data"]+inputs["file data"], index_col=0)
-data.index = pd.to_datetime(data.index)
-monthly_mean = data.resample("MS").mean()
-month_names = obtain_month_names()
-numyear = ["2005",
-           "",
-           "",
-           "2008",
-           "",
-           "",
-           "",
-           "2012",
-           "",
-           "",
-           "",
-           "2016",
-           "",
-           "",
-           "2019"]
-for year in range(inputs["year initial"], inputs["year final"]+1):
-    year_i = year-inputs["year initial"]
-    for day in range(365):
-        date = datetime.date(year, 1, 1)+datetime.timedelta(days=day)
-        try:
-            value = (data[inputs["column"]][str(date)]).mean()
-            cloud_map[year_i, day] = value
-        except:
-            month = date.month
-            date = datetime.date(year, month, 1)
-            value = monthly_mean[inputs["column"]][str(date)]
-            cloud_map[year_i, day] = value
-daysnum = np.arange(0, 365, 30.5)
-year = np.arange(inputs["year final"]-inputs["year initial"]+1)
-fig, ax = plt.subplots(1, 1)
-plt.subplots_adjust(left=0.11,
-                    right=0.97,
-                    bottom=0.20,
-                    top=0.94)
-map = ax.imshow(cloud_map,
-                interpolation="bessel",
-                cmap="coolwarm",
-                origin="lower")
-forceAspect(ax, 1.2)
-ax.set_title("Period 2005-2019",
-             fontsize="large")
-ax.set_yticks(year-0.5)
-ax.set_yticklabels(numyear,
-                   fontsize="large")
-ax.set_xticks(daysnum)
-ax.set_xticklabels(month_names,
-                   rotation=60,
-                   fontsize="large")
-ax.grid(linewidth=1,
-        color="black",
-        linestyle="--")
-cbar = fig.colorbar(map,
[…]

### 2021-07-12 Scripts/Graphics_daily_maximum.py

@@ -1,89 +1,0 @@
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import datetime
-import os
-
-
-def format_data(data, resize):
-    data.index = pd.to_datetime(data["Dates"])
-    data = data.drop(["Dates", "parameter", "unit"], 1)
-    data["value"] = data["value"]*resize*40
-    return data
-
-
-colors = {
-    "CHO": "Blue",
-    "CUA": "#03071e",
-    "CUT": "#83c5be",
-    "FAC":  "#d00000",
-    "HAN": "#b07d62",
-    "LAA": "#f72585",
-    "MER": "black",
-    "MON": "Purple",
-    "MPA": "#0096c7",
-    "PED": "#f89edf",
-    "SAG": "orange",
-    "SFE": "Green",
-    "TLA": "cyan",
-}
-for month in range(1, 13):
-    inputs = {
-        "path data": "../Data/SEDEMA_Data/Radiation/",
-        "path stations": "../Stations/",
-        "path graphics": "../Graphics/Daily_maximum/",
-        "radiation": "UVB",
-        "size": 0.0583,
-        "year": "2019",
-        "day initial": "2019-"+str(month).zfill(2)+"-01",
-        "day final": "2019-"+str(month+1).zfill(2)+"-01",
-
-    }
-    if month == 12:
-        inputs["day final"] = "2019-12-31"
-    file = inputs["radiation"]+"_"+inputs["year"]+".csv"
-    stations = sorted(os.listdir(inputs["path stations"]))
-    data = pd.read_csv(inputs["path data"]+file)
-    data = format_data(data,
-                       inputs["size"])
-    index = data.resample("D").max()
-    daily_max = pd.DataFrame(columns=stations,
-                             index=index.index)
-    for station in stations:
-        data_max = data[data["cve_station"] == station]
-        data_max = data_max[data_max.index.hour >= 11]
-        data_max = data_max[data_max.index.hour <= 15]
-        data_max = data_max.resample("D").max()
-        daily_max[station] = data_max["value"]
-    data_max = daily_max[daily_max.index <= inputs["day final"]]
-    data_max = data_max[data_max.index >= inputs["day initial"]]
-    for station in stations:
-        data = data_max[station]
-        if data.count() != 0:
-            plt.plot(data,
-                     label=station,
-                     ls="--",
-                     marker="o",
-                     color=colors[station])
-    plt.legend(ncol=5,
[…]

### 2021-07-12 Scripts/Graphics_days.py

@@ -1,53 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-import os
-
-inputs = {
-    "path stations": "../Stations/",
-    "date": "190803",
-}
-colors = {
-    "CHO": "Blue",
-    "CUA": "#03071e",
-    "CUT": "#6a040f",
-    "FAC":  "#d00000",
-    "HAN": "#b07d62",
-    "LAA": "#7400b8",
-    "MER": "black",
-    "MON": "Purple",
-    "MPA": "#0096c7",
-    "PED": "#f89edf",
-    "SAG": "orange",
-    "SFE": "Green",
-    "TLA": "#52b788",
-}
-stations = sorted(os.listdir(inputs["path stations"]))
-for station in stations:
-    path = inputs["path stations"]+station+"/Erythemal/"
-    try:
-        hour, data = np.loadtxt(path+inputs["date"]+".txt",
-                                unpack=True)
-        if np.mean(data) != 0:
-            color = colors[station]
-            plt.plot(hour, data*40,
-                     label=station,
-                     marker="o",
-                     color=color)
-    except:
-        pass
-plt.text(12, 17, "3 august 2019", fontsize=12)
-plt.ylabel("UV Index")
-plt.xlabel("Local time (h)")
-plt.xlim(5, 20)
-plt.ylim(0, 16)
-plt.yticks(np.arange(0, 17))
-plt.xticks(np.arange(5, 21))
-plt.grid(ls="--",
-         color="#000000",
-         alpha=0.5)
-plt.legend(frameon=False,
-           ncol=8,
-           fontsize=8,
-           bbox_to_anchor=(1.04, 1.01, 0.05, 0.05)
-           )
-plt.show()

### 2021-07-12 Scripts/Read_cloud_data.py
Change to use format string

@@ -1,28 +1,0 @@
-import pandas as pd
-
-
-def date_format(data):
-    data["Date"] = data["Datetime"].str[0:4]+"-" + \
-        data["Datetime"].str[4:6]+"-"+data["Datetime"].str[6:8]
-    data["Date"] = pd.to_datetime(data["Date"])
-    data.index = data["Date"]
-    data = data.drop(["Date", "Datetime"], 1)
-
-
-inputs = {
-    "path data": "../Data/",
-    "file data": "Data_OMI_",
-    "product": "OMTO3",
-    "skiprows": 27,
-    "column": "Cld. F.",
-    "file results": "Cloud_factor"
-}
-data = pd.read_fwf(inputs["path data"]+inputs["file data"]+inputs["product"]+".dat",
-                   skiprows=inputs["skiprows"])
-date_format(data)
-data_UVI = data[inputs["column"]]
-data_UVI = data_UVI[data_UVI.index >= "2005-01-01"]
-data_UVI = data_UVI[data_UVI.index <= "2019-12-31"]
-data_UVI.to_csv(inputs["path data"] +
-                inputs["file results"]+".csv",
-                float_format='%.4f')

### 2021-07-12 Scripts/Read_omi_ozone_data.py

@@ -7,7 +7,9 @@ def date_format(data):
         data["Datetime"].str[4:6]+"-"+data["Datetime"].str[6:8]
     data["Date"] = pd.to_datetime(data["Date"])
     data.index = data["Date"]
-    data = data.drop(["Date", "Datetime"], 1)
+    data = data.drop(["Date",
+                      "Datetime"],
+                     1)
     return data
 
 
@@ -66,7 +68,9 @@ inputs = {
     "day initial": "2005-01-01",
     "day final": "2019-12-31",
 }
-data = pd.read_fwf(inputs["path data"]+inputs["file data"]+inputs["product"]+".dat",
+data = pd.read_fwf("{}{}{}.dat".format(inputs["path data"],
+                                       inputs["file data"],
+                                       inputs["product"]),
                    skiprows=inputs["skiprows"])
 data = date_format(data)
 data = clean_data(data,

### 2021-07-12 Scripts/Read_pollutants.py
Change to string format

@@ -13,6 +13,7 @@ inputs = {
                    "PM10",
                    "SO2"],
     "path data": "../Data/SEDEMA_Data/Pollutants/",
+    "path results": "../Data",
     "path stations": "../Stations/",
     "file": "CDMX.csv"
 }
@@ -21,12 +22,13 @@ files = sorted((listdir(inputs["path data"])))
 n_param = len(inputs["pollutants"])
 info = np.zeros([n_param, 365, 20, 2])
 for file in files:
-    dates, stations_name, parameters_name, data_list = np.loadtxt(inputs["path data"]+file,
+    dates, stations_name, parameters_name, data_list = np.loadtxt("{}{}".format(inputs["path data"],
+                                                                                file),
                                                                   skiprows=11, usecols=[0, 1, 2, 3],
                                                                   delimiter=",",
                                                                   dtype=str,
                                                                   unpack=True)
-    print("Analizando "+file)
+    print("Analizando {}".format(file))
     for date, station_name, pollutant_name, data in zip(dates, stations_name, parameters_name, data_list):
         date, hour = obtain_date_and_hour(date)
         # <---------------------------------Verificacion de la hora--------------------------->
@@ -47,7 +49,10 @@ for file in files:
 # <---------------------------------Escritura de los Data---------------------------------->
 print("Calculando promedios y escribiendo Data")
 for parameter, n in zip(inputs["pollutants"], range(n_param)):
-    file = open("../Data/"+parameter+"_"+inputs["file"], "w")
+    file = open("{}{}_{}".format(inputs["path results"],
+                                 parameter,
+                                 inputs["file"]),
+                "w")
     file.write("Date")
     for year in range(20):
         file.write(",{}".format(year+2000))

### 2021-07-12 Scripts/Graphics_RD_between_OMI_and_measurements.py
Change xlabel

@@ -60,7 +60,7 @@ plt.subplots_adjust(left=0.085,
                     bottom=0.13,
                     right=0.971,
                     top=0.926)
-plt.xlabel("Years",
+plt.xlabel("Year",
            fontsize=parameters["fontsize"])
 plt.xlim(pd.to_datetime(parameters["Year initial"]),
          pd.to_datetime(parameters["Year final"]))

### 2021-07-12 Paper_third_version/Article_UV_Mexico.tex
Add references limit and change ylabel of RD OMI vs measurements
Add last change before thrid revision

@@
   and clouds (but not local pollution). The ground-based measurements were
-  systematically lower than the satellite-based estimates, by ca. 40\% in
+  systematically lower than the satellite-based estimates, by ca. 35\% in
   2000 and 20\% in 2019. Calculations with a radiative transfer model and
@@
 The UVI is recognized by the World Health and Meteorological
-Organizations (WHO and WMO) as a standardized measure of UV
+Organizations (WHO and WMO) as a standardized index of UV
 radiation\cite{who2002} for global public information. An advantage
@@
 Glenside, PA) detecting wavelengths between 280-400 nm have been
-measuring erythemally-weighted solar radiation. The calibration of the
+measuring erythemally-weighted solar radiation. Calibration of the
 UV sensors has been carried out annually by comparing against a
@@
 network’s sensors have been compared for at least one week against the UV
-readings from the reference sensor to derive a calibration factor. New
-calibration factors typically differ from the old ones by 2\% or less.
+readings from the reference sensor to derive new calibration factors, which typically differed
+from the old ones by 2\% or less.
 Reference sensors have been also calibrated by the manufacturer and updated
 periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
-Long term calibration drift are minimized by these yearly re-calibrations.
-Although at the beginning only a few stations were in operation and have
-been changing, currently 11 stations are recording erythemal
+Long term calibration drifts are minimized by these yearly re-calibrations.
+Although at the beginning only a few stations were in operation and
+varied, currently 11 stations are recording erythemal
 irradiances, which are then multiplied by 40 (see
@@
 
-With the aim to explore the relationship between UVI and air pollutants
+To explore the relationship between UVI and air pollutants
 levels, the hourly averages for ozone (O\textsubscript{3}), carbon
@@
 concentration is reported in $\mu$g m\textsuperscript{-3} at local
-conditions for temperature and pressure.
+temperature and pressure.
 
@@
 Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
-is operated in cooperation between the Netherlands Agency for Aerospace
+is operated collaboratively by the Netherlands Agency for Aerospace
 Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
@@
 The ozone column is estimated by differential absorption of several adjacent
-wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, while clouds are estimated from the reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm, \citet{Tanskanen_2007}).
+wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, and is used in a radiative transfer model to estimate clear-sky UVI at the surface.
+Clouds are estimated from the observed reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm) and the clear-sky UVI is adjusted for their presence.
 A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
@@
 
-Above the atmospheric boundary layer, the model atmosphere was specified to be,
+Above the atmospheric boundary layer, the model atmosphere was specified to be free of aerosols,
 NO\textsubscript{2}, or SO\textsubscript{2}. In one
@@
 knowledge of the exact vertical aerosol profile is not critical for
-ground-level UVI, but would obviously affect the vertical structure of
+ground-level UVI, though it would obviously affect the vertical structure of
 photolysis frequencies.
@@
 Figure~{\ref{628947}} shows the diurnal variation of
-the UVI for several specific cloud-free days, for different seasons and
-several locations (CHO, MER, MON, PED, SAG, SFE and TLA). UV Index calculated with
-the TUV model was used as reference of the behavior during clear sky days.
-According to the comparison of measurements minute by minute, the dates
-with prolonged fluctuations along the day were discarded. However,
+the UVI for typical cloud-free days, for different seasons and
+several locations (CHO, MER, MON, PED, SAG, SFE and TLA).
+The selection of cloud-free days was aided by comparison of the measurements
+with the TUV model predictions for clear skies, with prolonged deviations and
+fluctuations usually indicative of cloudy conditions.However,
 during the rainy period (from June to October) at least a brief episode of clouds,
-as shown at CHO station around noon in 13 June
+is seen at CHO station around noon in 13 June
 2017. Peak values range from 8 during autumn/winter to above 12
@@
 
-The daily maximum UV Index of each station is denoted
-by~\(UVI_{\max}\), these values were counted in the period 2000-2019.
-As shown in Figure~{\ref{461017}}, these values ranged
+The daily maximum UV Index values of each station,~\(UVI_{\max}\),
+are summarized in Figure~{\ref{461017}} for the entire period 2000-2019.
+These values are seen to range
 from 1 to 16, with a majority (61\%) of the days
-experienced~\(UVI_{\max}\) values between 6 and 10, and remarkably
+experiencing~\(UVI_{\max}\) values between 6 and 10, and remarkably
 few, less than 1\%, in the 13-16 range.~The lowest values are
@@
     \caption{{Frequency distribution of daily maximums UV Index values in Mexico City
-    during 2000 -2019.
+    during 2000-2019.
     {\label{461017}}%
@@
 point), the monthly averages (\(\overline{UVI}_m\))
-were calculated along the period 2000-2019 (except for June 2003 due to there were no measurements).
+were calculated along the period 2000-2019 (except for June 2003 due to lack of measurements).
 Long term trends in~\(\overline{UVI}_m\) are shown
@@
     \includegraphics[width=0.70\columnwidth]{figures/Boxplotcos}
-    \caption{{Boxplot of the monthly averages of the maximum UV Index values~(black
+    \caption{{Monthly averages of the maximum UV Index values~(black
           dot) in MCMA for the period 2000-2019: median (central bold line),
-          interquartile range (box edges), 10\% and 90\% percentiles (the whiskers),
+          interquartile range (box edges), 10\% and 90\% percentiles (whiskers),
           the minimum and maximum values (asterisk) and the cosine of the solar zenith angle at solar
@@
     \includegraphics[width=0.70\columnwidth]{figures/UV_Moving_Average}
-    \caption{{3-month running average (violet segments curve) applied to monthly
+    \caption{{Monthly
           average UV Index (black line), the standard deviation (blue fill area) and linear fit (red line).
@@
 
-The UV Index computed from satellite-based observations
+The UV Index computed from OMI satellite-based observations
 over the period 2005-2019 is shown in
@@
 observation of the UV index is due to the intense air pollution of
-Mexico City.~A rather similar behavior was detected in Santiago city,
+Mexico City.~A rather similar behavior was detected in the city of Santiago,
 Chile.\citep{Cabrera_2012} Although the OMI data are corrected for climatological aerosol absorption\citep{Arola_2009}, this correction likely underestimates the absorption within the polluted Mexico City BL.
@@
 
-\subsection{Effect of pollutants on UV radiation}
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
+  \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
+  \label{fig:percentage_relative_difference}
+\end{figure}
+
+Figure \ref{fig:percentage_relative_difference} deviation of the OMI-derived UVI from the ground-based monthly averages. The mean percentage relative difference
+was 35\% in the period 2005-2019. Comparable UV reductions, of 30-40\% due to aerosols, were reported by
+\citet{Panicker_2009} over Pune, India from April 2004 to
+March 2005, with sensitivity coefficients (i.e. change in UVI per unit
+change in AOD) similar to those found here in Table~\ref{table:TUVmodel}.
+
+Comparisons of OMI with ground-based UV measurements have been reviewed
+recently by \citet{Zhang_2019} and \citet{Vitt_2020}.
+OMI-derived UV generally overestimates
+ground-level measurements by 1-10\% in relatively clean conditions (e.g.
+rural U.S), by 10-30\% in Southern Europe and by 40\% or more in
+Santiago, Chile\citep{Cabrera_2012} and Thailand\citep{Janjai_2013}. The
+overestimations appear related in large part to incomplete accounting of
+UV absorption by BL aerosol, although other factors such as the
+correction to solar noon may also introduce some
+bias.\citep{Zhang_2019} Over Europe, ground-based UVI observations for
+several decades are systematically lower than those estimated from
+satellites even after consideration of climatological aerosol
+distributions, showing the importance of local pollution not resolved
+from space.\citep{Vitt_2020} However, the difference between
+satellite-derived and ground-based UVI was less than 1.0 UVI units in
+over 90\% of the cases, in contrast to the difference of 3-5 units found
+here for Mexico City (Table~{\ref{461017}}).
+
+\subsection{Effect of pollutants on UV radiation in Mexico City}
 
@@
   \begin{center}
-    \includegraphics[width=0.63\columnwidth]{figures/pollutants}
-    \caption{{Air quality trends in MCMA for the period 2000-2019~ from annual
+    \includegraphics[width=0.55\columnwidth]{figures/pollutants}
+    \caption{{Air quality trends in MCMA for the period 2000-2019.~ Annual
     averages obtained between 11h to 15h CST every day: PM\textsubscript{10}
@@
     SO\textsubscript{2}(black curve), O\textsubscript{3} (green curve) and
-    AOD\textsubscript{340} (pink curve).
+    AOD\textsubscript{340} (magenta curve).
     {\label{829996}}%
@@
   \end{tabular}
-  \caption{{{{UV Index and criteria pollutants: the absolute change per year for the period 2000-2019,
-                averages in units of $\mu g/m^3$(PM$_{10}$), ppm (CO), ppb
-                (SO$_2$, NO$_2$ and O$_3$), dimensionless (UV Index and AOD$_{340}$) and
-                annual percentage change (\%/year).}}}}
+  \caption{{{{Trends of UV Index and criteria pollutants over 2000-2019.
+                Units: $\mu g/m^3$ for PM$_{10}$, ppm for CO, ppb for SO$_2$, NO$_2$ and O$_3$.}}}}
   \label{table:uvindex}
@@
 15-16; and (2) the average of daily maxima of SIMAT observations and TUV UVI results using
-MCMA pollutants as input. Note that SIMAT and TUV values are in good agreement
-for both 2018-2019 and 2000-2001 and are considerably lower than for case (1). Compared to the OMI
-estimate that included the climatological aerosol correction (15.3),
+MCMA pollutants as input. Note that SIMAT and TUV value are in good agreement
+for both 2000-2001 and 2018-2019 and are considerably lower than for group (1). Compared to the OMI
+estimate that included the climatological absorbing aerosol correction (15.3),
 observed SIMAT values were lower by 35\% in 2000 and by 20\% in 2019.
@@
     \hline
-    \textbf{Conditions for estimation in June-July} & \textbf{UV Index} \\ \hline
+    \textbf{June-July}                              & \textbf{UV Index} \\ \hline
     SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
@@
     \begin{tabular}[c]{@{}l@{}
-      }TUV pristine pollution \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
+      }TUV pristine atmosphere \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.05, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
     \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
   \end{tabular}
-  \caption{{UVI maxima for June-July: averages and standard deviation from ground-based data
-        for the years 2018-2019 and 2000-2001. UVI maximum value reached in the period 2000-2019 for
-        UVI ground-based and the same for satellite in the period 2005-2019. TUV calculations for specified conditions.
+  \caption{{Comparison of June-July UVI maxima measured directly (SIMAT), inferred from satellite-based
+        observations (OMI), and modeled for different pollution levels (TUV).
       }}
@@
 cloud-free model. We cannot exclude that some of the observed trend in
-UVI is due to changes in cloud cover. However, the modeled fractional
+UVI is due to changes in cloud cover. However, the modeled
 UVI reductions due to pollutants, shown in Table
@@
 to have negligible effects in the UVI.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
-  \caption{The percentage relative difference (\% RD) of the satellite and ground-based monthly means UVI for the period 2005-2019.}
-  \label{fig:percentage_relative_difference}
-\end{figure}
-
-Figure \ref{fig:percentage_relative_difference} shows the percentage relative difference between monthly means
-satellite-based and ground-based data with respect to the last one. The mean percentage relative difference
-was 35\% in the period 2005-2019. Comparable UV reductions, of 30-40\% due to aerosols, were reported by
-\citet{Panicker_2009} over Pune, India from April 2004 to
-March 2005, with sensitivity coefficients (i.e. change in UVI per unit
-change in AOD) similar to those found here in Table~\ref{table:TUVmodel}.
-
-Comparisons of OMI with ground-based UV measurements have been reviewed
-recently by \citet{Zhang_2019} and \citet{Vitt_2020}.
-OMI-derived UV generally overestimates
-ground-level measurements by 1-10\% in relatively clean conditions (e.g.
-rural U.S), by 10-30\% in Southern Europe and by 40\% or more in
-Santiago, Chile\citep{Cabrera_2012} and Thailand\citep{Janjai_2013}. The
-overestimations appear related in large part to incomplete accounting of
-UV absorption by BL aerosol, although other factors such as the
-correction to solar noon may also introduce some
-bias.\citep{Zhang_2019} Over Europe, ground-based UVI observations for
-several decades are systematically lower than those estimated from
-satellites even after consideration of climatological aerosol
-distributions, showing the importance of local pollution not resolved
-from space.\citep{Vitt_2020} However, difference between
-satellite-derived and ground-based UVI was less than 1.0 UVI units in
-over 90\% of the cases, in contrast to the difference of 3-5 units found
-for Mexico City (Table~{\ref{461017}}).
 
@@
 observations. Although ideally both data sets should match,
-the satellite has a limitation to seeing boundary layer absorbers.
-When typical values of the pollutants: aerosols,
-tropospheric ozone, and to a lesser extent NO\textsubscript{2}
+space-based observations have difficulting inferring the extent of UV absorption by urban gases and particles.
+Thus, they do not reveal long-term UVI trends, due to substantial air quality improvemnets, that are evident in the ground-based UVI data.
+When typical values of pollutant: aerosols,
+tropospheric ozone, NO\textsubscript{2}
 and SO\textsubscript{2}, are included in a model (e.g. TUV), the
@@
 observed pollutants. Long term improvements in air quality over the last two decades,
-are accompanied by statistically significant increases in the
-observed UVI, again in good agreement with the model-predicted changes.
+were accompanied by statistically significant increases in the
+observed UVI, in agreement with the model-predicted changes.
 
@@
     \hline
-    Pollutant & UVI Change\\ \hline
-    AOD & 0.8\\
-    O\textsubscript{3} & 0.4\\
-    NO\textsubscript{2} & 0.4\\ 
+    Pollutant           & UVI Change \\ \hline
+    AOD                 & 0.8        \\
+    O\textsubscript{3}  & 0.4        \\
+    NO\textsubscript{2} & 0.4        \\
     SO\textsubscript{2} & 0.5        \\ \hline
@@
 
-Finally, based on our results, the solar radiation monitoring network could be
-improved by adding observation sites within or close to the Valley of Mexico, with minor
-influences of the urban plume (e. g., Amecameca; latitude: 19.13°N, longitude: 99.76°W, elevation: 2420 m asl),
-and the complementing of sensors in existing monitoring sites that are at elevations above the urban boundary
-layer like Ajusco (AJU, elevation: 2953 m asl) or Instituto de Investigaciones Nucleares (INN, elevation: 3082 m asl).
+Finally, based on our results, the solar radiation monitoring network might
+be improved by adding observation sites far enough away to lessen the
+influence of the urban plume (e. g., Amecameca; latitude: 19.13°N, longitude: 99.76°W, elevation: 2420 m asl),
+and the adding sensors to existing monitoring sites at higher elevations
+(Ajusco, AJU, 2953 m asl or Instituto de Investigaciones Nucleares, INN, 3082 m asl).
 These sites would provide valuable observations to assess quantitatively the effects of urban pollution on solar radiation levels.

### 2021-07-12 Paper_third_version/Article_UV_Mexico.tex
Add last change before thrid revision

@@
 factory-calibrated reference sensor. The output voltages from the
-network’s sensors have been compared for at least one week against the UV
+network’s sensors were compared for at least one week against the UV
 readings from the reference sensor to derive new calibration factors, which typically differed
 from the old ones by 2\% or less.
-Reference sensors have been also calibrated by the manufacturer and updated
+Reference sensors were also calibrated by the manufacturer and updated
 periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.

### 2021-07-12 Paper_third_version/Article_UV_Mexico.tex
Delete unused references

--- 2021-07-12 Paper_third_version/Article_UV_Mexico.tex
@@
 from the old ones by 2\% or less.
-Reference sensors have been also calibrated by the manufacturer and updated
+Reference sensors were also calibrated by the manufacturer and updated
 periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
@@
       }TUV pristine atmosphere \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.05, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
     \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
@@
 observations. Although ideally both data sets should match,
-space-based observations have difficulting inferring the extent of UV absorption by urban gases and particles.
+the satellite has a limitation to seeing boundary layer absorbers.
 Thus, they do not reveal long-term UVI trends, due to substantial air quality improvemnets, that are evident in the ground-based UVI data.

### 2021-07-12 Scripts/Graphics_omi_data.py
Change on graphics

@@ -32,32 +32,36 @@ def drop_data_useless(data, columns, limit):
     return data
 
 
-def plot_data(data,  date_initial, date_final, path, name):
+def plot_data(data,  date_initial, date_final, path, name, fontsize=14):
     plt.subplots(figsize=(10, 4))
     plt.subplots_adjust(top=0.963,
-                        bottom=0.13,
+                        bottom=0.2,
                         left=0.062,
                         right=0.967,
                         hspace=0.2,
                         wspace=0.2)
-    plt.xlabel("year")
-    plt.ylabel("UV Index")
+    plt.xlabel("Year",
+               fontsize=fontsize+1)
+    plt.ylabel("UV Index",
+               fontsize=fontsize+1)
     dates, xtick = obtain_xticks(date_initial,
                                  date_final)
     plt.xlim(pd.to_datetime(date_initial).date(),
              pd.to_datetime(date_final).date())
-    plt.xticks(dates, xtick)
+    plt.xticks(dates, xtick,
+               fontsize=fontsize)
     plt.scatter(data.index, data,
                 c="#023e8a",
                 marker=".")
     plt.ylim(0, 18)
-    plt.yticks(np.arange(0, 20, 2))
+    plt.yticks(np.arange(0, 20, 2),
+               fontsize=fontsize)
     plt.grid(ls="--",
              color="#000000",
              alpha=0.5)
+    plt.tight_layout()
     plt.savefig("{}{}.png".format(path,
                                   name))
-    plt.show()
 
 
 def obtain_xticks(date_initial, date_final):
@@ -94,10 +98,6 @@ data = obtain_data_in_period(data,
 data = drop_data_useless(data,
                          inputs["UVIcolumns"],
                          inputs["UVI limit"])
-year = data[data.index.month >= 6]
-year = year[year.index.month <= 7]
-#print(year[year == year.max()])
-print(year)
 for uvicolumn in inputs["UVIcolumns"]:
     print("Creando archivo {}".format(uvicolumn))
     data_UVI = data[uvicolumn]

### 2021-07-12 Scripts/Graphics_omi_data.py
Update graphics

@@ -51,7 +51,7 @@ def plot_data(data,  date_initial, date_final, path, name, fontsize=14):
     plt.xticks(dates, xtick,
                fontsize=fontsize)
     plt.scatter(data.index, data,
-                c="#023e8a",
+                c="#6C48A9",
                 marker=".")
     plt.ylim(0, 18)
     plt.yticks(np.arange(0, 20, 2),

### 2021-07-13 Paper_third_version/Article_UV_Mexico.tex
Merge

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title[The UV radiation in Mexico City]
+\title[The UV Radiation in Mexico City]
   {The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico
@@
 the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
-The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths.
-The ozone column is estimated by differential absorption of several adjacent
+The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths.\cite{Tanskanen_2006} The ozone column is estimated by differential absorption of several adjacent
 wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, and is used in a radiative transfer model to estimate clear-sky UVI at the surface.
-Clouds are estimated from the observed reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm) and the clear-sky UVI is adjusted for their presence.
-A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
+Clouds are estimated from the observed reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm) and the clear-sky UVI is adjusted for their presence.\cite{Tanskanen_2007} A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
 The UV Index used for Mexico City corresponds to values at local noon time and clear sky
@@
   \centering
-  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
+  \includegraphics[width=0.71\columnwidth]{figures/Monthly_mean_RD.png}
   \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
@@
 
-Figure \ref{fig:percentage_relative_difference} deviation of the OMI-derived UVI from the ground-based monthly averages. The mean percentage relative difference
+Figure \ref{fig:percentage_relative_difference} shows the deviation of the OMI-derived UVI from the ground-based monthly averages. The mean deviation
 was 35\% in the period 2005-2019. Comparable UV reductions, of 30-40\% due to aerosols, were reported by

### 2021-07-13 Paper_third_version/Article_UV_Mexico.tex
Proposed changes by Piacentini

@@
   and clouds (but not local pollution). The ground-based measurements were
-  systematically lower than the satellite-based estimates, by ca. 35\% in
-  2000 and 20\% in 2019. Calculations with a radiative transfer model and
+  systematically lower than the satellite-based estimates, by ca. 40\% in
+  2000 and 25\% in 2019. Calculations with a radiative transfer model and
   observed concentrations of air pollutants explained well the difference
@@
 
-The question of how air pollution alters the urban UV environment
+The question of how air pollution alters the urban UV radiation environment
 (and~\emph{vice versa}) is not new, but studies have relied mostly on
@@
 reasons: (1) Nearly 23 million people inhabit the Mexico City
-Metropolitan Area (MCMA), and the UV environment has direct implications
+Metropolitan Area (MCMA), and the UV radiation environment has direct implications
 for their health, both in terms of skin/eye UV exposure and~\emph{via}
@@
 
-Here, we analyze two decades of continuous measurements of the UV Index
+In this work, we analyze two decades of continuous measurements of the UV Index
 at multiple locations within the MCMA, collected by the Secretariat of
@@
 with the TUV model predictions for clear skies, with prolonged deviations and
-fluctuations usually indicative of cloudy conditions.However,
+fluctuations usually indicative of cloudy conditions. However,
 during the rainy period (from June to October) at least a brief episode of clouds,
-is seen at CHO station around noon in 13 June
+is seen at CHO station around noon on 23 June
 2017. Peak values range from 8 during autumn/winter to above 12
@@
     \caption{{Frequency distribution of daily maximums UV Index values in Mexico City
-    during 2000-2019.
+    for the period 2000-2019.
     {\label{461017}}%
@@
   \centering
-  \includegraphics[width=0.71\columnwidth]{figures/Monthly_mean_RD.png}
+  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
   \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
@@
 for both 2000-2001 and 2018-2019 and are considerably lower than for group (1). Compared to the OMI
-estimate that included the climatological absorbing aerosol correction (15.3),
-observed SIMAT values were lower by 35\% in 2000 and by 20\% in 2019.
+estimate that included the climatological absorbing aerosol correction (16.6),
+observed SIMAT values were lower by 40\% in 2000 and by 25\% in 2019.
 Similarly, TUV values were 35\% lower in 2000 and 22\% lower in 2019
@@
 The reductions in surface UV radiation with respect to an ideally clear
-atmosphere -- by nearly 40\% in 2000 and still 20\% in 2020 -- are
+atmosphere -- by nearly 40\% in 2000 and still 20\% in 2019 -- are
 large, both within the context of human UV exposure and air quality
@@
   wishes to thank CONICET and National University of Rosario, Argentina,
-  for their partial support to the present work. The National Center for
+  for their partial support to the present work. We thank Dr. Jay Herman
+  (University of Maryland Baltimore County) for useful discussions. The National Center for
   Atmospheric Research is sponsored by the National Science Foundation.

### 2021-07-13 Scripts/Graphics_RD_between_OMI_and_measurements.py
Figures 6 and 7 with the same size

@@ -56,10 +56,12 @@ print("La diferencial relativa promedio es {:.2f}".format(
 dates, years = obtain_xticks(parameters["Year initial"],
                              parameters["Year final"])
 plt.figure(figsize=(10, 4))
-plt.subplots_adjust(left=0.085,
-                    bottom=0.13,
-                    right=0.971,
-                    top=0.926)
+plt.subplots_adjust(top=0.963,
+                    bottom=0.2,
+                    left=0.062,
+                    right=0.967,
+                    hspace=0.2,
+                    wspace=0.2)
 plt.xlabel("Year",
            fontsize=parameters["fontsize"])
 plt.xlim(pd.to_datetime(parameters["Year initial"]),
@@ -76,5 +78,6 @@ plt.scatter(monthly_mean.index, monthly_mean["RD"],
 plt.grid(ls="--",
          color="#000000",
          alpha=0.5)
+plt.tight_layout()
 plt.savefig("{}Monthly_mean_RD.png".format(parameters["path graphics"]),
             dpi=400)

### 2021-07-13 Scripts/Graphics_omi_data.py

@@ -41,9 +41,9 @@ def plot_data(data,  date_initial, date_final, path, name, fontsize=14):
                         hspace=0.2,
                         wspace=0.2)
     plt.xlabel("Year",
-               fontsize=fontsize+1)
+               fontsize=fontsize)
     plt.ylabel("UV Index",
-               fontsize=fontsize+1)
+               fontsize=fontsize)
     dates, xtick = obtain_xticks(date_initial,
                                  date_final)
     plt.xlim(pd.to_datetime(date_initial).date(),

### 2021-07-14 Paper_third_version/Article_UV_Mexico.tex
Figures 6 and 7 with the same size
Chnage on Table 4

@@
   observed concentrations of air pollutants explained well the difference
-  between satellite- and ground-based UVI, and showed specific
-  contributions from aerosols in the boundary layer and the free troposphere,
-  O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}, in
-  decreasing order of importance. Such large changes in UV radiation
-  between 2000 and 2019 have important implications ranging from human
-  health (skin cancer and cataract induction) to air pollution control
-  (photochemical smog formation).
+  between satellite and ground-based UVI, and showed specific contributions
+  from aerosols, O\textsubscript{3}, NO\textsubscript{2},
+  and SO\textsubscript{2}, in decreasing order of importance. Such large
+  changes in UV radiation between 2000 and 2019 have important implications
+  ranging from human health (skin cancer and cataract induction) to air
+  pollution control (photochemical smog formation).
 \end{abstract}
@@
   \begin{center}
-    \includegraphics[width=0.70\columnwidth]{figures/CSUVindex}
+    \includegraphics[width=0.95\columnwidth]{figures/CSUVindex}
     \caption{{UV Index at solar noon for clear sky recorded by OMI-Aura/NIVR-FMI-NASA,
@@
   \centering
-  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
+  \includegraphics[width=0.95\columnwidth]{figures/Monthly_mean_RD.png}
   \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
@@
   \caption{{Comparison of June-July UVI maxima measured directly (SIMAT), inferred from satellite-based
-        observations (OMI), and modeled for different pollution levels (TUV).
+        observations (OMI), and modeled for different pollution levels (TUV calculation for 21 June at solar noon).
       }}
@@
 
-Table~{\ref{table:year2000-2019}} shows the contribution of different pollutants
-to the UVI increase between 2000 and 2019, computed with the TUV model.
-The year 2000 was taken as the base case, and each pollutant was decreased
-to its 2019 value individually while the others were maintained at their 2000 value.
-Decreasing aerosol AOD has been the largest driver of the UVI changes,
-but the absorption by gaseous pollutants has also decreased significantly.
-Additional future reductions in AOD, NO\textsubscript{2}, and O\textsubscript{3} could increase the
-UVI further, while the low SO\textsubscript{2} levels reached by 2019 are expected
-to have negligible effects in the UVI.
+Table~{\ref{table:year2000-2019}} shows the contribution to UVI reductions from individual pollutants,
+computed with the TUV model for conditions similar to those in Table {\ref{table:TUVmodel}} (21 June solar noon).
+If the pollutant levels of the year 2000 are added one at the time to a pollution-free atmosphere
+(see middle column of Table {\ref{table:year2000-2019}}),
+aerosols account for more than half of the total UVI reduction,
+with the gases O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2},
+contributing in order of importance to the remainder. It should be noted that the sum
+of these individual contributions (-6.8) differs from the value obtained if these pollutants
+are applied simultaneously rather than one at the time (-5.9, from Table {\ref{table:TUVmodel}}).
+This non-additivity results mainly from (1) saturation of overlapping absorption spectra,
+especially for O\textsubscript{3} and SO\textsubscript{2} at the shortest wavelengths, and (2)
+interactions between absorption and scattering, e.g. aerosols causing a change in photon
+pathlengths through absorbing gases; both effects are treated in the TUV model.
+
+The right column of Table {\ref{table:year2000-2019}} shows the contribution of the individual pollutants to the UVI
+increase experienced over the years 2000-2019. For this calculation, the pollutants
+were decreased individually to their 2019 level while the others were held at the 2000 values.
+Aerosol reductions were the largest single factor responsible for the UV increase,
+but more than half of the increase was due to reductions of the gases, of which the near-complete
+elimination of SO\textsubscript{2} was most important. The total increase computed from the sum (1.8) is in
+good agreement with the 2000-2019 increase in which all pollutants were changed simultaneously
+(1.9, from Table {\ref{table:TUVmodel}}), as smaller changes in UVI mitigate non-linearities.
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{lcc}
+    \hline
+    Pollutant           & $\Delta$UVI, 2000 - zero pollution (a) & $\Delta$UVI, 2000-2019 (b) \\ \hline
+    AOD                 & -3.7                                   & 0.8                        \\
+    O\textsubscript{3}  & -1.4                                   & 0.3                        \\
+    NO\textsubscript{2} & -0.9                                   & 0.3                        \\
+    SO\textsubscript{2} & -0.8                                   & 0.4                        \\
+    \textbf{Total}      & \textbf{-6.8}                          & \textbf{1.8}               \\\hline
+  \end{tabular}
+  \caption{Contribution of different pollutants to UV Index changes in Mexico City, calculated with the TUV model for 21 June at solar noon.
+(a) Pollutants from year 2000 added to clean atmosphere, one at the time.
+(b) Pollutants lowered from 2000 to 2019 levels, one at the time.}
+  \label{table:year2000-2019}
+\end{table}
 
@@
           axis, red) for zero pollution (solid) and Mexico City in the years 2000
-          (dashed) and 2019 (dotted)
+          (dashed) and 2019 (dotted). TUV calculation for 21 June at solar noon.
             {\label{973680}}%
@@
 observed UVI, in agreement with the model-predicted changes.
-
-\begin{table}[H]
-  \centering
-  \begin{tabular}{cc}
-    \hline
-    Pollutant           & UVI Change \\ \hline
-    AOD                 & 0.8        \\
-    O\textsubscript{3}  & 0.4        \\
-    NO\textsubscript{2} & 0.4        \\
-    SO\textsubscript{2} & 0.5        \\ \hline
-  \end{tabular}
-  \caption{Contributions of individual pollutants to the 2000-2019 UV Index changes.
-Baseline calculation for 2000 conditions (AOD = 0.7, O\textsubscript{3} = 70 ppb, NO\textsubscript{2} = 40 ppb, SO\textsubscript{2} = 20 ppb).
-Individual pollutant contributions are estimated by adjusting each pollutant, one at the time, to its 2019 value (AOD = 0.5, O\textsubscript{3} = 50 ppb, NO\textsubscript{2} = 20 ppb, SO\textsubscript{2} = 1 ppb), while maintaining the others at their 2000 value.}
-  \label{table:year2000-2019}
-\end{table}
 

### 2021-07-19 Paper_4_version/Article_UV_Mexico.tex
Paper version 4
Little changes

--- 2021-07-14 Paper_third_version/Article_UV_Mexico.tex
@@
 \usepackage{multirow}
-
+\usepackage{achemso}
+\setkeys{acs}{etalmode=truncate,maxauthors=40}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
+The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W and 2240
 meters above sea level (m asl), surrounded by mountain ridges exceeding
@@
   \begin{tabular}{cccc} \hline
-    Variable               & $\frac{absolute change}{year}$ & Avg$_{2000-2019}$ & $\Delta(\%/year)$ \\ \hline
+    Variable               & $\frac{\text{absolute change}}{year}$ & Avg$_{2000-2019}$ & $\Delta(\%/year)$ \\ \hline
     UVI                    & 0.08                                  & 9.2               & 0.9               \\

### 2021-07-21 Paper/v1/full_article.tex
Rename paper folders

\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage[section]{placeins}
\usepackage{xcolor}
\usepackage{breakcites}
\usepackage{lineno}
\usepackage{hyphenat}

\setlength\columnsep{25pt}

\PassOptionsToPackage{hyphens}{url}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{etoolbox}
\makeatletter
% \patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
%   \errmessage{\noexpand\@combinedblfloats could not be patched}%
% }%
\makeatother

\usepackage{natbib}

\renewenvironment{abstract}
  {{\bfseries\noindent{\abstractname}\par\nobreak}\footnotesize}
  {\bigskip}

\titlespacing{\section}{0pt}{*3}{*1}
\titlespacing{\subsection}{0pt}{*2}{*0.5}
\titlespacing{\subsubsection}{0pt}{*1.5}{0pt}

\usepackage{authblk}

\usepackage{graphicx}
\usepackage[space]{grffile}
\usepackage{latexsym}
\usepackage{textcomp}
\usepackage{longtable}
\usepackage{tabulary}
\usepackage{booktabs,array,multirow}
\usepackage{amsfonts,amsmath,amssymb}
\providecommand\citet{\cite}
\providecommand\citep{\cite}
\providecommand\citealt{\cite}
% You can conditionalize code for latexml or normal latex using this.
\newif\iflatexml\latexmlfalse
\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}%

\AtBeginDocument{\DeclareGraphicsExtensions{.pdf,.PDF,.eps,.EPS,.png,.PNG,.tif,.TIF,.jpg,.JPG,.jpeg,.JPEG}}

\usepackage[utf8]{inputenc}
\usepackage[ngerman,greek,english]{babel}

\usepackage{float}

% Edit this header.tex file to include frontmatter definitions and global macros

% Add here any LaTeX packages you would like to load in all document blocks
% \usepackage{xspace}

% Add here any LaTeX macros you would like to load in all document blocks
% \def\example{This is an example macro.}

% -----

\iflatexml
% Add here any LaTeXML-specific commands

% -----

\else
% Add here any export style-specific LaTeX commands. These will only be loaded upon document export. 
% \paperfield{Subject domain of my document}
% \keywords{keyword1, keyword2}
% \corraddress{Author One PhD, Department, Institution, City, State or Province, Postal Code, Country}
% \fundinginfo{Funder One, Funder One Department, Grant/Award Number: 123456.}
\fi

\begin{document}

\title{The Ultraviolet Environment of a Tropical Megacity in Transition: Mexico
City 2000-2019}

\author[1,2]{Adriana Ipiña}
\author[3]{Gamaliel López-Padilla}
\author[4]{Armando Retama}
\author[1]{Rubén D. Piacentini}
\author[5]{Sasha Madronich}

\affil[1]{Instituto de Física Rosario (CONICET-UNR), Rosario, Argentina}
\affil[2]{Centro de Ciencias de la Atmósfera, Universidad Nacional Autónoma de México, Mexico City, Mexico}
\affil[3]{Facultad de Ciencias Físico Matemáticas, Universidad Autónoma de Nuevo León, San Nicolás de los Garza, México}
\affil[4]{Independent researcher, Mexico City, Mexico}
\affil[5]{National Center for Atmospheric Research, Boulder, Colorado, USA}

\vspace{-1em}

  \date{}

\begingroup
\let\center\flushleft
\let\endcenter\endflushleft
\maketitle
\endgroup

\linenumbers

\doublespacing

\selectlanguage{english}
\begin{abstract}
Tropical regions experience naturally high levels of UV radiation, but
urban pollution can reduce these levels substantially. We analyzed 20
years of measurements of the UV Index (UVI) at several ground-level
locations in the Mexico City Metropolitan Area and compared these with
UVI values estimated from satellite overpasses observing ozone and
clouds (but not local pollution). The ground-based measurements were
systematically lower than the satellite-based estimates, by ca. 40\% in
2000 and 30\% in 2019. Calculations with a radiative transfer model and
observed concentrations of air pollutants explained well the difference
between satellite- and ground-based UVI, and showed specific
contributions from boundary layer aerosols, O\textsubscript{3},
NO\textsubscript{2}, and SO\textsubscript{2}, in decreasing order of
importance. Such large changes in UV radiation have important
implications ranging from human health (skin cancer and cataract
induction) to air pollution control (photochemical smog formation).%
\end{abstract}%

\sloppy

Keywords: Ultraviolet radiation, UV~Index, Megacities, Air pollution,
Urban photochemistry.

Synopsis: Improvements in Mexico City's air quality during 2000-2019
were accompanied by increases in UV radiation, augmenting human exposure
and photochemical smog formation.

\section*{Introduction}

{\label{123750}}

Ultraviolet (UV) radiation is an important component of the urban
environment, affecting human populations directly through UV exposure of
skin and eyes\textsuperscript{\hyperref[csl:1]{1},\hyperref[csl:2]{2},\hyperref[csl:3]{3}} and less directly (but with great
impact) by driving the formation of photochemical smog, including
tropospheric ozone and other oxidants, as well as secondary aerosols
containing nitrates, sulfates, and organics.\textsuperscript{\hyperref[csl:4]{4},\hyperref[csl:5]{5},\hyperref[csl:6]{6}} These
pollutants, along with others of primary origin commonly found in urban
atmospheres (e.g., black carbon, sulfur dioxide), can in turn scatter
and/or absorb UV radiation, alter its vertical distribution, and so
modify the photochemical rate of their own formation. Such feedback
complicates the calculation of both the UV radiation field (including at
the surface), and the evolution of photochemical smog in the urban
boundary layer.

The question of how air pollution alters the urban UV environment
(and~\emph{vice versa}) is not new, but studies have relied mostly on
numerical models,\textsuperscript{\hyperref[csl:7]{7},\hyperref[csl:8]{8},\hyperref[csl:9]{9}} with relatively fewer available
observations (e.g.,~\emph{McKenzie et
al.\textsuperscript{\hyperref[csl:10]{10}}};~\emph{Panicker et
al.}\textsuperscript{\hyperref[csl:11]{11}};~\emph{Palancar et al}.\textsuperscript{\hyperref[csl:12]{12}};
reviewed by Bais et al.\textsuperscript{\hyperref[csl:13]{13}}). Increases in UV have been
estimated in association with decadal emission reductions, e.g. in
China,\textsuperscript{\hyperref[csl:14]{14},\hyperref[csl:15]{15},\hyperref[csl:16]{16}} and have led to less-than-expected reductions
in photochemical smog, in part due to stronger UV
photochemistry.\textsuperscript{\hyperref[csl:17]{17},\hyperref[csl:18]{18},\hyperref[csl:19]{19}} Emission reductions have also occurred
globally during the 2020 COVID-19 pandemic,\textsuperscript{\hyperref[csl:20]{20},\hyperref[csl:21]{21}} but
ground-level ozone in polluted have actually
increased,\textsuperscript{\hyperref[csl:22]{22},\hyperref[csl:23]{23}} due at least in part to the increased UV
radiation. Unfortunately, the observational data base of relevant UV
radiation remains rather sparse to evaluate such model-derived
hypotheses.~~

The environment of Mexico City is of particular interest for several
reasons: (1) Nearly 23 million people inhabit the Mexico City
Metropolitan Area (MCMA), and the UV environment has direct implications
for their health, both in terms of skin/eye UV exposure and~\emph{via}
photochemical smog formation. (2) As a tropical megacity, it is to some
extent representative of the situation of many others, with year-round
intense midday UV irradiance, a shallower atmosphere due to significant
elevation above sea level, and a transition toward newer and cleaner
technologies, leading to gradual improvements in air quality. (3) Air
quality within MCMA has undergone extensive scrutiny, with
well-established monitoring network since 1986,\textsuperscript{\hyperref[csl:24]{24}}
numerous intensive field campaigns to study the meteorology, emissions,
and photochemistry of smog formation,\textsuperscript{\hyperref[csl:25]{25},\hyperref[csl:26]{26},\hyperref[csl:27]{27}} and numerical
modeling incorporating the evolving knowledge.\textsuperscript{\hyperref[csl:28]{28},\hyperref[csl:29]{29},\hyperref[csl:30]{30},\hyperref[csl:31]{31}} This
extensive body of knowledge provides the foundation for understanding
our study.

Here, we analyze two decades of continuous measurements of the UV Index
at multiple locations within the MCMA, collected by the Secretariat of
the Environment (Secretar\selectlanguage{ngerman}ía del Medio Ambiente, SEDEMA) of the Mexico
City government as part of an intensive monitoring network over the
MCMA.\textsuperscript{\hyperref[csl:32]{32}}~The UV Index is defined as:

\begin{equation}
\label{eq:UVI}
UVI=40 \int_{250nm}^{400nm} E\left(\lambda,t\right) \cdot S_{er}(\lambda) d\lambda
\end{equation}

where~\(E(\lambda,t)\)\emph{~} is the solar spectral irradiance in
units of W/(m\textsuperscript{2} ·nm) and~\(S_{er}\left(\lambda\right)\) is the
erythemal sensitivity of human skin.\textsuperscript{\hyperref[csl:33]{33},\hyperref[csl:34]{34}} Multiplication by
40 is chosen historically to yield small integer scales, but is
otherwise scientifically arbitrary.

The UVI is recognized by the World Health and Meteorological
Organizations (WHO and WMO) as a standardized metric of UV
radiation\textsuperscript{\hyperref[csl:33]{33}} for global public information. An advantage
of using the UVI as (one) metric of UV radiation is that it is being
increasingly observed or calculated and disseminated, enabling more
objective comparisons between seasons and locations. The UVI
observations from Mexico City, considered here, are an important element
of this global picture. ~

While the UVI at the surface cannot be translated directly into
photolysis frequencies for various photo-labile molecules, the spectral
weighting of the UVI (ca. 300-320 nm) is approximately similar to that
for the photolysis of ozone to singlet oxygen atoms. Other UV
wavelengths are of course also important, e.g. for the photolysis of
nitrogen dioxide, and may be affected differently depending on the
pollutant. With these considerations and a few other \emph{caveats}, UVI
trends examined here can also be used to infer accompanying trends in
photolysis frequencies.

\section*{Methods}

{\label{770133}}

\subsection*{Ground-based measurements}

{\label{220276}}

The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
meters above sea level (asl), surrounded by mountain ridges exceeding
5000 m asl, with complex topography and thermal inversions that inhibit
winds and favor intense air pollution.\textsuperscript{\hyperref[csl:35]{35},\hyperref[csl:36]{36}} Air quality
monitoring and surface meteorological measurements in the MCMA are
conducted~continuously by the Atmospheric Monitoring System (SIMAT, by
its Spanish acronym) of the Mexico City Government. Since the year 2000,
UV radiometers (model 501-A, Solar Light Company Inc., Glenside, PA)
detecting wavelengths between 280-400 nm have been measuring
erythemally-weighted solar radiation. The calibrations were carried out
annually, using a periodically calibrated reference sensor from the same
manufacturer. Although at the beginning only a few stations were in
operation and have been changing, currently 11 stations are recording
erythemal irradiances, which are then multiplied by 40 (see
Eq.~{\ref{eq:UVI}}) to give UV Indices.
Table~{\ref{table:stations}} describes the location of
the stations where UV Index has been measured.
Figure~{\ref{977905}} shown the radiometers of the
SIMAT have been distributed over MCMA, prioritizing the sites with more
density of population. Near real-time data for each station are
available on the SIMAT official
website~\url{http://www.aire.cdmx.gob.mx/default.php}.\selectlanguage{english}
\begin{table}[H]
\centering 
\begin{tabular}{ccccc}
\hline
Station&Environment &Lat (\selectlanguage{ngerman}°N) &Lon (\selectlanguage{ngerman}°W)&El (masl)\\ \hline
CHO &school zone&19.27&99.89&2253\\ 
CUT &ecological park&19.72&99.20&2263\\
FAC &urban&19.48&99.24&2299\\
HAN &urban&19.42&99.08&2235\\
LAA &urban&19.48&99.15&2255\\
MER&downtown&19.42&99.12&2245\\
MON&rural&19.46&98.90&2252\\
MPA&rural&19.18&98.99&2594\\
PED&residential &19.33&99.20&2326\\
SAG&urban&19.53&99.03&2241\\
SFE&residential &19.36&99.26&2599\\
TLA&urban &19.53&99.20&2311\\ 
CCA &University city&  19.33 & 99.18 & 2294\\\hline
\end{tabular}
\caption{\selectlanguage{ngerman}{{{SIMAT stations, environmental descriptors and geographical positions. Abbreviations names: Chalco (CHA), Cuautitlán (CUT), FES Acatlán (FAC), Hangares (HAN), Laboratorio de Análisis Ambiental (LAA), Merced (MER), Montecillo (MON), Milpa Alta (MPA), Pedregal (PED), San Agustín (SAG), Santa Fe (SFE), Centro de Ciencias de la Atmósfera (CCA) and Tlalnepantla (TLA). }}}}
\label{table:stations}
\end{table}\selectlanguage{ngerman}\selectlanguage{english}
\begin{figure}[H]
\begin{center}
\includegraphics[width=0.70\columnwidth]{figures/MapaUV v4Dec20/MapaUV v4Dec20}
\caption{{Map with the location of the SIMAT continuos monitoring stations over
MCMA. Sites denoted by the blue solid dots correspond to the sites were
UV had been measured, the site on open blue dot denoted a discontinued
site, the red dot corresponds to the location of the AERONET site. The
location~of Mexico City and the acronyms of the UV and AERONET site are
shown at the upper and lower frames at the rigth, respectively.
{\label{977905}}%
}}
\end{center}
\end{figure}

With the aim to explore the relationship between UVI and air pollutants
levels, the hourly averages for ozone (O\textsubscript{3}), carbon
monoxide (CO), nitrogen dioxide (NO\textsubscript{2}), sulfur
dioxide~(SO\textsubscript{2}) and particle matter with diameter
sizes~\(\le\) 10 micrometers (PM\textsubscript{10}), were
downloaded from the SIMAT\textsuperscript{\hyperref[csl:37]{37}}. Only values obtained
between 11h and 14h CST were considered for the trends analysis.
Pollutants measurements are conducted by the SIMAT using
regulatory-grade commercial instruments. Measurement principles include
ultraviolet photometry (model 400E, Teledyne-API) for
O\textsubscript{3}, chemiluminescence (model 200E, Teledyne-API) for
NO\textsubscript{2}, UV fluorescence (model 100E, Teledyne API) for
SO\textsubscript{2}, and infrared absorption (model 300E, Teledyne-API)
for CO. The PM\textsubscript{10} continuous mass concentration was
measured with Tapered Element Oscillating Microbalance (TEOM 1400AB or
TEOM 1405 DF, Thermo Scientific) monitors. Gaseous pollutant levels are
reported in ppb concentration units for O\textsubscript{3},
SO\textsubscript{2} and NO\textsubscript{2}, and in ppm for CO.
Particulate matter mass concentration is reported in \selectlanguage{greek}µ\selectlanguage{english}g
m\textsuperscript{-3} at local conditions for temperature and pressure.

Aerosol optical depth at 340 nm was obtained from the Centro de Ciencias
de la Atm\selectlanguage{ngerman}ósfera (CCA), measurements were conducted with a photometer of
the AErosol RObotic NETwork (AERONET\textsuperscript{\hyperref[csl:38]{38}}). The data
Product Level 2.0 were selected, and annual averages
AOD\textsubscript{340} were calculated from continuous measurements
during at least 7 months\textsubscript{.}

\subsection*{Satellite data}

{\label{800866}}

Estimates of the UV Index from satellite-based measurements of clouds
and O\textsubscript{3} were used for comparing to the ground-based
measurements. These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\textsuperscript{\hyperref[csl:39]{39}} OMI
was created in cooperation between the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI (hereafter OMI-Aura/NIVR-FMI-NASA) performs observations over a
geographical dimension of 13 × 24km\textsuperscript{2} at nadir. For
Mexico City, the satellite overpass time is between 19:00h - 21:00h UTC
and data are specific for the coordinates and elevation of Mexico City.
To our knowledge, no correction is made for local air pollution.

\subsection*{TUV model}

{\label{308972}}

Calculations of the UV Index were also made with the Tropospheric
Ultraviolet Visible (TUV v5.3) model.\textsuperscript{\hyperref[csl:40]{40}} The model
vertical structure was modified to place the surface at 2.24 km asl,
overlain by a 3 km boundary layer\textsuperscript{\hyperref[csl:41]{41},\hyperref[csl:36]{36}} in which the aerosol
optical depth (AOD) and the concentrations of gaseous
O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2} can be
varied. Above the atmospheric boundary layer (ABL) (i.e. above 5.24 km
asl) the model defaults to a climatological continental aerosol
profile\textsuperscript{\hyperref[csl:42]{42}} whose remaining optical depth (i.e. from 5.24
km to space) is 0.23 at 340 nm, and O\textsubscript{3} profile from the
US Standard Atmosphere with the total ozone column scaled to a
climatological value of 265 Dobson Units. ABL aerosols are modeled by
prescribing the AOD at 340 nm (from AERONET observations), scaled to
other wavelengths inversely with wavelength (Angstrom coefficient =
1.0), asymmetry factor of 0.7, and a single scattering albedo of 0.85 at
UV wavelengths, following the determinations made in Mexico City by Corr
et al.\textsuperscript{\hyperref[csl:43]{43}} and Palancar et al.\textsuperscript{\hyperref[csl:12]{12}}.
Radiative transfer calculations were carried out with the
pseudo-spherical 4-stream option.

\section*{Results and Discussion}

{\label{447962}}

Figure~{\ref{628947}} shows the diurnal variation of
the UVI for several specific cloud-free days, for different seasons and
several locations. Peak values range from 8 during autumn/winter to
almost 12 in spring/summer, in correspondence to the respective December
and June solstices, and follow closely the yearly variation of the
cosine of the solar zenith angle at noon (see
Figure~{\ref{310112}}). Although the stations are all
within a 25 km radius, substantial differences among them are notable.
The differences are particularly evident in the afternoons,~when air
pollutants have significantly accumulated within the boundary layer and
the mixing height is maximum, suggesting that their origin is not
related to calibration biases between the instruments. Survey of the
locations revealed that shadowing from nearby structures is not an
issue. It is more likely that local differences in air pollution,
particularly aerosols, are the cause of this variability. Previous
studies~(e.g., Castro et al.\textsuperscript{\hyperref[csl:44]{44}}~and Palancar et
al.\textsuperscript{\hyperref[csl:12]{12}})~have shown that surface UV radiation in Mexico
City is attenuated significantly by aerosols. The measurements shown in
Fig~{\ref{628947}} are consistent with increasing
pollution during the course of the day, with highest aerosol loading
(and highest variability) attained in the afternoon. Further support for
the role of pollution in suppressing the UVI comes from the observation
made at Santa Fe (SFE) site which in
Fig.~{\ref{628947}} are seen to be systematically
higher, e.g. by over 10\% in autumn afternoons, compared to the other
stations. The SFE station is located at 2600 m asl, approximately 300 m
higher than Mexico City downtown, and so avoids a substantial fraction
of the polluted MCMA boundary layer.\textsuperscript{\hyperref[csl:45]{45}} It is indeed
expected to have higher values of the UVI, in agreement with the
observations.\selectlanguage{english}
\begin{figure}[H]
\begin{center}
\includegraphics[width=0.70\columnwidth]{figures/season/season}
\caption{{UV Index measured over MCMA by SIMAT stations each minute along the day
under cloudless conditions for the seasons and dates (month/day/year):
Spring (04/20/2018), Summer (06/23/2018), Autumn (11/13/2018) and Winter
(02/02/2018).
{\label{628947}}%
}}
\end{center}
\end{figure}

Daily maximum values,~\(UVI_{\max}\), were extracted from the time
interval 11:00 h-14:00 h CST from each of the stations, with 7305
continuous days of measurements, during the period 2000-2019. As shown
in Figure~{\ref{461017}}, these values ranged from 1 to
15, with a majority (62\%) of the days experienced~\(UVI_{\max}\)
values between 6 and 10, and remarkably few, less than 1\%, in the
higher 13-15 range.\selectlanguage{english}
\begin{figure}[H]
\begin{center}
\includegraphics[width=0.49\columnwidth]{figures/HistTotal/HistTotal}
\caption{{Frequency distribution of daily maximum UV Index values in Mexico City
during 2000 -2019.
{\label{461017}}%
}}
\end{center}
\end{figure}

Similar patterns are found when considering the monthly averages
(\(\overline{UVI}_m\)) of daily~\(UVI_{\max}\) as shown in
Figure~{\ref{310112}}. The long-term averages present a
seasonal variation (as in Fig.~{\ref{628947}}),
following approximately the cosine of the noontime solar zenith angle.
Notably, values rarely if ever exceed 12 (as in
Fig.~{\ref{461017}}). Long term trends
in~\(\overline{UVI}_m\) are shown in
Figure~{\ref{185758}}. A clear~upward trend is seen,
with a slope for the linear fit of 0.7\%/year or +1.2 UVI units over the
two decades.\selectlanguage{english}
\begin{figure}[H]
\begin{center}
\includegraphics[width=0.70\columnwidth]{figures/Boxplotcos/Boxplotcos}
\caption{{Boxplot of monthly UV Index in MCMA for the period 2000-2019: median
(central bold line), average (black dot), 25\textsuperscript{th} and
75\textsuperscript{th} percentiles (box edges), standard deviation (the
whiskers), the minimum and maximum values (plus sign) and the cosine of
the solar zenith angle at solar noon (blue curve).
{\label{310112}}%
}}
\end{center}
\end{figure}\selectlanguage{english}
\begin{figure}[H]
\begin{center}
\includegraphics[width=0.70\columnwidth]{figures/CloudDaily/UVyearlyError}
\caption{{Moving average function (gray curve) applied to monthly average UV
Index, standard deviation (black dots and dash line) and linear fit (red
line).
{\label{185758}}%
}}
\end{center}
\end{figure}

The UV Index computed from satellite-based observations
(OMI-Aura/NIVR-FMI-NASA) over the period 2005-2019 is mapped in
Figure~{\ref{485116}}. The satellite-derived UVIs vary
from 8 in winter to 15 in summer, both values being substantially higher
than the ground-based observations (ca. 6 for winter and 11 for summer,
see Fig.~{\ref{310112}}). We hypothesize that this
large difference between satellite-based estimation and ground-based
observation of the UV index is due to the intense air pollution of
Mexico City.~A rather similar behavior was detected in Santiago city,
Chile.~\textsuperscript{\hyperref[csl:46]{46}}\selectlanguage{english}
\begin{figure}[H]
\begin{center}
\includegraphics[width=0.70\columnwidth]{figures/UVI-OMI/UVI-OMI}
\caption{{UV Index recorded by OMI-Aura/NIVR-FMI-NASA, from 2005 to 2019.
{\label{485116}}%
}}
\end{center}
\end{figure}

\subsection*{Effect of pollutants on UV
radiation}

{\label{884442}}

Trends and averages in aerosol optical depth AOD\textsubscript{340} and
criteria pollutants PM\textsubscript{10}, CO, NO\textsubscript{2},
O\textsubscript{3~}and SO\textsubscript{2} observed at the SIMAT
stations over 2000-2019, are shown in
Figure~{\ref{829996}} and summarized in
Table~{\ref{table:uvindex}} together with
the~\(UVI_{\max}\). Similar trends have been noted
before~\emph{\textsuperscript{\hyperref[csl:47]{47},\hyperref[csl:48]{48},\hyperref[csl:49]{49}}} and reflect the long-term success of
emission reduction policies and programs.

The observed changes in the concentrations of these air pollutants have
significant implications for surface UV radiation, as can be
demonstrated with the TUV radiative transfer model (see
Table~{\ref{table:TUVmodel}}). The UVI under an ideally
clear atmosphere would reach 15.9 (at noon on 21 June), but pollutant
concentrations in the year 2000 (estimated from
Table~{\ref{table:uvindex}} and
Fig.~{\ref{829996}}) reduce the UVI by nearly 40\%,
down to 9.7. Most of this reduction is due to aerosols in the ABL, with
additional contributions from aerosols in the free troposphere (FT), and
ABL gaseous O\textsubscript{3}, NO\textsubscript{2}, and
SO\textsubscript{2} in order of decreasing importance. The
pollution-related UV reductions in 2019 are less severe, with UVI
increasing by 14\% to 11.1 over the two decades, but still 30\% below
values of ideally clean skies. Thus, the model calculations for clear
skies are in good agreement with the satellite-derived UVI values, and
the model calculations with observed pollutants are in good agreement
with ground-based UVI values, even reflecting their long-term trend.\selectlanguage{english}
\begin{figure}[H]
\begin{center}
\includegraphics[width=0.63\columnwidth]{figures/contCDMX/contCDMX}
\caption{{Air quality trends in MCMA for the period 2000-2019~ from annual
averages obtained between 11h to 14h CST every day: PM\textsubscript{10}
(brown curve), CO (purple curve), NO\textsubscript{2} (blue curve),
SO\textsubscript{2}(black curve), O\textsubscript{3} (green curve) and
AOD\textsubscript{340} (pink curve).
{\label{829996}}%
}}
\end{center}
\end{figure}\selectlanguage{english}
\begin{table}[H]
\centering
\begin{tabular}{cccc} \hline
Variable &$\frac{\Delta variable}{\Delta t}$ & Avg$_{2000-2019}$ & $\Delta(\%/year)$\\ \hline
UVI &0.06 &9.1 &0.7 \\
PM\textsubscript{10} &-0.12 & 51.1& -0.2\\ 
CO &-0.08 &1.0 &-8.2\\ 
NO\textsubscript{2} &-1.04 & 30.4 &-3.4\\ 
O\textsubscript{3} &-1.05 & 58.5 &-1.8\\ 
AOD\textsubscript{340} &-0.01 &0.6 &-1.6\\
SO\textsubscript{2} & -0.82 &8.9 & -9.2\\
\hline
\end{tabular}
\caption{{{{UV Index and criteria pollutants: slope for the period 2000-2019, averages in units of $\mu g/m^3$(PM$_{10}$), ppm (CO), ppb (SO$_2$, NO$_2$ and O$_3$), dimensionless (UV Index and AOD$_{340}$) and annual percentage change (\%/year).}}}}
\label{table:uvindex}
\end{table}

{Comparable UV reductions, of 30-40\% due to aerosols, were reported by
Panicker et al.}\textsuperscript{\hyperref[csl:11]{11}}{ over Pune, India from April 2004 to
March 2005, with sensitivity coefficients (i.e. change in UVI per unit
change in AOD) similar to those found here in
Table~}{\ref{table:TUVmodel}}{. Over Europe,
ground-based UVI observations for several decades are systematically
lower than those estimated from satellites even after consideration of
climatological aerosol distributions, showing the importance of local
pollution not resolved from space.}\textsuperscript{\hyperref[csl:50]{50}}\selectlanguage{english}
\begin{table}[H]
\centering
\begin{tabular}{lcc} \hline
\textbf{Conditions} & \textbf{UV Index at Noon 21 June} & \textbf{Description} \\ \hline
Clean PBL & 15.9 & \\ \hline
Year 2000 - Aerosols AOD:&\multirow{3}{*}{9.7}& \multirow{3}{5cm}{-6.2 (a 39\% reduction from clean atmosphere)} \\ 0.23 in FT, 0.7 in PBL;\\ O\textsubscript{3}=70, NO\textsubscript{2}=40, SO\textsubscript{2}=10 ppb\\ \hline
Excluding FT aerosols & 10.8 & +1.1 \\\hline
Excluding PBL aerosols & 12.7 & +3.0 \\\hline
Excluding PBL O\textsubscript{3} & 10.4 & +0.7 \\\hline
Excluding PBL NO\textsubscript{2} & 10.1 & +0.4 \\\hline
Excluding PBL SO\textsubscript{2} & 9.9 & +0.2\\\hline
Year 2019 - Aerosol AOD: & \multirow{4}{*}{11.1} & \multirow{4}{5cm}{+1.4 (relative to 2000) a 14\% increase; +4.8 (relative to clean atmosphere) still 30\% reduction from clean atmosphere}\\
0.23 in FT, 0.5 in PBL;\\ O\textsubscript{3}=50, NO\textsubscript{2}=20, SO\textsubscript{2}=1 ppb\\ &&\\\hline
\end{tabular}
\caption{{TUV Model Calculation Illustrating the Effect of Pollutants on the UV Index in Mexico City. The contribution of each pollutant is evaluated by subtraction from the full mixture, rather than individual additions to clean air, to represent more faithfully the interaction between scattering and absorption, e.g. scattering-induced changes in photon path lengths through absorbing gases.}}
\label{table:TUVmodel}
\end{table}

UV reductions by air pollutants are expected to be most severe near the
surface. Thus, such reductions cannot be applied directly to the
photochemical processing that occurs throughout the ABL. If the aerosols
are optically thin and moderately absorbing (as is the case here), the
reduction in vertically averaged UV can be estimated crudely as half of
the reduction seen at the surface (e.g., Castro et
al.~\textsuperscript{\hyperref[csl:44]{44}}, see their Fig. 7). However, scattering
complicates the situation, and a full radiative transfer calculation is
preferable to such crude estimates, with the observed surface UVI used
to anchor the model at the lower boundary.

An issue that is beginning to gain relevance in radiative balance models
is the influence of a group of organic compounds capable of strongly
absorbing in the UV region (brown carbon).\textsuperscript{\hyperref[csl:51]{51}} Some of
these compounds are related with emissions from local and regional
wildfires.\textsuperscript{\hyperref[csl:52]{52}} Mexico City is frequently exposed to
regional fire smoke transport during the dry part of the year (November
to May)\textsuperscript{\hyperref[csl:53]{53}}, that sporadically modify the optical
properties of the aerosols.\textsuperscript{\hyperref[csl:54]{54}} This could partly explain
the relatively minor reductions in PM\textsubscript{10} (see
Fig.~{\ref{829996}}), compared to the larger reductions
of CO, NO\textsubscript{2}, and O\textsubscript{3} that are more
directly related to urban activities, as well as some of the seasonal
asymmetry seen in Fig. {\ref{461017}}. ~

The UVI is specific to wavelengths mainly in the 300-320 nm range, and
so the question remains whether these results can be applied at longer
UV wavelengths, e.g. those important for NO\textsubscript{2} photolysis
(\textless{}420 nm). Absorption by SO\textsubscript{2} and
O\textsubscript{3} vanishes, while absorption by NO\textsubscript{2}
increases and typical aerosols optical depth decrease. These changes can
easily be modeled, but unfortunately far fewer measurements of these
longer wavelengths are available in Mexico City or elsewhere.

\section*{Conclusion}\label{conclusion}

Two decades of observations in Mexico City demonstrate unequivocally
that air pollution reduces UV radiation at the ground. The ground-based
observations are well below estimates derived from satellite-based
observations, and below model calculations do not consider optically
important pollutant aerosols, tropospheric ozone, and to a lesser extent
NO\textsubscript{2} and SO\textsubscript{2}. When typical observed
values of these pollutants are included in a model (e.g. TUV), the
differences between satellite-derived and ground-based measured values
are explained and can be attributed quantitatively to individual
observed pollutants. Long term improvements in air quality, over two
decades, are accompanied by statistically significant increases in the
observed UVI, again in good agreement with the model-predicted changes.
~

The reductions in surface UV radiation with respect to an ideally clear
atmosphere -- by 40\% in 2000 and still 30\% in 2020 -- are large, be it
the context of human UV exposure or air quality mitigation. In urban
areas where ozone production scales proportionally with UV levels and
with volatile organic compound~(VOC) emissions (the VOC-limited regime),
a 20\% increase in average UV means that VOC emissions will need to be
reduced by 20\% to meet the same values, or else successful reductions
in aerosols would lead to unwanted UV-driven increases in
O\textsubscript{3}. Given the importance of the formation of
photochemical secondary compounds in the degradation of the air quality,
it is advisable to extend a study of the impacts in the changes of
actinic flux.~The efforts that Mexico City has made to improve air
quality have achieved positive results in the levels of most air
pollutants. Nevertheless, ironically they caused an increase in UV
radiation that reaches the surface, which could have consequences on
human health. For human exposure, a 30\% increase in UV-induced skin
cancer and cataract would constitute a non-negligible public health
issue and require a reassessment of preventive behaviors. ~

A limitation of the present work is our focus on daily maximum values,
which largely exclude cloud cover. Absorption within clouds can be
enhanced by the long path lengths of multiply scattered photons (e.g.,
Mayer et al.\textsuperscript{\hyperref[csl:55]{55}}), so that accurate quantification of UV
effects of clouds in polluted environments remains a significant
challenge and interesting opportunity for future work.~

\section*{Acknowledgements}\label{acknowledgements}

We wish to acknowledge the staff of SIMAT, from the Secretariat of
Environment, for the data and the continuous assistance during the
realization of this project. Adriana Ipi\selectlanguage{ngerman}ña would like to extend her
thanks to\textbf{~}Dirección General de Personal Académico, Universidad
Nacional Autónoma~de México (DGAPA-UNAM) for the postdoctoral fellowship
at Centro de Ciencias~de la Atmósfera of the UNAM.~Rubén D Piacentini
wishes to thank CONICET and National University of Rosario, Argentina,
for their partial support to the present work.~The National Center for
Atmospheric Research is sponsored by the National Science Foundation.

\selectlanguage{english}
\FloatBarrier
\section*{References}\sloppy
\phantomsection
\label{csl:1}(1) Taylor, H. R.; West, S. K.; Rosenthal, F. S.; Mu{\~{n}}oz, B.; Newland, H. S.; Abbey, H.; Emmett, E. A. {Effect of Ultraviolet Radiation on Cataract Formation}. \textit{New England Journal of Medicine} \textbf{1988}, \textit{319} (22), 1429–1433. \url{https://doi.org/10.1056/nejm198812013192201.}

\phantomsection
\label{csl:2}(2) Varotsos, C.; Feretis, E. {Health Effects on Human Eye Resulting from the Increased Ambient Solar Ultraviolet Radiation}. \textit{Toxicological {\&} Environmental Chemistry} \textbf{1997}, \textit{61} (1-4), 43–68. \url{https://doi.org/10.1080/02772249709358473.}

\phantomsection
\label{csl:3}(3) Lucas, R. M.; Yazar, S.; Young, A. R.; Norval, M.; de-Gruijl, F. R.; Takizawa, Y.; Rhodes, L. E.; Sinclair, C. A.; Neale, R. E. {Human Health in Relation to Exposure to Solar Ultraviolet Radiation under Changing Stratospheric Ozone and Climate}. \textit{Photochemical {\&} Photobiological Sciences} \textbf{2019}, \textit{18} (3), 641–680. \url{https://doi.org/10.1039/c8pp90060d.}

\phantomsection
\label{csl:4}(4) Leighton, P. A. {Physical Chemistry}. In \textit{Photochemistry of Air Pollution}; Elsevier, 1961; pp v--vi. \url{https://doi.org/10.1016/b978-0-12-442250-6.50004-3.}

\phantomsection
\label{csl:5}(5) Seinfeld, J. H.; Pandis, S. N.; Noone, K. {Atmospheric Chemistry and Physics: From Air Pollution to Climate Change}. \textit{Physics Today} \textbf{1998}, \textit{51} (10), 88–90. \url{https://doi.org/10.1063/1.882420.}

\phantomsection
\label{csl:6}(6) Finlayson-Pitts, B. J.; Pitts, J. N. {Theory, Experiments, and Applications}. In \textit{Chemistry of the Upper and Lower Atmosphere}; Elsevier, 2000; pp xvii--xviii. \url{https://doi.org/10.1016/b978-012257060-5/50000-9.}

\phantomsection
\label{csl:7}(7) Liu, S. C.; McKeen, S. A.; Madronich, S. {Effect of Anthropogenic Aerosols on Biologically Active Ultraviolet Radiation}. \textit{Geophysical Research Letters} \textbf{1991}, \textit{18} (12), 2265–2268. \url{https://doi.org/10.1029/91gl02773.}

\phantomsection
\label{csl:8}(8) Sabziparvar, A. A.; Forster, P. M. F.; Shine, K. P. {Changes in Ultraviolet Radiation Due to Stratospheric and Tropospheric Ozone Changes since Preindustrial Times}. \textit{Journal of Geophysical Research: Atmospheres} \textbf{1998}, \textit{103} (D20), 26107–26113. \url{https://doi.org/10.1029/98jd02277.}

\phantomsection
\label{csl:9}(9) Madronich, S.; Wagner, M.; Groth, P. {Influence of Tropospheric Ozone Control on Exposure to Ultraviolet Radiation at the Surface}. \textit{Environmental Science {\&} Technology} \textbf{2011}, \textit{45} (16), 6919–6923. \url{https://doi.org/10.1021/es200701q.}

\phantomsection
\label{csl:10}(10) McKenzie, R. L.; Weinreis, C.; Johnston, P. V.; Liley, B.; Shiona, H.; Kotkamp, M.; Smale, D.; Takegawa, N.; Kondo, Y. {Effects of Urban Pollution on {UV} Spectral Irradiances}. \textit{Atmospheric Chemistry and Physics} \textbf{2008}, \textit{8} (18), 5683–5697. \url{https://doi.org/10.5194/acp-8-5683-2008.}

\phantomsection
\label{csl:11}(11) Panicker, A. S.; Pandithurai, G.; Takamura, T.; Pinker, R. T. {Aerosol Effects in the {UV}-B Spectral Region over Pune an Urban Site in India}. \textit{Geophysical Research Letters} \textbf{2009}, \textit{36} (10). \url{https://doi.org/10.1029/2009gl037632.}

\phantomsection
\label{csl:12}(12) Palancar, G. G.; Lefer, B. L.; Hall, S. R.; Shaw, W. J.; Corr, C. A.; Herndon, S. C.; Slusser, J. R.; Madronich, S. {Effect of Aerosols and NO$_{2}$ Concentration on Ultraviolet Actinic Flux near Mexico City during MILAGRO: Measurements and Model Calculations}. \textit{Atmospheric Chemistry and Physics} \textbf{2013}, \textit{13} (2), 1011–1022. \url{https://doi.org/10.5194/acp-13-1011-2013.}

\phantomsection
\label{csl:13}(13) Bais, A. F.; McKenzie, R. L.; Bernhard, G.; Aucamp, P. J.; Ilyas, M.; Madronich, S.; Tourpali, K. {Ozone Depletion and Climate Change: Impacts on {UV} Radiation}. \textit{Photochemical {\&} Photobiological Sciences} \textbf{2015}, \textit{14} (1), 19–52. \url{https://doi.org/10.1039/c4pp90032d.}

\phantomsection
\label{csl:14}(14) Hollaway, M.; Wild, O.; Yang, T.; Sun, Y.; Xu, W.; Xie, C.; Whalley, L.; Slater, E.; Heard, D.; Liu, D. {Photochemical Impacts of Haze Pollution in an Urban Environment}. \textit{Atmospheric Chemistry and Physics} \textbf{2019}, \textit{19} (15), 9699–9714. \url{https://doi.org/10.5194/acp-19-9699-2019.}

\phantomsection
\label{csl:15}(15) Li, K.; Jacob, D. J.; Liao, H.; Shen, L.; Zhang, Q.; Bates, K. H. {Anthropogenic Drivers of 2013-2017 Trends in Summer Surface Ozone in China}. \textit{Proceedings of the National Academy of Sciences} \textbf{2018}, \textit{116} (2), 422–427. \url{https://doi.org/10.1073/pnas.1812168116.}

\phantomsection
\label{csl:16}(16) Wang, Y.; Gao, W.; Wang, S.; Song, T.; Gong, Z.; Ji, D.; Wang, L.; Liu, Z.; Tang, G.; Huo, Y.; et al. {Contrasting Trends of {PM}2.5 and Surface-Ozone Concentrations in China from 2013 to 2017}. \textit{National Science Review} \textbf{2020}, \textit{7} (8), 1331–1339. \url{https://doi.org/10.1093/nsr/nwaa032.}

\phantomsection
\label{csl:17}(17) Wang, W.; Li, X.; Shao, M.; Hu, M.; Zeng, L.; Wu, Y.; Tan, T. {The Impact of Aerosols on Photolysis Frequencies and Ozone Production in  Beijing during the 4-Year Period 2012-2015}. \textit{Atmospheric Chemistry and Physics} \textbf{2019}, \textit{19} (14), 9413–9429. \url{https://doi.org/10.5194/acp-19-9413-2019.}

\phantomsection
\label{csl:18}(18) Gao, J.; Li, Y.; Zhu, B.; Hu, B.; Wang, L.; Bao, F. {What Have We Missed When Studying the Impact of Aerosols on Surface Ozone via Changing Photolysis Rates?}. \textbf{2020}. \url{https://doi.org/10.5194/acp-2020-140.}

\phantomsection
\label{csl:19}(19) Ma, X.; Huang, J.; Zhao, T.; Liu, C.; Zhao, K.; Xing, J.; Xiao, W. {Rapid Increase in Summer Surface Ozone over the North China Plain during 2013-2019: a Side Effect of Particulate Matters Reduction Control?}. \textbf{2020}. \url{https://doi.org/10.5194/acp-2020-385.}

\phantomsection
\label{csl:20}(20) Bauwens, M.; Compernolle, S.; Stavrakou, T.; Müller, J.-F.; Gent, J.; Eskes, H.; Levelt, P. F.; A, R.; Veefkind, J. P.; Vlietinck, J.; et al. {Impact of Coronavirus Outbreak on NO2 Pollution Assessed Using TROPOMI and OMI Observations}. \textbf{2020}, \textit{47} (11). \url{https://doi.org/10.1029/2020gl087978.}

\phantomsection
\label{csl:21}(21) Venter, Z. S.; Aunan, K.; Chowdhury, S.; Lelieveld, J. {{COVID}-19 Lockdowns Cause Global Air Pollution Declines}. \textit{Proceedings of the National Academy of Sciences} \textbf{2020}, \textit{117} (32), 18984–18990. \url{https://doi.org/10.1073/pnas.2006853117.}

\phantomsection
\label{csl:22}(22) Shi, X.; Brasseur, G. P. {The Response in Air Quality to the Reduction of Chinese Economic Activities During the {COVID}-19 Outbreak}. \textit{Geophysical Research Letters} \textbf{2020}, \textit{47} (11). \url{https://doi.org/10.1029/2020gl088070.}

\phantomsection
\label{csl:23}(23) Le, T.; Wang, Y.; Liu, L.; Yang, J.; Yung, Y. L.; Li, G.; Seinfeld, J. H. {Unexpected Air Pollution with Marked Emission Reductions during the {COVID}-19 Outbreak in China}. \textit{Science} \textbf{2020}, \textit{369} (6504), 702–706. \url{https://doi.org/10.1126/science.abb7431.}

\phantomsection
\label{csl:24}(24) \textit{{Red Automática De Monitoreo Atmosférico (RAMA)}}; \url{http://www.aire.cdmx.gob.mx/descargas/datos/excel/RAMAxls.pdf.}

\phantomsection
\label{csl:25}(25) Doran, J. C.; Abbott, S.; Archuleta, J.; Bian, X.; Chow, J.; Coulter, R. L.; Wekker, S. F. J. de; Edgerton, S.; Elliott, S.; Fernandez, A.; et al. {The IMADA-AVER Boundary Layer Experiment in the Mexico City Area}. \textit{Bulletin of the American Meteorological Society} \textbf{1998}, \textit{79} (11), 2497–2508. \url{https://doi.org/10.1175/1520-0477(1998)079<2497:TIABLE>2.0.CO;2.}

\phantomsection
\label{csl:26}(26) Molina, L. T.; Kolb, C. E.; Foy, B. de; Lamb, B. K.; Brune, W. H.; Jimenez, J. L.; Ramos-Villegas, R.; Sarmiento, J.; Paramo-Figueroa, V. H.; Cardenas, B.; et al. {Air Quality in North America's Most Populous City - Overview of the {MCMA}-2003 Campaign}. \textit{Atmospheric Chemistry and Physics} \textbf{2007}, \textit{7} (10), 2447–2473. \url{https://doi.org/10.5194/acp-7-2447-2007.}

\phantomsection
\label{csl:27}(27) Molina, L. T.; Madronich, S.; Gaffney, J. S.; Apel, E.; Foy, B. de; Fast, J.; Ferrare, R.; Herndon, S.; Jimenez, J. L.; Lamb, B.; et al. {An Overview of the {MILAGRO} 2006 Campaign: Mexico City Emissions and Their Transport and Transformation}. \textit{Atmospheric Chemistry and Physics} \textbf{2010}, \textit{10} (18), 8697–8760. \url{https://doi.org/10.5194/acp-10-8697-2010.}

\phantomsection
\label{csl:28}(28) Jazcilevich, A. D.; Garc{\'{\i}}a, A. R.; Caetano, E. {Locally Induced Surface Air Confluence by Complex Terrain and Its Effects on Air Pollution in the Valley of Mexico}. \textit{Atmospheric Environment} \textbf{2005}, \textit{39} (30), 5481–5489. \url{https://doi.org/10.1016/j.atmosenv.2005.05.046.}

\phantomsection
\label{csl:29}(29) Tie, X.; Madronich, S.; Li, G. H.; Ying, Z.; Zhang, R.; Garcia, A. R.; Lee-Taylor, J.; Liu, Y. {Characterizations of Chemical Oxidants in Mexico City: A Regional Chemical Dynamical Model ({WRF}-Chem) Study}. \textit{Atmospheric Environment} \textbf{2007}, \textit{41} (9), 1989–2008. \url{https://doi.org/10.1016/j.atmosenv.2006.10.053.}

\phantomsection
\label{csl:30}(30) Zhang, Y.; Dubey, M. K.; Olsen, S. C.; Zheng, J.; Zhang, R. {Comparisons of {WRF}/Chem Simulations in Mexico City with Ground-Based {RAMA} Measurements during the 2006-{MILAGRO}}. \textit{Atmospheric Chemistry and Physics} \textbf{2009}, \textit{9} (11), 3777–3798. \url{https://doi.org/10.5194/acp-9-3777-2009.}

\phantomsection
\label{csl:31}(31) Zavala, M.; Brune, W. H.; Velasco, E.; Retama, A.; Cruz-Alavez, L. A.; Molina, L. T. {Changes in Ozone Production and {VOC} Reactivity in the Atmosphere of the Mexico City Metropolitan Area}. \textit{Atmospheric Environment} \textbf{2020}, \textit{238}, 117747. \url{https://doi.org/10.1016/j.atmosenv.2020.117747.}

\phantomsection
\label{csl:32}(32) \textit{{Secretaría Del Medio Ambiente (SEDEMA)}}; \url{https://www.sedema.cdmx.gob.mx/.}

\phantomsection
\label{csl:33}(33) WHO. \textit{{Global Solar UV Index: A Practical Guide}}; 2002.

\phantomsection
\label{csl:34}(34) Webb, A. R.; Slaper, H.; Koepke, P.; Schmalwieser, A. W. {Know Your Standard: Clarifying the {CIE} Erythema Action Spectrum}. \textit{Photochemistry and Photobiology} \textbf{2011}, \textit{87} (2), 483–486. \url{https://doi.org/10.1111/j.1751-1097.2010.00871.x.}

\phantomsection
\label{csl:35}(35) Whiteman, C. D.; Zhong, S.; Bian, X.; Fast, J. D.; Doran, J. C. {Boundary Layer Evolution and Regional-Scale Diurnal Circulations over the and Mexican Plateau}. \textit{Journal of Geophysical Research: Atmospheres} \textbf{2000}, \textit{105} (D8), 10081–10102. \url{https://doi.org/10.1029/2000jd900039.}

\phantomsection
\label{csl:36}(36) Fast, J. D.; Foy, B. de; Rosas, F. A.; Caetano, E.; Carmichael, G.; Emmons, L.; McKenna, D.; Mena, M.; Skamarock, W.; Tie, X.; et al. {A Meteorological Overview of the {MILAGRO} Field Campaigns}. \textit{Atmospheric Chemistry and Physics} \textbf{2007}, \textit{7} (9), 2233–2257. \url{https://doi.org/10.5194/acp-7-2233-2007.}

\phantomsection
\label{csl:37}(37) \textit{{Sistema De Monitoreo Atmosférico (SIMAT)}}; www.aire.cdmx.gob.mx.

\phantomsection
\label{csl:38}(38) Holben, B. N.; Eck, T. F.; Slutsker, I.; Tanr{\'{e}}, D.; Buis, J. P.; Setzer, A.; Vermote, E.; Reagan, J. A.; Kaufman, Y. J.; Nakajima, T.; et al. {{AERONET}'A Federated Instrument Network and Data Archive for Aerosol Characterization}. \textit{Remote Sensing of Environment} \textbf{1998}, \textit{66} (1), 1–16. \url{https://doi.org/10.1016/s0034-4257(98)00031-5.}

\phantomsection
\label{csl:39}(39) \textit{{NASA EOS/Aura Validation Data Center (AVDC) - Correlative Data, Field of View Predictions, Data Subsets, GEOMS, DCIO}}; \url{https://avdc.gsfc.nasa.gov/pub/most_popular/overpass/OMI/.}

\phantomsection
\label{csl:40}(40) Madronich, S. {Intercomparison of {NO}2 Photodissociation and U.V. Radiometer Measurements}. \textit{Atmospheric Environment} \textbf{1987}, \textit{21} (3), 569–578. \url{https://doi.org/10.1016/0004-6981(87)90039-4.}

\phantomsection
\label{csl:41}(41) Shaw, W. J.; Pekour, M. S.; Coulter, R. L.; Martin, T. J.; Walters, J. T. {The Daytime Mixing Layer Observed by Radiosonde Profiler, and Lidar during {MILAGRO}}. \textit{Atmospheric Chemistry and Physics Discussions} \textbf{2007}, \textit{7} (5), 15025–15065. \url{https://doi.org/10.5194/acpd-7-15025-2007.}

\phantomsection
\label{csl:42}(42) Elterman, L. \textit{{An Atlas of Aerosol Attenuation and Extinction Profiles for the Troposphere and Stratosphere}}; Defense Technical Information Center, 1966. \url{https://doi.org/10.21236/ad0649778.}

\phantomsection
\label{csl:43}(43) Corr, C. A.; Krotkov, N.; Madronich, S.; Slusser, J. R.; Holben, B.; Gao, W.; Flynn, J.; Lefer, B.; Kreidenweis, S. M. {Retrieval of Aerosol Single Scattering Albedo at Ultraviolet Wavelengths at the T1 Site during {MILAGRO}}. \textit{Atmospheric Chemistry and Physics} \textbf{2009}, \textit{9} (15), 5813–5827. \url{https://doi.org/10.5194/acp-9-5813-2009.}

\phantomsection
\label{csl:44}(44) Castro, T.; Madronich, S.; Rivale, S.; Muhlia, A.; Mar, B. {The Influence of Aerosols on Photochemical Smog in Mexico City}. \textit{Atmospheric Environment} \textbf{2001}, \textit{35} (10), 1765–1772. \url{https://doi.org/10.1016/s1352-2310(00)00449-0.}

\phantomsection
\label{csl:45}(45) SEDEMA. \textit{{Calidad Del Aire En La Ciudad De México, Informe 2017}}; Secretaría del Medio Ambiente, Gobierno de la Ciudad de México, México, 2018a.

\phantomsection
\label{csl:46}(46) Cabrera, S.; Ipi{\~{n}}a, A.; Damiani, A.; Cordero, R. R.; Piacentini, R. D. {{UV} Index Values and Trends in Santiago Chile (33.5$\circ$S) Based on Ground and Satellite Data}. \textit{Journal of Photochemistry and Photobiology B: Biology} \textbf{2012}, \textit{115}, 73–84. \url{https://doi.org/10.1016/j.jphotobiol.2012.06.013.}

\phantomsection
\label{csl:47}(47) Parrish, D. D.; Singh, H. B.; Molina, L.; Madronich, S. {Air Quality Progress in North American Megacities: A Review}. \textit{Atmospheric Environment} \textbf{2011}, \textit{45} (39), 7015–7025. \url{https://doi.org/10.1016/j.atmosenv.2011.09.039.}

\phantomsection
\label{csl:48}(48) \textit{{Informe Anual Calidad Del Aire 2017}}; \url{http://www.aire.cdmx.gob.mx/descargas/publicaciones/flippingbook/informe_anual_calidad_aire_2017/mobile/#p=1.}

\phantomsection
\label{csl:49}(49) Molina; Velasco; Retama; Zavala. {Experience from Integrated Air Quality Management in the Mexico City Metropolitan Area and Singapore}. \textit{Atmosphere} \textbf{2019}, \textit{10} (9), 512. \url{https://doi.org/10.3390/atmos10090512.}

\phantomsection
\label{csl:50}(50) Vitt, R.; Laschewski, G.; Bais, A.; Di{\'{e}}moz, H.; Fountoulakis, I.; Siani, A.-M.; Matzarakis, A. {{UV}-Index Climatology for Europe Based on Satellite Data}. \textit{Atmosphere} \textbf{2020}, \textit{11} (7), 727. \url{https://doi.org/10.3390/atmos11070727.}

\phantomsection
\label{csl:51}(51) Laskin, A.; Laskin, J.; Nizkorodov, S. A. {Chemistry of Atmospheric Brown Carbon}. \textit{Chemical Reviews} \textbf{2015}, \textit{115} (10), 4335–4382. \url{https://doi.org/10.1021/cr5006167.}

\phantomsection
\label{csl:52}(52) Gadhavi, H.; Jayaraman, A. {Absorbing Aerosols: Contribution of Biomass Burning and Implications for Radiative Forcing}. \textit{Annales Geophysicae} \textbf{2010}, \textit{28} (1), 103–111. \url{https://doi.org/10.5194/angeo-28-103-2010.}

\phantomsection
\label{csl:53}(53) Rios, B.; Raga, G. B. {Smoke Emissions from Agricultural Fires in Mexico and Central America}. \textit{Journal of Applied Remote Sensing} \textbf{2019}, \textit{13} (03), 1. \url{https://doi.org/10.1117/1.jrs.13.036509.}

\phantomsection
\label{csl:54}(54) Barnard, J. C.; Volkamer, R.; Kassianov, E. I. {Estimation of the Mass Absorption Cross Section of the Organic Carbon Component of Aerosols in the Mexico City Metropolitan Area}. \textit{Atmospheric Chemistry and Physics} \textbf{2008}, \textit{8} (22), 6665–6679. \url{https://doi.org/10.5194/acp-8-6665-2008.}

\phantomsection
\label{csl:55}(55) Mayer, B.; Kylling, A.; Madronich, S.; Seckmeyer, G. {Enhanced Absorption of {UV} Radiation Due to Multiple Scattering in Clouds: Experimental Evidence and Theoretical Explanation}. \textit{Journal of Geophysical Research: Atmospheres} \textbf{1998}, \textit{103} (D23), 31241–31254. \url{https://doi.org/10.1029/98jd02676.}
\end{document}

### 2021-07-21 Paper/v2/Article_UV_Mexico.tex
Rename paper folders

--- 2021-07-13 Paper_third_version/Article_UV_Mexico.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title[The UV Radiation in Mexico City]
-  {The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico
+\title[The Ultraviolet Environment]
+  {The Ultraviolet Environment of a Tropical Megacity in Transition: Mexico
   City 2000-2019}
@@
   years of measurements of the UV Index (UVI) at several ground-level
-  locations in the Mexico City Metropolitan Area and compared these data
-  with UVI values derived from satellite observations of ozone
-  and clouds (but not local pollution). The ground-based measurements were
+  locations in the Mexico City Metropolitan Area and compared these with
+  UVI values estimated from satellite overpasses observing ozone and
+  clouds (but not local pollution). The ground-based measurements were
   systematically lower than the satellite-based estimates, by ca. 40\% in
-  2000 and 25\% in 2019. Calculations with a radiative transfer model and
+  2000 and 20\% in 2019. Calculations with a radiative transfer model and
   observed concentrations of air pollutants explained well the difference
   between satellite- and ground-based UVI, and showed specific
-  contributions from aerosols in the boundary layer and the free troposphere,
+  contributions from boundary layer and free trophosperic aerosols,
   O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}, in
@@
 
-The question of how air pollution alters the urban UV radiation environment
+The question of how air pollution alters the urban UV environment
 (and~\emph{vice versa}) is not new, but studies have relied mostly on
 numerical models \cite{Liu_1991,Sabziparvar_1998,Madronich_2011},
-with relatively few available observations (e.g.,
+with relatively fewer available observations (e.g.,
 \citet{McKenzie_2008}, \citet{Panicker_2009}, \citet{Palancar_2013},
-reviewed by \citet{Bais_2015}). Increases in UV have been estimated as a consequence
-of emission reductions over the last decades, e.g. in China,\citep{Hollaway_2019,Li_2018,Wang_2020}
-and have led to less-than-expected
+reviewed by \citet{Bais_2015}). Increases in UV have been
+estimated in association with decadal emission reductions, e.g. in
+China,\citep{Hollaway_2019,Li_2018,Wang_2020}
+and that have led to less-than-expected
 reductions in photochemical smog, in part due to stronger UV
-photochemistry.\citep{Wang_2019,Gao_2020,Ma_2021}
+photochemistry.\citep{Wang_2019,Gao_2020,Ma_2020}
 Emission reductions have also occurred
@@
 radiation. Unfortunately, the observational data base of relevant UV
-radiation remains rather sparse to evaluate such model-predicted feedbacks between chemistry and radiation.~~
+radiation remains rather sparse to evaluate such model-derived
+hypotheses.~~
 
@@
 reasons: (1) Nearly 23 million people inhabit the Mexico City
-Metropolitan Area (MCMA), and the UV radiation environment has direct implications
+Metropolitan Area (MCMA), and the UV environment has direct implications
 for their health, both in terms of skin/eye UV exposure and~\emph{via}
@@
 quality. (3) Air quality within MCMA has undergone extensive scrutiny,
-with a well-established monitoring network operating since
+with a well-established monitoring network since
 1986,\cite{RAMA}
@@
 
-In this work, we analyze two decades of continuous measurements of the UV Index
+Here, we analyze two decades of continuous measurements of the UV Index
 at multiple locations within the MCMA, collected by the Secretariat of
@@
 The UVI is recognized by the World Health and Meteorological
-Organizations (WHO and WMO) as a standardized index of UV
+Organizations (WHO and WMO) as a standardized metric of UV
 radiation\cite{who2002} for global public information. An advantage
-of using the UVI as (one) measure of UV radiation is that it is being
+of using the UVI as (one) metric of UV radiation is that it is being
 increasingly observed or calculated and disseminated, enabling more
@@
 The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
-meters above sea level (m asl), surrounded by mountain ridges exceeding
+meters above sea level (asl), surrounded by mountain ridges exceeding
 5000 m asl, with complex topography and thermal inversions that inhibit
@@
 Glenside, PA) detecting wavelengths between 280-400 nm have been
-measuring erythemally-weighted solar radiation. Calibration of the
-UV sensors has been carried out annually by comparing against a
+measuring erythemally-weighted solar radiation. The calibration of the
+UV sensors was carried out annually by comparing against a
 factory-calibrated reference sensor. The output voltages from the
-network’s sensors have been compared for at least one week against the UV
-readings from the reference sensor to derive new calibration factors, which typically differed
-from the old ones by 2\% or less.
+measuring sensors were compared during at least one week against the UV
+readings from the reference sensor to derive the calibration factor. New
+calibration factors typically differed from the old ones by 2\% or less.
 Reference sensors were also calibrated by the manufacturer and updated
-periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
-Long term calibration drifts are minimized by these yearly re-calibrations.
-Although at the beginning only a few stations were in operation and
-varied, currently 11 stations are recording erythemal
+periodically (between 3 to 5 years) to avoid any bias due to aging. Long
+term calibration drift was avoided by the yearly re-calibrations.
+Although at the beginning only a few stations were in operation and have
+been changing, currently 11 stations are recording erythemal
 irradiances, which are then multiplied by 40 (see
@@
 Table~{\ref{table:stations}} describes the location of
-the stations where the UV Index has been measured.
+the stations where UV Index has been measured.
 Figure~{\ref{fig:map}} shows how the radiometers of the
-SIMAT have been distributed over MCMA, prioritizing sites with higher population density.
-Near real-time data for each station are
+SIMAT have been distributed over MCMA, prioritizing the sites with more
+density of population. Near real-time data for each station are
 available on the SIMAT official
 website~\url{http://www.aire.cdmx.gob.mx/default.php}. Daily maximum
-values (\(UVI_{\max}\)) were extracted~in each of the stations
+values (\(UVI_{\max}\)) were extracted~from each of the stations
 around solar noon from the time interval from 11:00 h-15:00 h CST
@@
     \hline
-    Station  & Environment     & Lat (°N) & Lon (°W) & El (m asl) \\ \hline
+    Station  & Environment     & Lat (ºN) & Lon (ºW) & El (masl) \\ \hline
     CHO      & semi-urban      & 19.27    & 98.89    & 2253      \\
@@
           with UV measurements, while the black dots indicate SIMAT stations
-          without UV measurements, the site indicated by an open blue dot represents a
-          discontinued site, the red dot shows the location of the
+          without UV measurements, the site on open blue dot represents a
+          discontinued site, the red dot corresponds to the location of the
           AERONET site. The location~of Mexico City and the acronyms of the UV and
@@
 
-To explore the relationship between UVI and air pollutants
+With the aim to explore the relationship between UVI and air pollutants
 levels, the hourly averages for ozone (O\textsubscript{3}), carbon
@@
 concentration is reported in $\mu$g m\textsuperscript{-3} at local
-temperature and pressure.
+conditions for temperature and pressure.
 
 Aerosol optical depth at 340 nm was obtained from the Institute of
-Geophysics of the National Autonomous University of Mexico (UNAM).
-Measurements were conducted with a CIMEL sun photometer model CE-318,
+Geophysics of the National Autonomous University of Mexico (UNAM);
+measurements were conducted with a CIMEL sun photometer model CE-318,
 which is an automatic sun-sky-scanning spectral radiometer of
@@
 Product Level 2.0 and 1.5 (only in 2019) were selected, and annual
-averages AOD\textsubscript{340} were calculated for the period 2000-2019,
-except for the year 2011 which contained large data gaps and was therefore not used.
-A previous study of the AOD behavior from 2000 to 2014 demonstrated that data gaps did not
-significantly change the trends calculated for this.\citep{Carabali_2017}
-Only 8\% of the data between the years 2014 and 2019 were missing.
-The largest data gap occurred in 2018 when the instrument was returned for calibration.
+averages AOD\textsubscript{340} were calculated from continuous
+measurements during at least 7 months. A previous study of the AOD
+behavior from 2000 to 2014 demonstrated that the gaps of data did not
+significantly change the trends over the analyzed
+period.\citep{Carabali_2017} From 2014 to 2019 there was only 8\% of the
+missing data, when the instrument was sent for calibration in 2018.
 
@@
 
-The UV Index data derived from satellite-based measurements
-were used for comparison with the ground-based measurements.
-These data were provided by the Ozone Monitoring
+Estimates of the UV Index from satellite-based measurements of clouds
+and O\textsubscript{3} were used for comparing to the ground-based
+measurements. These data were provided by the Ozone Monitoring
 Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
-is operated collaboratively by the Netherlands Agency for Aerospace
+was created in cooperation between the Netherlands Agency for Aerospace
 Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
-OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
-the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
-the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
-The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths.\cite{Tanskanen_2006} The ozone column is estimated by differential absorption of several adjacent
-wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, and is used in a radiative transfer model to estimate clear-sky UVI at the surface.
-Clouds are estimated from the observed reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm) and the clear-sky UVI is adjusted for their presence.\cite{Tanskanen_2007} A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
-The UV Index used for Mexico City corresponds to values at local noon time and clear sky
-from OMUVB Level 2 OVP data product, version 1.3 and collection 3.
+OMI (hereafter OMI-Aura/NIVR-FMI-NASA) performs observations over a
+geographical dimension of 13$\times$24km\textsuperscript{2} at nadir. For
+Mexico City, the satellite overpass time is between 19:00h - 21:00h UTC
+and data are specific for the coordinates and elevation of Mexico City.
+Measurements of the ozone profile and cloud cover are used via a
+radiative transfer model to estimate the UVI at the ground. The OMI web
+site reports UVI values for both the overpass time, and corrected to
+local solar noon.
+
+While the early OMI estimates of the UVI did not consider aerosols in
+the boundary layer, \citet{Arola_2009} suggested correcting
+the clean-skies UV index with a reduction factor based on a monthly
+global climatology of BL aerosols. For Mexico City a reduction of about
+8\% is applied, starting ca. 2013, to the OMI UVI data.
 
@@
 Ultraviolet Visible (TUV v5.3) model.\citep{Madronich_1987} The
-model atmosphere is represented by 80 vertical layers, each 1 km thick,
+model atmosphere was represented by 80 vertical layers, each 1 km thick,
 starting at the 2.24 km asl elevation of MCMA, and for which the first
@@
 (BL).\citep{Shaw_2007} The ozone profile above the BL is from the US
-Standard Atmosphere, but rescaled to a value of 259.6 DU. Total ozone columns
+Standard Atmosphere, but rescaled to a value of 259.6 DU. Totals
 including the BL contributions (of 13.7 DU in the year 2000 and 9.8 DU
-in 2019, see below) were 273.1 DU in 2000 and 269.2 DU in 2019, respectively. The
+in 2019, see below) were 273.1 DU in 2000 and 269.2 DU. The
 climatological O\textsubscript{3} column for this latitude and season is
@@
 
-Above the atmospheric boundary layer, the model atmosphere was specified to be free of aerosols,
-NO\textsubscript{2}, or SO\textsubscript{2}. In one
+Above the atmospheric boundary layer, the model was taken to be free of
+aerosols, NO\textsubscript{2}, or SO\textsubscript{2}. In one
 sensitivity study, a total AOD of 0.7 was redistributed placing 0.2 in
@@
 differed by less than 1\%. Thus, as long as the total AOD is known,
-knowledge of the exact vertical aerosol profile is not critical for
-ground-level UVI, though it would obviously affect the vertical structure of
+knowledge of the exact vertical aerosol profile is not critical towards
+ground-level UVI -- but would obviously affect the vertical structure of
 photolysis frequencies.
@@
 Figure~{\ref{628947}} shows the diurnal variation of
-the UVI for typical cloud-free days, for different seasons and
-several locations (CHO, MER, MON, PED, SAG, SFE and TLA).
-The selection of cloud-free days was aided by comparison of the measurements
-with the TUV model predictions for clear skies, with prolonged deviations and
-fluctuations usually indicative of cloudy conditions. However,
-during the rainy period (from June to October) at least a brief episode of clouds,
-is seen at CHO station around noon on 23 June
+the UVI for several specific cloud-free days, for different seasons and
+several locations (CHO, MER, MON, PED, SAG, SFE and TLA). UV Index from
+TUV model was used as reference of the behavior under clear sky days.
+According to the comparison of measurements minute by minute, the dates
+with prolonged fluctuations along the day were discarded. However,
+during the rainy period (from June to October) at least a brief clouds
+presence is common, as shown at CHO station around noon in 13 June
 2017. Peak values range from 8 during autumn/winter to above 12
@@
 the other stations, and remains in the outskirts. This site is also
-approximately 300 m higher than Mexico City downtown, so that the cleaner atmosphere at SFE
-is a result of the station’s location farther away from pollution sources,
-both horizontally and vertically.\citep{SEDEMA2018a} It is indeed expected to have
+approximately 300 m higher than Mexico City downtown, so that the
+cleaner atmosphere results from both vertical and horizontal variations
+in pollution levels.\citep{SEDEMA2018a} It is indeed expected to have
 higher values of the UVI, in agreement with the observations.
@@
     \includegraphics[width=0.70\columnwidth]{figures/season}
-    \caption{{UV Index measurements at 1-minute resolution from several SIMAT stations within the MCMA
-          under mostly cloudless conditions for representative days of the year.
+    \caption{{UV Index measured over MCMA by SIMAT stations each minute along the day
+          under practically cloudless conditions for representative days of the
+          year.
             {\label{628947}}%
@@
 
-The daily maximum UV Index values of each station,~\(UVI_{\max}\),
-are summarized in Figure~{\ref{461017}} for the entire period 2000-2019.
-These values are seen to range
+The daily maximum UV Index of each station is denoted
+by~\(UVI_{\max}\), all of them were counted in the period 2000-2019.
+As shown in Figure~{\ref{461017}}, these values ranged
 from 1 to 16, with a majority (61\%) of the days
-experiencing~\(UVI_{\max}\) values between 6 and 10, and remarkably
-few, less than 1\%, in the 13-16 range.~The lowest values are
+experienced~\(UVI_{\max}\) values between 6 and 10, and remarkably
+few, less than 1\%, in the higher 13-16 range.~The lowest values are
 likely due to winter days with heavy cloud cover and low sun angles, and
@@
     \caption{{Frequency distribution of daily maximums UV Index values in Mexico City
-    for the period 2000-2019.
+    during 2000 -2019.
     {\label{461017}}%
@@
 Fig.~{\ref{461017}}). The lowest average UVI (near 7)
-occurs in winter while from March to August the values seem to be
-flattened in the range 10-11. The rather low monthly UV Index values
-could be a consequence of the presence of clouds in the rainy
+take place in winter while from March to August the values seem to be
+flattened in the range 10-11. The rather low monthly UV Index values,
+mainly could be a consequence of the presence of clouds in the rainy
 season. However, urban aerosol pollution sources, biomass burning for
@@
 maximum~\(UVI_{\max}\) from all of stations every day (one daily
-point), the monthly averages (\(\overline{UVI}_m\))
-were calculated along the period 2000-2019 (except for June 2003 due to lack of measurements).
-Long term trends in~\(\overline{UVI}_m\) are shown
+point), the monthly averages (\(\overline{UVI}_m\)) were calculated along
+the period 2000-2019. Long term trends in~\(\overline{UVI}_m\) are shown
 in Figure~{\ref{185758}}. A clear~upward trend is seen,
@@
     \includegraphics[width=0.70\columnwidth]{figures/Boxplotcos}
-    \caption{{Monthly averages of the maximum UV Index values~(black
+    \caption{{Boxplot of the monthly averages of the maximum UV Index values~(black
           dot) in MCMA for the period 2000-2019: median (central bold line),
-          interquartile range (box edges), 10\% and 90\% percentiles (whiskers),
-          the minimum and maximum values (asterisk) and the cosine of the solar zenith angle at solar
+          standard deviation (box edges),
+          25\textsuperscript{th} and 75\textsuperscript{th} percentiles (the whiskers),
+          the minimum and maximum  values (plus sign) and the cosine of the solar zenith angle at solar
           noon (blue curve).
@@
     \includegraphics[width=0.70\columnwidth]{figures/UV_Moving_Average}
-    \caption{{Monthly
-          average UV Index (black line), the standard deviation (blue fill area) and linear fit (red line).
+    \caption{{Moving average function (light gray curve) quarterly applied to monthly
+          average UV Index, standard deviation of all data within a given month
+          (black dots and dash line) and linear fit (red line).
             {\label{185758}}%
@@
 
-The UV Index computed from OMI satellite-based observations
-over the period 2005-2019 is shown in
+The UV Index computed from satellite-based observations
+(OMI-Aura/NIVR-FMI-NASA) over the period 2005-2019 is mapped in
 Figure~{\ref{485116}}. The satellite-derived UVIs vary
-from 8 in winter to 16 in summer, these values being substantially higher
+from 8 in winter to 16 in summer, both values being substantially higher
 than the ground-based observations (ca. 7 for winter and 11 for summer,
-see Fig.~{\ref{310112}}). The maximum values are reached in June and July of each year for both data sets.
-We hypothesize that this large difference between satellite-based estimation and ground-based
+see Fig.~{\ref{310112}}). We hypothesize that this
+large difference between satellite-based estimation and ground-based
 observation of the UV index is due to the intense air pollution of
-Mexico City.~A rather similar behavior was detected in the city of Santiago,
-Chile.\citep{Cabrera_2012} Although the OMI data are corrected for climatological aerosol absorption\citep{Arola_2009}, this correction likely underestimates the absorption within the polluted Mexico City BL.
+Mexico City.~A rather similar behavior was detected in Santiago city,
+Chile.\citep{Cabrera_2012}
+
+Close inspection of Figure~{\ref{485116}} shows that
+the maximum values, those from June and July of each year, show a slight
+but systematic decrease starting ca. 2013. As mentioned in
+section Methods, this is due to the post-processing of
+OMI UVI data to account for absorption by BL aerosols\citep{Arola_2009},
+using a climatological reduction of about 8\% for Mexico City.
 
@@
 
+\subsection{Effect of pollutants on UV radiation}
+
+Trends and averages in aerosol optical depth AOD\textsubscript{340} and
+criteria pollutants PM\textsubscript{10}, CO, NO\textsubscript{2},
+O\textsubscript{3~}and SO\textsubscript{2} observed at the SIMAT
+stations over 2000-2019, are shown in
+Figure~{\ref{829996}} and summarized in
+Table~{\ref{table:uvindex}} together with
+the~\(UVI_{\max}\). Similar trends in pollutants have been noted
+before\citep{Parrish_2011,aire_cmdx_2017,Molina_2019}
+and reflect the long-term success of
+emission reduction policies and programs.
+
 \begin{figure}[H]
-  \centering
-  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
-  \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
-  \label{fig:percentage_relative_difference}
+  \begin{center}
+    \includegraphics[width=0.63\columnwidth]{figures/pollutants}
+    \caption{{Air quality trends in MCMA for the period 2000-2019~ from annual
+    averages obtained between 11h to 15h CST every day: PM\textsubscript{10}
+    (brown curve), CO (purple curve), NO\textsubscript{2} (blue curve),
+    SO\textsubscript{2}(black curve), O\textsubscript{3} (green curve) and
+    AOD\textsubscript{340} (pink curve).
+    {\label{829996}}%
+    }}
+  \end{center}
 \end{figure}
 
-Figure \ref{fig:percentage_relative_difference} shows the deviation of the OMI-derived UVI from the ground-based monthly averages. The mean deviation
-was 35\% in the period 2005-2019. Comparable UV reductions, of 30-40\% due to aerosols, were reported by
+\begin{table}[H]
+  \centering
+  \begin{tabular}{cccc} \hline
+    Variable               & $\frac{\Delta variable}{\Delta t}$ & Avg$_{2000-2019}$ & $\Delta(\%/year)$ \\ \hline
+    UVI                    & 0.08                               & 9.2               & 0.9               \\
+    PM\textsubscript{10}   & -0.10                              & 50.2              & -0.2              \\
+    CO                     & -0.08                              & 1.0               & -8.2              \\
+    NO\textsubscript{2}    & -0.96                              & 28.6              & -3.4              \\
+    O\textsubscript{3}     & -1.05                              & 61.3              & -1.7              \\
+    AOD\textsubscript{340} & -0.01                              & 0.6               & -1.6              \\
+    SO\textsubscript{2}    & -0.76                              & 8.4               & -9.1              \\
+    \hline
+  \end{tabular}
+  \caption{{{{UV Index and criteria pollutants: slope for the period 2000-2019,
+                averages in units of $\mu g/m^3$(PM$_{10}$), ppm (CO), ppb
+                (SO$_2$, NO$_2$ and O$_3$), dimensionless (UV Index and AOD$_{340}$) and
+                annual percentage change (\%/year).}}}}
+  \label{table:uvindex}
+\end{table}
+
+The observed changes in the concentrations of these air pollutants have
+significant implications for surface UV radiation, as can be
+demonstrated with the TUV radiative transfer model.
+Table~{\ref{table:TUVmodel}} summarizes UVI values for
+the June-July time period, estimated by the three methods: OMI
+satellite-derived UVI, RAMA ground-based observations, and TUV modeling
+using air pollution estimates. Two groups of values can be readily
+identified: (1) RAMA daily record values, OMI with or without BL
+aerosols, and TUV for very clean conditions, all with UVI values around
+15-16; and (2) RAMA average daily maxima and TUV UVI using MCMA
+pollutants as input, which are in good agreement for both 2018/19 and
+2000/01 but much lower than the first group. Compared to the OMI
+estimate that included the climatological aerosol correction (15.3),
+observed RAMA values were lower by 35\% in 2000 and by 20\% in 2019.
+Similarly, TUV values were 35\% lower in 2000 and 22\% lower in 2019
+relative to the TUV values of 15.6 for a pristine atmosphere.
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{lc}
+    \hline
+    \textbf{Conditions for estimation in June-July}                    & \textbf{UV Index} \\ \hline
+    RAMA maximum reached in period 2000-2019                           & 15.0              \\ \hline
+    RAMA average maxima 2018, 2019                                     & 12.3              \\ \hline
+    RAMA average maxima 2000, 2001                                     & 9.9               \\ \hline
+    OMI clear, local noon, no corrected for BL aerosols                & 16.6              \\ \hline
+    OMI with 8\% reduction for BL aerosol (Figure 1 from Arola et al.) & 15.3              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                                         & 16.1              \\ \hline
+    \begin{tabular}[c]{@{}l@{}
+      }TUV pristine pollution \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                                         & 15.6              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                                         & 12.1              \\ \hline
+    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                                         & 10.2              \\ \hline
+  \end{tabular}
+  \caption{{UV Index monthly maximum estimates for June-July.}}
+  \label{table:TUVmodel}
+\end{table}
+
+The agreement between RAMA observations and TUV model estimates is
+excellent but also probably a bit fortuitous. Clouds on average reduce
+the irradiance impingent on the surface, but scattering from them can
+also cause transient enhancements (especially if the direct sunbeam is
+not blocked) that could be recorded as daily maxima -- with cancellation
+between these cloud effects resulting in improved agreement with the
+cloud-free model. We cannot exclude that some of the observed trend in
+UVI is due to changes in cloud cover. However, the modeled fractional
+UVI reductions due to pollutants, shown in Table
+  {\ref{table:TUVmodel}}, are in such good agreement with
+the observed UVI reductions, that a compelling case can be made for a
+dominant role of air pollutants in the long-term UVI trends.
+
+Table~{\ref{table:year2000-2019}} shows the
+contributions to UVI reductions from individual pollutants. Aerosols are
+seen to be the major factor in both time periods, followed by
+O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}. The
+2000-2019 UVI increase is seen to result in comparable proportions from
+fewer aerosols, less SO\textsubscript{2}, and the combined reductions in
+O\textsubscript{3} and NO\textsubscript{2}.
+
+Comparable UV reductions, of 30-40\% due to aerosols, were reported by
 \citet{Panicker_2009} over Pune, India from April 2004 to
@@
 distributions, showing the importance of local pollution not resolved
-from space.\citep{Vitt_2020} However, the difference between
+from space.\citep{Vitt_2020} However, difference between
 satellite-derived and ground-based UVI was less than 1.0 UVI units in
 over 90\% of the cases, in contrast to the difference of 3-5 units found
-here for Mexico City (Table~{\ref{461017}}).
-
-\subsection{Effect of pollutants on UV radiation in Mexico City}
-
-Trends and averages in aerosol optical depth AOD\textsubscript{340} and
-criteria pollutants PM\textsubscript{10}, CO, NO\textsubscript{2},
-O\textsubscript{3~}and SO\textsubscript{2} observed at the SIMAT
-stations over 2000-2019, are shown in
-Figure~{\ref{829996}} and summarized in
-Table~{\ref{table:uvindex}} together with
-the~\(UVI_{\max}\). Similar trends in pollutants have been noted
-before\citep{Parrish_2011,aire_cmdx_2017,Molina_2019}
-and reflect the long-term success of
-emission reduction policies and programs.
-
-\begin{figure}[H]
-  \begin{center}
-    \includegraphics[width=0.55\columnwidth]{figures/pollutants}
-    \caption{{Air quality trends in MCMA for the period 2000-2019.~ Annual
-    averages obtained between 11h to 15h CST every day: PM\textsubscript{10}
-    (brown curve), CO (purple curve), NO\textsubscript{2} (blue curve),
-    SO\textsubscript{2}(black curve), O\textsubscript{3} (green curve) and
-    AOD\textsubscript{340} (magenta curve).
-    {\label{829996}}%
-    }}
-  \end{center}
-\end{figure}
-
-\begin{table}[H]
-  \centering
-  \begin{tabular}{cccc} \hline
-    Variable               & $\frac{absolute change}{year}$ & Avg$_{2000-2019}$ & $\Delta(\%/year)$ \\ \hline
-    UVI                    & 0.08                           & 9.2               & 0.9               \\
-    PM\textsubscript{10}   & -0.10                          & 50.2              & -0.2              \\
-    CO                     & -0.08                          & 1.0               & -8.2              \\
-    NO\textsubscript{2}    & -0.96                          & 28.6              & -3.4              \\
-    O\textsubscript{3}     & -1.05                          & 61.3              & -1.7              \\
-    AOD\textsubscript{340} & -0.01                          & 0.6               & -1.6              \\
-    SO\textsubscript{2}    & -0.76                          & 8.4               & -9.1              \\
-    \hline
-  \end{tabular}
-  \caption{{{{Trends of UV Index and criteria pollutants over 2000-2019.
-                Units: $\mu g/m^3$ for PM$_{10}$, ppm for CO, ppb for SO$_2$, NO$_2$ and O$_3$.}}}}
-  \label{table:uvindex}
-\end{table}
-
-The observed changes in the concentrations of these air pollutants have
-significant implications for surface UV radiation, as can be
-demonstrated with the TUV radiative transfer model.
-Table~{\ref{table:TUVmodel}} summarizes UVI values for
-the June-July time period, estimated by the three methods: OMI
-satellite-derived UVI, SIMAT ground-based observations, and TUV modeling
-using air pollution estimates. Two groups of values can be readily
-identified: (1) SIMAT daily record values, OMI with or without BL
-aerosols, and TUV for very clean conditions, all with UVI values around
-15-16; and (2) the average of daily maxima of SIMAT observations and TUV UVI results using
-MCMA pollutants as input. Note that SIMAT and TUV value are in good agreement
-for both 2000-2001 and 2018-2019 and are considerably lower than for group (1). Compared to the OMI
-estimate that included the climatological absorbing aerosol correction (16.6),
-observed SIMAT values were lower by 40\% in 2000 and by 25\% in 2019.
-Similarly, TUV values were 35\% lower in 2000 and 22\% lower in 2019
-relative to the TUV values of 15.6 for a pristine atmosphere.
-
-\begin{table}[H]
-  \centering
-  \begin{tabular}{lc}
-    \hline
-    \textbf{June-July}                              & \textbf{UV Index} \\ \hline
-    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
-    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
-    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
-    OMI maximum value reached in period 2005-2019   & 16.6              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
-    \begin{tabular}[c]{@{}l@{}
-      }TUV pristine atmosphere \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
-    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
-  \end{tabular}
-  \caption{{Comparison of June-July UVI maxima measured directly (SIMAT), inferred from satellite-based
-        observations (OMI), and modeled for different pollution levels (TUV).
-      }}
-  \label{table:TUVmodel}
-\end{table}
-
-The agreement between SIMAT observations and TUV model estimates is
-excellent but also probably a bit fortuitous. Clouds on average reduce
-the irradiance impingent on the surface, but scattering from them can
-also cause transient enhancements (these are only possible if the disk of the Sun is visible)
-that could be recorded as daily maxima -- with cancellation
-between these cloud effects resulting in improved agreement with the
-cloud-free model. We cannot exclude that some of the observed trend in
-UVI is due to changes in cloud cover. However, the modeled
-UVI reductions due to pollutants, shown in Table
-  {\ref{table:TUVmodel}}, are in such good agreement with
-the observed UVI reductions, that a compelling case can be made for a
-dominant role of air pollutants in the long-term UVI trends.
-
-Table~{\ref{table:year2000-2019}} shows the contribution of different pollutants
-to the UVI increase between 2000 and 2019, computed with the TUV model.
-The year 2000 was taken as the base case, and each pollutant was decreased
-to its 2019 value individually while the others were maintained at their 2000 value.
-Decreasing aerosol AOD has been the largest driver of the UVI changes,
-but the absorption by gaseous pollutants has also decreased significantly.
-Additional future reductions in AOD, NO\textsubscript{2}, and O\textsubscript{3} could increase the
-UVI further, while the low SO\textsubscript{2} levels reached by 2019 are expected
-to have negligible effects in the UVI.
+for Mexico City (Table~{\ref{461017}}).
 
@@
 surface, while chemical reactions leading to photochemical smog occur
-throughout the vertical extent of the BL.
+through the vertical extent of the BL.
 Figure~{\ref{973680}} shows the vertical profiles of
-photolysis coefficients (the reciprocals of photolytic lifetimes) computed with the TUV model, for
+photolysis coefficients (the reciprocals of photolytic lifetimes) for
 two key reactions, the photolysis of O\textsubscript{3} to yield excited
@@
 An issue that is beginning to gain relevance in radiative balance models
-is the influence of a group of organic compounds known as “brown carbon” that are
-capable of strongly absorbing in the UV region.\citep{Laskin_2015} Some of
-these compounds are related to emissions from local and regional
+is the influence of a group of organic compounds capable of strongly
+absorbing in the UV region (brown carbon).\citep{Laskin_2015} Some of
+these compounds are related with emissions from local and regional
 wildfires.\citep{Gadhavi_2010} Mexico City is frequently exposed to
 regional fire smoke transport during the dry part of the year (November
-to May)\citep{Rios_2019}, which sporadically modify the optical
+to May)\citep{Rios_2019}, that sporadically modify the optical
 properties of the aerosols.\citep{Barnard_2008} This could partly explain
@@
 (\textless{}420 nm). Absorption by SO\textsubscript{2} and
-O\textsubscript{3} vanishes for wavelengths larger than about 330 nm,
-while NO\textsubscript{2} photolysis is mostly driven by UV-A radiation
-and typical aerosols optical depth decrease with wavelength. These changes can
+O\textsubscript{3} vanishes, while absorption by NO\textsubscript{2}
+increases and typical aerosols optical depth decrease. These changes can
 easily be modeled, but unfortunately far fewer measurements of these
@@
 that air pollution reduces UV radiation at the ground. The ground-based
-observations are well below values derived from satellite-based
-observations. Although ideally both data sets should match,
-the satellite has a limitation to seeing boundary layer absorbers.
-Thus, they do not reveal long-term UVI trends, due to substantial air quality improvemnets, that are evident in the ground-based UVI data.
-When typical values of pollutant: aerosols,
-tropospheric ozone, NO\textsubscript{2}
-and SO\textsubscript{2}, are included in a model (e.g. TUV), the
+observations are well below estimates derived from satellite-based
+observations, and below model calculations do not consider optically
+important pollutant aerosols, tropospheric ozone, and to a lesser extent
+NO\textsubscript{2} and SO\textsubscript{2}. When typical observed
+values of these pollutants are included in a model (e.g. TUV), the
 differences between satellite-derived and ground-based measured values
 are explained and can be attributed quantitatively to individual
-observed pollutants. Long term improvements in air quality over the last two decades,
-were accompanied by statistically significant increases in the
-observed UVI, in agreement with the model-predicted changes.
+observed pollutants. Long term improvements in air quality, over two
+decades, are accompanied by statistically significant increases in the
+observed UVI, again in good agreement with the model-predicted changes.
 
@@
   \centering
-  \begin{tabular}{cc}
+  \begin{tabular}{lccccc}
     \hline
-    Pollutant           & UVI Change \\ \hline
-    AOD                 & 0.8        \\
-    O\textsubscript{3}  & 0.4        \\
-    NO\textsubscript{2} & 0.4        \\
-    SO\textsubscript{2} & 0.5        \\ \hline
+    \multicolumn{1}{c}{\multirow{2}{*}{Pollutant}} & \multicolumn{2}{c}{Year 2000} & \multicolumn{2}{c}{Year 2019} & 2019-2000                 \\ \cline{2-6}
+    \multicolumn{1}{c}{}                           & poll. level (a)               & UVI (b)                       & poll. level & UVI   & (c) \\ \hline
+    AOD                                            & 0.7                           & -3.7                          & 0.5         & -2.7  & 1.0 \\
+    O\textsubscript{3} ppb (DU)                    & 70 (14)                       & -1.4                          & 50 (10)     & -1.0  & 0.4 \\
+    NO\textsubscript{2} ppb                        & 40                            & -0.9                          & 20          & -0.5  & 0.4 \\
+    SO\textsubscript{2} ppb                        & 30                            & -0.8                          & 1           & -0.04 & 0.8 \\ \hline
   \end{tabular}
-  \caption{Contributions of individual pollutants to the 2000-2019 UV Index changes.
-Baseline calculation for 2000 conditions (AOD = 0.7, O\textsubscript{3} = 70 ppb, NO\textsubscript{2} = 40 ppb, SO\textsubscript{2} = 20 ppb).
-Individual pollutant contributions are estimated by adjusting each pollutant, one at the time, to its 2019 value (AOD = 0.5, O\textsubscript{3} = 50 ppb, NO\textsubscript{2} = 20 ppb, SO\textsubscript{2} = 1 ppb), while maintaining the others at their 2000 value.}
+  \caption{Contributions of individual pollutants to UV Index changes.
+(a) Values used one at the time, with the others held at zero.
+(b) UVI deviation from the zero-pollution value of 16.1 (from Table \ref{table:TUVmodel}).
+(c) 2019-2000 UVI change due to changes in each pollutant.}
   \label{table:year2000-2019}
@@
 The reductions in surface UV radiation with respect to an ideally clear
-atmosphere -- by nearly 40\% in 2000 and still 20\% in 2019 -- are
+atmosphere -- by nearly 40\% in 2000 and still 20\% in 2020 -- are
 large, both within the context of human UV exposure and air quality
@@
 and other UV-related health effects. The efforts that Mexico City has
-made to improve air quality have reduced levels
+made to improve air quality have achieved positive results in the levels
 of most air pollutants. Nevertheless, they caused an increase in UV
@@
 
-Finally, based on our results, the solar radiation monitoring network might
-be improved by adding observation sites far enough away to lessen the
-influence of the urban plume (e. g., Amecameca; latitude: 19.13°N, longitude: 99.76°W, elevation: 2420 m asl),
-and the adding sensors to existing monitoring sites at higher elevations
-(Ajusco, AJU, 2953 m asl or Instituto de Investigaciones Nucleares, INN, 3082 m asl).
+A limitation of the present work is our focus on daily maximum values,
+which largely exclude cloud cover. Absorption within clouds can be
+enhanced by the long path lengths of multiply scattered photons (e.g.,
+\citet{Mayer_1998}), so that accurate quantification of UV
+effects of clouds in polluted environments remains a significant
+challenge and interesting opportunity for future work.
+
+Finally, based on our results, the solar radiation monitoring network could be
+improved by adding observation sites within or close to the basin, with minor
+influences of the urban plume (e. g., Amecameca; latitude: 19.13ºN, longitude: 99.76ºW, elevation: 2420 m asl),
+and the complementing of sensors in existing monitoring sites that are at elevations above the urban boundary
+layer like Ajusco (AJU, elevation: 2953 m asl) or Instituto de Investigaciones Nucleares (INN, elevation: 3082 m asl).
 These sites would provide valuable observations to assess quantitatively the effects of urban pollution on solar radiation levels.
@@
   wishes to thank CONICET and National University of Rosario, Argentina,
-  for their partial support to the present work. We thank Dr. Jay Herman
-  (University of Maryland Baltimore County) for useful discussions. The National Center for
+  for their partial support to the present work. The National Center for
   Atmospheric Research is sponsored by the National Science Foundation.

### 2021-07-21 Paper/v4/Article_UV_Mexico.tex
Rename paper folders

--- 2021-07-19 Paper_4_version/Article_UV_Mexico.tex
@@
 A previous study of the AOD behavior from 2000 to 2014 demonstrated that data gaps did not
-significantly change the trends calculated for this.\citep{Carabali_2017}
+significantly change the trends calculated for this time period.\citep{Carabali_2017}
 Only 8\% of the data between the years 2014 and 2019 were missing.
@@
 the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
-the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
+the satellite overpass time is between 19:00h - 21:00h UTC (13:00h - 15:00h CST).
 The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths.\cite{Tanskanen_2006} The ozone column is estimated by differential absorption of several adjacent
@@
 fluctuations usually indicative of cloudy conditions. However,
-during the rainy period (from June to October) at least a brief episode of clouds,
+during the rainy period (from June to October) at least a brief episode of clouds
 is seen at CHO station around noon on 23 June
@@
 over 90\% of the cases, in contrast to the difference of 3-5 units found
-here for Mexico City (Table~{\ref{461017}}).
+here for Mexico City.
 
@@
 two key reactions, the photolysis of O\textsubscript{3} to yield excited
-oxygen atoms O(1D), and the photolysis of NO\textsubscript{2}. In the
+oxygen atoms O(\textsuperscript{1}D), and the photolysis of NO\textsubscript{2}. In the
 absence of optically active pollutants, these coefficients would be
@@
     \caption{{Vertical profiles of the photolysis coefficients for the
-          reaction~\(O_3 + h\nu \rightarrow O(1D) + O_2\) (top axis, blue)~\(NO_2 + h\nu \rightarrow O+NO \) (bottom
+          reaction~\(O_3 + h\nu \rightarrow O(^1D) + O_2\) (top axis, blue)~\(NO_2 + h\nu \rightarrow O+NO \) (bottom
           axis, red) for zero pollution (solid) and Mexico City in the years 2000
@@
 observations. Although ideally both data sets should match,
-the satellite has a limitation to seeing boundary layer absorbers.
+the limited ability of satellites to detect BL absorbers means that they cannot reveal long-term UV trends.
 Thus, they do not reveal long-term UVI trends, due to substantial air quality improvemnets, that are evident in the ground-based UVI data.
-When typical values of pollutant: aerosols,
+When typical values of pollutant aerosols,
 tropospheric ozone, NO\textsubscript{2}
@@
 are explained and can be attributed quantitatively to individual
-observed pollutants. Long term improvements in air quality over the last two decades,
+observed pollutants. Long term improvements in air quality over the last two decades
 were accompanied by statistically significant increases in the
